### 2016-02-23 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
updates to numerical model, energy budget section; removed appendix

\documentclass[apj]{emulateapj}

%Specify packages
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage[tight]{subfigure}
\usepackage[breaklinks,colorlinks,citecolor=blue]{hyperref}
\usepackage[all]{hypcap}
\usepackage[utf8]{inputenc} %force unicode in bibtex
\usepackage{enumitem}
%use for editing/highlighting
\usepackage{color,soul}
%\usepackage{lineno}

%Define new commands as needed
\newcommand{\ang}{\AA~}
\defcitealias{barnes_inference_2016}{Paper I}
\renewcommand{\sectionautorefname}{Section}
\renewcommand{\subsectionautorefname}{Subsection}
%\linenumbers
%Set options for list spacing
\setenumerate{noitemsep}
%Set tikz options
\tikzstyle{box} = [rectangle, rounded corners, text centered, draw=black]
\tikzstyle{ghost} = [rectangle, rounded corners, text centered, draw=white]
\tikzstyle{arrow} = [thick, ->, >=stealth]

\begin{document}
	%Frontmatter
	\title{Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains}
	\author{W. T. Barnes}
	\affil{Department of Physics \& Astronomy, Rice University, Houston, TX 77251-1892}
	\email{will.t.barnes@rice.edu}
	\author{P. J. Cargill}
	\affil{Space and Atmospheric Physics, The Blackett Laboratory, Imperial College, London SW7 2BW}
	\affil{School of Mathematics and Statistics, University of St. Andrews, St. Andrews, Scotland KY16 9SS}
	\and
	\author{S. J. Bradshaw}
	\affil{Department of Physics \& Astronomy, Rice University, Houston, TX 77251-1892}
	%Abstract
	\begin{abstract}
		Faint, high-temperature emission in active region cores has long been predicted as a signature of nanoflare heating. However, the detection of such emission has proved difficult due to a combination of the efficiency of thermal conduction, non-equilibrium ionization, and inadequate instrument sensitivity. This second paper in our series on hot non-flaring plasma in active regions aims to show how the assumption of electron-ion equilibrium leads to misleading conclusions regarding the hot emission. We have used an efficient two-fluid hydrodynamic model to carry out a parameter exploration in preferentially heated species, heating event frequency, and the power-law index determining the distribution of event energies. By computing the emission measure distributions and calculating their ``hotward'' slopes, we have concluded that not treating the electron and ion populations separately leads to a mischaracterization of the hot emission. Additionally, we find that, while emission due to separate electron and ion heating differs greatly hotward of the peak, the respective coolward emission measure slopes are similar such that a distinction between the heating of one species over another based on this criteria alone is not possible. 
	\end{abstract}
	%Body
	\section{Introduction}
	\label{sec:intro}
	%
	\par Heating of the solar corona by nanoflares, first proposed by \citet{parker_nanoflares_1988}, has become one of the most favored and contentious coronal heating models  \citep{cargill_implications_1994,cargill_nanoflare_2004,klimchuk_solving_2006}. The term \textit{nanoflare} has now become synonomous with impulsive heating in the energy range $10^{24}-10^{27}$ erg, with no specific assumption regarding the underlying physical mechanism; though its origin is almost certainly magnetic.  
	%
	\par \citet{cargill_implications_1994} and \citet{cargill_nanoflare_2004} have predicted that emission measure distributions resulting from nanoflare models should be wide and have a faint, high-temperature (8-10 MK) component and thus a steep hotward slope, the so-called ``smoking gun'' of nanoflare heating. Unfortunately, observing this high-temperature emission is difficult and in some cases impossible. The reason for this difficulty is twofold. First, thermal conduction is a very efficient cooling mechanism at high temperatures and large spatial temperature gradients. When a loop is heated impulsively, its temperature rises quickly while the increase in density lags behind. By the time the density has increased sufficiently (due to chromospheric evaporation brought about by the response of the transition region to the strong downward coronal heat flux) to allow for an appreciable amount of emission (recalling $\mathrm{EM}\propto n^2$), thermal conduction has cooled the loop far below its initial hot temperature, making a direct detection of $\sim10$ MK plasma very difficult. 
	%
	\par The second reason for this difficulty is non-equilibrium ionization (NEI). It is usually assumed that the observed emission lines, because of their known formation temperatures, are a direct indicator of the plasma temperature. However, if the heating (or cooling) timescale is shorter than the ionization equilibration timescale, the time it takes for the ion population to settle into the assumed charge state, an equilibrium assumption can lead to a misdiagnosis of the plasma temperature. This makes signatures of hot, nanoflare-heated plasma especially difficult to detect if the high temperatures persist for less than the ionization timescale \citep{bradshaw_explosive_2006,bradshaw_what_2011,reale_nonequilibrium_2008}.
	%
	\par Despite these difficulties, various attempts have been made to observe this faint high-temperature emission. Using the broadband X-Ray Telescope (XRT) \citep{golub_x-ray_2007} on board the \textit{Hinode} spacecraft \citep{kosugi_hinode_2007}, \citet{schmelz_hinode_2009} and \citet{reale_evidence_2009} show a faint hot component in the reconstructed $\mathrm{DEM}$ curves. However, since the channels on such broadband instruments can often be polluted by low-temperature emission, the reliability of such measurements depends on the filtering technique used. Additionally, \citet{winebarger_defining_2012} showed that combinations of measurements from XRT and the Extreme-ultraviolet Imaging Spectrometer (EIS) \citep{culhane_euv_2007}, also on  \textit{Hinode}, leave a ``blind spot'' in the $\mathrm{EM}-T$ space conincident with the range where evidence for nanoflare heating is likely to be found. 
	%
	\par Unambiguous observational evidence of nanoflare heating must come from pure spectroscopic measurements \citep[see][]{brosius_pervasive_2014}. Additionally, new instruments with higher spatial and temporal resolution, such as \textit{IRIS} \citep{de_pontieu_interface_2014} and the \textit{Hi-C} sounding rocket \citep{cirtain_energy_2013} have provided encouraging results for impulsive heating \citep{testa_observing_2013,testa_evidence_2014}. Future missions like the Marshall Grazing Incidence X-ray Spectrometer (MaGIXS) \citep{kobayashi_marshall_2011,winebarger_new_2014}, with a wavelength range of 6-24 \ang and a temperature range of $6.2<\log{T}<7.2$, aim to probe this previously poorly-resolved portion of the coronal spectrum in hopes of better quantifying the presence of faint, high-temperature plasma.
	%
	\par One strategy for constraining the nanoflare model is analysis of modeled and observed emission measure distributions for signatures of impulsive heating in active region cores. As with cool emission, hot emission is also often described by a power-law relation of the form $\mathrm{EM}\propto T^{-b}$. Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $6.6\lesssim\log{T}\lesssim7.2$. However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range. \citet{warren_systematic_2012}, using spectral measurements from EIS, provided hotward fits for $\mathrm{EM}$ reconstructions for a large number of active regions. All measured slopes fell in the range $6.1<b<10.3$, with large uncertainties on each hotward fit.
	%
	\par An often overlooked consequence of impulsive heating in the corona is electron-ion non-equilibrium. In a fully-ionized hydrogen plasma like the solar corona, interactions between electrons and ions are governed by binary Coulomb collisions. For $n\sim10^9~\mathrm{cm}^{-3}$ and $T\sim10^7~\mathrm{K}$, parameters typical of nanoflare heating, the collisional timescale, $\tau_{ei}=1/\nu_{ei}$, where $\nu_{ei}$ is the Coulomb collision frequency (see \autoref{eq:col_freq}) can be estimated as $\tau_{ei}\approx800$ s. Thus, any heating that occurs on a timescale less than 800 s, such as a nanoflare with a duration of $\tau_H\le100$ s, will result in electron-ion non-equilibrium. Chromospheric evaporation, the response from the transition region to the strong coronal heat flux, does lead to an increase in $n$ and thus a decrease in $\tau_{ei}$. However, we maintain that during this initial phase of impulsive heating, $\tau_{ei}\gg\tau_H$ still holds, with 800 s being an approximate upper bound on $\tau_{ei}$. 
	%
	\par Additionally, while it is often assumed that the electrons are the direct recipients of the prescribed heating function, the degree to which the ions or electrons are preferentially heated in the solar corona is unknown. Thus, it is possible that the ions are preferentially heated, for instance, through ion-cyclotron wave resonances \citep{markovskii_intermittent_2004}. Ion cyclotron waves are excited by plasma instabilities in the lower corona. These waves then propagate upwards through the coronal plasma and wave particle interactions can occur for those ions whose gyrofrequencies have a resonance with the ion-cyclotron wave. Additionally, there is also evidence for ion heating via reconnection, both in laboratory plasmas and in particle-in-cell simulations \citep{ono_ion_1996,yoo_bulk_2014,drake_onset_2014}. Thus, ion heating in the solar corona should not be discounted as a possibility.
	%
	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares and nanoflare trains. In this second paper in our series on hot emission in active region cores, we use an efficient two-fluid hydrodynamic model to explore the effect of electron and ion heating on nanoflare-heated loops. In particular, we look at how the hot emission is affected by heating preferentially one species or the other as well as how this hot emission can vary with heating frequency and the power-law index that determines the event energy distribution. Additionally, we consider how NEI may affect hot emission measure slopes in the cases of electron and ion heating as well as the single-fluid case.
	%
	\par\autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure curves and slopes for the electron and ion heating cases as well as the equivalent single-fluid cases. In \autoref{sec:discussion}, we discuss the implications of two-fluid effects in the context of hot and cool emission measure slopes and the nanoflare heating model. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.
	%%
	\section{Methodology}
	\label{sec:methods}
	%
	\subsection{Numerical Model}
	\label{subsec:numerics}
	%
	\par 1D hydrodynamic models are excellent tools for computing field-aligned quantities in coronal loops. However, because of the small cell sizes needed to resolve the transition region and consequently small timesteps demanded by thermal conduction, the use of such models in large parameter space explorations is made impractical by long computational runtimes \citep{bradshaw_influence_2013}. We use the popular 0D enthalpy-based thermal evolution of loops (EBTEL) model \citep{klimchuk_highly_2008,cargill_enthalpy-based_2012,cargill_enthalpy-based_2012-1,cargill_modelling_2015}. This model, which has been successfully benchmarked against the 1D hydrodynamic HYDRAD code of \citet{bradshaw_influence_2013}, computes, with very low computational overhead, time-dependent, spatially-averaged loop quantities.
	%
	\par In order to treat the evolution of the electron and ion populations separately, we use a modified version of the usual EBTEL equations. This amounts to computing spatial averages of the two-fluid hydrodynamic equations over both the transition region and corona. A full description and derivation of these equations can be found in the appendix of \citetalias{barnes_inference_2016}. The relevant two-fluid pressure and density equations are,
	\begin{align}
		\frac{d}{dt}\bar{p}_e &= \frac{\gamma - 1}{L}\left\lbrack\psi_{TR} - (\mathcal{R}_{TR} + \mathcal{R}_C)\right\rbrack + \\ &k_B\bar{n}\nu_{ei}(\bar{T}_i - \bar{T}_e) + (\gamma - 1)\bar{Q}_e,\label{eq:ebtel2fl_pe}\\
		\frac{d}{dt}\bar{p}_i &= -\frac{\gamma - 1}{L}\psi_{TR} + k_B\bar{n}\nu_{ei}(\bar{T}_e - \bar{T}_i) +\\ &(\gamma - 1)\bar{Q}_i,\label{eq:ebtel2fl_pi}\\
		\frac{d}{dt}\bar{n} &= \frac{c_2(\gamma - 1)}{c_3\gamma Lk_B\bar{T}_e}\left(\psi_{TR} - F_{ce,0} - \mathcal{R}_{TR}\right),\label{eq:ebtel2fl_n}
	\end{align}
	%%
	where $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency and $\psi_{TR}$ is a term included to maintain charge and current and neutrality and is defined in the appendix of \citetalias{barnes_inference_2016}. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$.
	%
	\par\hl{Include some temperature and density profiles for nanoflare trains in here somehow? May need to move to next section...}
	%
	\subsection{Energy Budget}
	\label{subsec:params}
	%
	\par\hl{Details about static parameters for all runs.} All events are modeled as triangular pulses of fixed duration $\tau=200$ s.
	%
	\par We define our heating function in terms of a series of discrete heating events plus a static background heating to ensure that the loop does not drop to unphysically low temperatures and densities between events. Thus, for loop half-length $L$ and cross-sectional area $A$, for a triangular heating pulse of duration $\tau$, the total  event energy is $\varepsilon=LAH\tau/2$, where $H$ is the heating rate. Each run will consist of $N$ heating events, each with peak amplitude $H_i$, and a steady background value of $H_{bg}=3.5\times10^{-5}$ erg cm$^{-3}$ s$^{-1}$.
	%
	\begin{figure}
		\centering
		\include{parameter_space_graphic}
		\caption{Total Parameter space covered. $\Sigma$ indicates the species that is heated, where ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent. Note that $(3~\alpha~\mathrm{values})\times(3~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 10 different types of heating functions. \hl{Adjust depending on what value of $\beta$ we use in the end.}}
		\label{fig:parameter_space}
	\end{figure}
	%
	\par Recent observations have suggested that loops in active region cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim4.5\times10^{-3}$. In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored. Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by 
	\begin{equation}
		\label{eq:heating_rate_constraint}
		H_{eq} = \frac{1}{t_{total}}\sum_{i=1}^N\int_{t_i}^{t_i+\tau}\mathrm{d}t~h_i(t) = \frac{\tau}{2t_{total}}\sum_{i=1}^NH_i,
	\end{equation}
	where $t_{total}$ is the total simulation time. Note that if $H_i=H_0$ for all $i$, the uniform heating rate $H_0$ is $H_0=2t_{total}H_{eq}/N\tau$. Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the total amount of energy injected into the loop by one heating event for a loop heated by $N=20$ nanoflares in $t_{tot}=80000$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx7.2\times10^{24}$ erg, consistent with the energy budget of the Parker nanoflare model. 
	%
	\par Determining the heating frequency in active region cores will help to place constraints on the source(s) of heat in the corona. We define the heating frequency in terms of the waiting time, $t_N$, between successive heating events. Following \citet{cargill_active_2014}, the range of waiting times is $250\le T_N\le5000$ s in increments of 250 s, for a total of 20 different possible heating frequencies. Additionally, $t_N$ can be written as $T_N=(T-N\tau_H)/N$, where we fix $T=80000$ s. Note that because $T$ and $\tau_H$ are fixed, as $t_N$ increases, $N$ decreases. Correspondingly, $Q_i$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant, regardless of $t_N$.
	%
	\begin{figure}
		\centering
		\includegraphics[width=\columnwidth]{figures/heating_functions.pdf}
		\caption{\textbf{Top left}: uniform heating amplitudes for $T_N=1000$ s; \textbf{Top right:} uniform heating amplitudes for $T_N=5000$ s; \textbf{Bottom left:} power-law distributed heating amplitudes for $\alpha=-1.5$, $T_N=2000$ s; \textbf{Bottom right:} power-law distributed amplitudes for $\alpha=-1.5$ where the wait times depend on the event energies and the mean wait time for both values of $\beta$ is $\langle T_N\rangle=2000$ s.\hl{Adjust depending on what $\beta$ we use in the end.}}
		\label{fig:heating_funcs}
	\end{figure}
%
	\par According to the nanoflare heating model of \citet{parker_nanoflares_1988}, turbulent loop footpoint motions twist and stress the field, leading to a buildup and subsequent release of energy. Following \citet{cargill_active_2014}, we let $\varepsilon_i\propto t_{N,i}^{\beta}$, where $\varepsilon_i,t_{N,i}$ are the total energy and waiting time following event $i$, respectively, and $\beta=1,2$ such that the event energy scales either linearly or quadratically with the waiting time. The reasoning for such an expression is as follows. Bursty, nanoflare heating is thought to arise from the stressing and subsequent relaxation of the coronal field. If a sufficient amount of time has elapsed since the last energy release event, the field will have had enough time to ``wind up'' such that the subsequent energy release is large. Conversely, if only a small amount of time has elapsed since the last event, the field will have not had time to become as stressed, resulting in a lower energy event. Thus, this scaling provides a way to incorporate a more physically motivated heating function into a hydrodynamic model which cannot self-consistently determine the heat input based on the evolving magnetic field. \autoref{fig:heating_funcs} shows the various heating functions used for several example $t_N$ values.
	%
	\subsection{Heating Statistics}
	\label{subsec:em_dist}
	%
	%
	\par We compute the peak heating rate per event in two different ways: 1) the heating rate is uniform such that $H_i=H_0$ for all $i$ and 2) $H_i$ is chosen from a power-law distribution with index $\alpha$ where $\alpha=-1.5,-2.0,$ or $-2.5$. For the second case, it should be noted that, when $T_N\approx5000$ s, $N\sim20$ events, meaning a single run does not accurately represent the distribution of index $\alpha$. Thus, a sufficiently large number of runs, $N_{R}$, are computed for each $t_N$ to ensure that the total number of events is $N_{tot}=N\times N_{R}\sim10^4$ such that the distribution is well-represented. \autoref{fig:parameter_space} shows the parameter space we will explore. For each set of parameters and waiting time $t_N$, we compute the resulting emission measure distribution for $N$ events in a period $T$. This procedure is repeated $N_R$ times until $N\times N_R\sim10^4$ is satisfied.
	%
	\section{Results}
	\label{sec:results}
	%
	\par In our 0D model, the emission measure is calculated using the familiar expression $\mathrm{EM}=n^2(2L)$, where $L$ is the loop half-length. We consider a temperature range of $4.0\le\log{T}\le8.5$ with bin sizes of $\Delta\log{T}=0.01$. At each iteration $i$, the coronal temperature range $[T_0,T_a]$ is calculated from $\bar{T}_e$ (see \autoref{appendix}). For each bin that falls within $[T_0,T_a]$, $\bar{n}_i^2(2L)$ is added to that bin, where $\bar{n}_i$ is the spatially-averaged number density at iteration $i$. The emission measure in each bin is then averaged over the entire simulation period. When measured observationally, $\mathrm{EM}(T)$ is a line-of-sight quantity. Assuming an aspect ratio (i.e. ratio of loop length to loop width) of 10, we apply a correction factor 1/10 to all calculated $\mathrm{EM}$ curves. We do not attempt to apply an advanced forward modeling treatment here and instead reserve such an approach for a future paper. However, while effects due to NEI are neglected in our parameter space exploration, in \autoref{subsec:non-eq_ion} we consider the emission measure due to $T_{eff}$, the effective temperature due to NEI, for several test cases in order to diagnose how this might affect our calculated emission measure slopes.
	%
	\par For each species, type of power-law heating function, and waiting time $t_N$, $N_{R}$ emission measure curves are calculated. Because drawing event amplitudes from a power-law distribution introduces random fluctuations into our model, we must be sure to account for the full range of effects due to the distribution. This is especially true in the low-frequency regime, when $T_N\ge\tau_{cool}$, the cooling timescale, and there are fewer events per run. In this case, one or two especially strong heating events can lead to an extremely enhanced hotward emission measure; conversely, a run with only small events will lead to a diminished hotward slope. Thus, the mean $\mathrm{EM}$ curve of each set of $N_{R}$ runs can be said to reasonably represent the expected hot emission for a given $t_N$.
	%
	\par To characterize the emission measure, we compute the slopes on both the cool and hot sides of the peak. To be consistent with past observational and computational studies of cool emission \citep[see][and references therein]{bradshaw_diagnosing_2012}, we fit the cool slope on the interval $6.0\le\log{T}\le6.6$. Contrastingly, past studies of hot emission are less abundant; thus, the ``hot'' region where the $\mathrm{EM}$ is thought to follow a power-law is far less constrained. In order to best describe the steepness of the emission measure hotward of the peak, we choose to fit $\mathrm{EM}$ between the temperatures at which the emission measure is $99\%$ and $92\%$ of the peak value. We have no physical reason for choosing these particular bounds, but note that on this interval, the mean hotward emission is reasonably well-described by a power-law relationship. Fitting too close to the wide peak leads to misleadingly shallow slopes while fitting too close to the steep drop near $\log{T}\sim7.5$ results in steep slopes not particularly representative of the hotward emission. We perform the fit using the Levenberg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}.
	%
	\subsection{Separate Electron and Ion Heating}
	\label{subsec:electron_ion_heating}
	%
	\begin{figure*}[t]
		\centering
		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_electron_heating_dem}.pdf}
			\label{fig:el_em_curves}}
		\end{minipage}
		%
		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_electron_heating_hs_compare}.pdf}
			\label{fig:el_em_slopes}}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_electron_heating_dem_derivs}.pdf}
			\label{fig:el_em_derivs}}
		\end{minipage}
		\caption{$\alpha=-2.5,~\beta=1,~L=40$ Mm, electron heating. \textbf{Left:} $\log{\mathrm{EM}}$ as a function of $\log{T}$ for all values of $t_N$. There is an artificial spacing of $\Delta\log{\mathrm{EM}}=0.2$ between each curve. The bold blue (red) lines on either side of the peak show the linear fit to the cool (hot) emission. \textbf{Top right:} Average slopes from power-law fits to all $N_{R}$ curves as a function of $t_N$. The error bars indicate one standard deviation from the distribution of $N_{R}$ fits. In the case of hot slopes, the absolute value is shown. The dashed, solid, and dot-dashed reference lines are placed at 2, 3, and 5 respectively. \textbf{Bottom right:} Derivative of $\log{\mathrm{EM}}$ with respect to $\log{T}$. The dotted reference lines are placed at -5.5, -2.5, 2, and 3. The legend is the same as the left panel.}
		\label{fig:el_em}
	\end{figure*}
	%
	\begin{figure*}
		\centering
		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_ion_heating_dem}.pdf}
			\label{fig:ion_em_curves}}
		\end{minipage}
		%
		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_ion_heating_hs_compare}.pdf}
			\label{fig:ion_em_slopes}}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_ion_heating_dem_derivs}.pdf}
			\label{fig:ion_em_derivs}}
		\end{minipage}
		\caption{Same as \autoref{fig:el_em}, but for the case in which all of the heating is given to the ions.}
		\label{fig:ion_em}
	\end{figure*}
	%
	\par \autoref{fig:el_em} and \autoref{fig:ion_em} show the results of our emission measure study for the two distinct cases where only the electrons are heated and only the ions are heated with $\alpha=-2.5,\beta=1$ for a loop half-length of $40$ Mm, consistent with \citetalias{barnes_inference_2016}. The panels on the left show the mean $\mathrm{EM}$ for all $t_N$, where the average is taken over all $N_{R}$ runs. There is an artifical spacing of $\Delta\log{\mathrm{EM}}=0.2$ between each curve so that they can be easily distinguished from each other. The blue (red) lines indicate the cool (hot) power-law fits, where the slopes of the lines are the averages taken over all $N_{R}$ runs. We note that the $\mathrm{EM}$, for all $t_N$, peaks at approximately 4 MK ($10^{6.6}$ K), consistent with the constraints laid out in \autoref{subsec:params}. The top right panels show these average slope values as a function of $t_N$. The error bars indicate one standard deviation as calculated from the distribution of all $N_{R}$ runs.
	%
	\par Lastly, the bottom right panels show the first derivative as a function of temperature, $d\log{\mathrm{EM}}/d\log{T}$, computed using central differences. The color scheme and line styles correspond to the emission mesure curves in the left panel. As in \citetalias{barnes_inference_2016}, we compute the derivative in an effort to better assess at what temperatures the emission measure is not well described by a power-law.
	%
	\par We first briefly consider the calculated cool emission measure slopes. Looking at the top right panels of \autoref{fig:el_em} and \autoref{fig:ion_em}, we note that in the cases of electron and ion heating, the cool emission measure slopes are consistent with both observational and modeling studies of cool emission in active region cores, having values that fall within the range $2\le a\le5$ \citep[and references therein]{bradshaw_diagnosing_2012}. Furthermore, the cool slopes computed using our new modified EBTEL model, with a heating function of the form $Q\propto T_N^{\beta}$, are consistent with those values reported in \citet{cargill_active_2014} and show a dependence on the waiting time $t_N$.  
	%
	\par Additionally, looking at the bottom right panels of \autoref{fig:el_em} and \autoref{fig:ion_em}, we see that, within the range $6.0\le\log{T}\le6.6$, the $\mathrm{EM}$ is reasonably well-described by a power-law, where $2\lesssim d\log{\mathrm{EM}/d\log{T}}\lesssim3$. Comparing the cases of electron and ion heating for both the cool slopes and $d\log{\mathrm{EM}/d\log{T}}$ on $6.0\le\log{T}\le6.6$, there are no substantial differences for all values of $t_N$ considered.
	%
	\par This is not the case for the hot emission measure. Looking first at the case of electron heating in \autoref{fig:el_em}, we note that there is a pronounced ``hot shoulder'' in the emission measure (left panel) just above $10^7$ K for $T_N\gtrsim2000$ s. This feature is even more evident when looking at the derivative of $\mathrm{EM}$ in the bottom right panel of \autoref{fig:el_em}. The peak between $10^7$ and $10^{7.5}$ K shows how the $\mathrm{EM}$ flattens out around $10^7$ K, indicating an enhanced hot emission measure. Considering the large range of values of $d\log{\mathrm{EM}}/d\log{T}$ on the interval over which the fit was performed, we acknowledge that a single power-law fit is not a good description of the hot emission measure in the case of electron heating.
	%
	\par Contrastingly, we have not calculated the hot emission measure slopes for the case of ion heating. Looking at the left panel of \autoref{fig:ion_em}, for $T_N\gtrsim1000$ s, the $\mathrm{EM}$ peak is wide with a sharp cutoff just above $10^7$ K. There is no substantial emission measure component above $10^7$ K and, consequently, no hot shoulder as in the electron heating case. Applying the fitting procedure outlined above to the hot emission in the case of ion heating yields meaningful results for only a few short $t_N$. Thus, as in the case of electron heating, the resulting hot emission measure from ion heating is also not well described by a power-law. The lower right panel of \autoref{fig:ion_em} further highlights this by showing that around $10^7$ K, $d\log{\mathrm{EM}}/d\log{T}\to-\infty$.
	%
	\subsection{Single-fluid}
	\label{subsec:single_heating}
	%
	\par \autoref{fig:single_em} shows the same results as \autoref{fig:el_em} and \autoref{fig:ion_em}, but for the single-fluid case in which electron-ion equilibrium is assumed at all times. To compute these $\mathrm{EM}$ curves, we have used the original, single-fluid EBTEL model as described in \citet{klimchuk_highly_2008} and \citet{cargill_enthalpy-based_2012}. The equivalent parameter space that was investigated with the modified two-fluid EBTEL model is explored with the single-fluid EBTEL code as well.
	%
	\par We compute the hot and cool emission measure slopes in the same manner as the electron and ion heating cases. We first note that the cool emission measure slopes are comparable to those in both the electron and ion heating cases. In particular, we find $2\lesssim a\lesssim5$ for all values of $t_N$ as expected. Again, we confirm the validity of our linear fit to the cool emission by computing the derivative $d\log{\mathrm{EM}}/d\log{T}$ in the lower right panel of \autoref{fig:single_em}. For $T_N\gtrsim2000$ s, the slope is bounded between 2 and 3 on the interval $6.0\le\log{T}\le6.6$. 
	%
	\par The hot emission measure in the single-fluid case differs significantly from the two-fluid case. In contrast to the electron heating case in \autoref{fig:el_em}, the $\mathrm{EM}$ curves in the left panel of \autoref{fig:single_em} show no hot shoulder. This is further confirmed by the lower right panel; the derivative, in contrast to the electron heating case, shows no peak near $10^7$ K. For low $t_N$, $d\log{\mathrm{EM}}/d\log{T}$ is monotonically decreasing for $\log{T}\gtrsim6.6$. For $T_N\ge3000$ s, $d\log{\mathrm{EM}}/d\log{T}$ is relatively flat for $\log{T}\ge7.0$, indicating that a power-law provides a good description of the hot emission in this region. This is confirmed by noting the agreement between the fit lines and the $\mathrm{EM}$ curves in the left panel.
	%
	\par Comparing the top right panels of \autoref{fig:single_em} and \autoref{fig:el_em} further highlights the enhanced hot emission in the electron case. For high $t_N$, the hot emission slopes in the electron case converge to a value just above 3; for the single-fluid case, the hot slopes converge to approximately 4.5. Thus, while a single power-law is not a good descriptor for the hot emission in the case of electron heating, the slope still captures the enhanced hot shoulder relative to the weaker hot emission of the single-fluid case. Additionally, comparing the single-fluid case to the ion heating case in \autoref{fig:ion_em}, it is obvious that the single-fluid case shows a great deal more hot emission as the $\mathrm{EM}$ curves in the left panel of \autoref{fig:single_em} extend well above $10^7$ K while those in the left panel of \autoref{fig:ion_em} show a steep cutoff at temperatures just above the peak.
	%
	\begin{figure*}
		\centering
		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_single_heating_dem}.pdf}
			\label{fig:single_em_curves}}
		\end{minipage}
		%
		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_single_heating_hs_compare}.pdf}
			\label{fig:single_em_slopes}}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_single_heating_dem_derivs}.pdf}
			\label{fig:single_em_derivs}}
		\end{minipage}
		\caption{Same as \autoref{fig:el_em}, but for the single-fluid case in which electron-ion equilibrium is assumed.}
		\label{fig:single_em}
	\end{figure*}
	%
	\subsection{Non-equilibrium Ionization}
	\label{subsec:non-eq_ion}
	%
	\begin{figure*}
		\centering
		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{teff_electron_profiles}.pdf}
			\label{fig:teff_el_em}}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{teff_ion_profiles}.pdf}
			\label{fig:teff_ion_em}}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{teff_single_profiles}.pdf}
			\label{fig:teff_single_em}}
		\end{minipage}
		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{teff_electron_em}.pdf}
			\label{fig:teff_el_derivs}}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{teff_ion_em}.pdf}
			\label{fig:teff_ion_derivs}}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{teff_single_em}.pdf}
			\label{fig:teff_single_derivs}}
		\end{minipage}
			\caption{Non-equilibrium ionization $T$ (solid), $T_{eff}$ (dashed) and $n$ (dot-dashed), profiles (\textbf{left column}) and  $\mathrm{EM}$ distributions (\textbf{right column}) for electron heating (\textbf{top row}), ion heating (\textbf{middle row}), and the single-fluid case (\textbf{bottom row}). In all cases, $L=40$ Mm and the loop is subject to a single pulse of energy $Q\approx10^{25}$ erg with a duration of $\tau_H=100$ s. The values printed on the $\mathrm{EM}$ plots are the resulting emission measure slopes for the cool (blue) and hot (red) slopes for the cases of $\mathrm{EM}$ and $\mathrm{EM}_{eff}$.}
			\label{fig:teff_test_case}
	\end{figure*}
	%
	\par As mentioned in \autoref{sec:intro}, NEI can make it difficult to observe emission signatures from nanoflare-heated plasma because the heating timescale is shorter than the ionization timescale such that the charge state of the plasma is not representative of the plasma temperature. In order to diagnose how NEI might affect hot emission measure slopes, we use $n$ and $T_e$ profiles from our modified EBTEL code along with the method outlined by \citet{bradshaw_numerical_2009} to compute $T_{eff}$, the temperature that would be measured based on the actual ionization states. An effective emission measure distribution, $\mathrm{EM}_{eff}$, can then be calculated. Following \citetalias{barnes_inference_2016}, we use iron (Fe) and the ionization states Fe IX through FeXXV.
	%
	\par As the calculation of $T_{eff}$ is significantly more expensive than an EBTEL calculation, we do not compute $\mathrm{EM}_{eff}$ for the entire parameter space and instead consider only a small number of single-pulse test cases of duration $\tau_H=100$ s and peak heating rate $H_0=0.8$ erg cm$^{-3}$ s$^{-1}$. \autoref{fig:teff_test_case} shows temperature and density profiles (left column)  and emission measure distributions (right column) for the cases where NEI is (dashed) and is not (solid) included. These profiles are computed for all preferentially-heated species (electron, ion, single-fluid). For all three species, we note that including NEI in the calculation of the cool slope makes essentially no difference .
	%
	\par As in \autoref{fig:ion_em}, we do not compute the hot slope for the case of ion heating. Looking at the right panel in the middle row of \autoref{fig:teff_test_case}, we see that the inclusion of NEI in the case of ion heating has little to no effect on the emission measure. This is confirmed by the left panel of the middle row which shows that the difference between $T$ and $T_{eff}$ is relatively small and only occurs at low densities. Conversely, in the single-fluid and electron-heating cases, $T$ and $T_{eff}$ differ greatly during the heating phase and NEI has two distinct effects on the $\mathrm{EM}$: it leads to an overestimation of the amount of emission in the mid-range hot temperatures ($7.0\lesssim\log{T}\lesssim7.2$) and causes a steeper cutoff in the emission at lower temperatures (before $\log{T}\approx7.25$) compared to the case where NEI is not included. Interestingly, in both the electron-heating (first row) and single-fluid (third row) cases, $b_{eff}<b$ though we note that in the electron-heating case (first row), a power-law fit does not adequately describe the hot side of the $\mathrm{EM}$ distribution.
	%
	\subsection{Full Parameter Space Comparison}
	\label{subsec:all_params}
	%
	\begin{figure*}
		\centering
		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{el_cool_alpha_histo}.pdf}
			\label{fig:el_cool_alpha_histo}}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{el_hot_tn_histo}.pdf}
			\label{fig:el_hot_tn_histo}}
		\end{minipage}
		\begin{minipage}[c]{0.49\textwidth}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{ion_cool_alpha_histo}.pdf}
			\label{fig:ion_cool_alpha_histo}}
			\subfigure{%
			\includegraphics[width=\columnwidth]{figures/{single_hot_tn_histo}.pdf}
			\label{fig:single_cool_tn_histo}}
		\end{minipage}
			\caption{Histograms of emission measure slopes from the entire parameter space as described in \autoref{fig:parameter_space}. \textbf{Top left:} cool slopes grouped by heating function for the electron heating case; \textbf{Top right:} cool slopes grouped by heating function for the ion heating case; \textbf{Bottom left:} hot slopes grouped by $t_N$ for the electron heating case; \textbf{Bottom right:} hot slopes grouped by $t_N$ value for the single-fluid case. In the cases where the slopes are grouped by $t_N$, only $T_N=1000,2000,3000,4000,5000$ s are shown for aesthetic purposes.}
			\label{fig:histos}
	\end{figure*}
	%
	\par To compare the effects of varying $\alpha$, $\beta$, and $t_N$ for each species (i.e. electron, ion, single-fluid), we construct histograms of hot and cool emission measure slopes for each parameter space point. Recall that in the case where the distributions of heating event energies are non-uniform, we have $N_{R}$ emission measure slopes to properly account for the statistical spread in hot emission measure slopes due to power-law distributions.
	%
	\par As seen in \autoref{fig:histos}, these histograms, denoted by type of slope (i.e. hot or cool) and species, are constructed in one of two ways: each distinct histogram (denoted by linestyle and/or color) is either representative of a distinct heating function (e.g. top row of \autoref{fig:histos}) or a distinct value of $t_N$ (e.g. bottom row of \autoref{fig:histos}). In the four panels of \autoref{fig:histos}, we choose to separate the cool emission measure slopes by type of heating function and the hot emission measure slopes by $t_N$. This means, for example, that the dot-dashed blue $\alpha=-1.5,\beta=1$ histogram in the upper left panel of \autoref{fig:histos} encapsulates cool emission measure slopes for $250\le T_N\le5000$ s while the solid blue $T_N=2000$ s histogram in the lower left panel includes emission measure slopes for all 10 types of heating functions (as listed in \autoref{fig:parameter_space} and the legend in the upper left panel of \autoref{fig:histos}). All histograms are normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$. Additionally, the bin widths are calculated using the well-known Freedman-Diaconis formula \citep{freedman_histogram_1981}.
	%
	\par Concerning the distributions of cool slopes grouped by type of heating function (bottom row of \autoref{fig:histos}), we note that there are no discernible differences between the cases of electron and ion heating. In both cases, all heating functions except for those where $\beta=1$ are peaked sharply between 2 and 2.5. In the case where $\beta=1$ (for all $\alpha$), the distribution is peaked between 2.5 and 3, with the width of the distribution increasing as $\alpha$ steepens. This larger range of cool emission measure slopes for the case of $\beta=1$ is consistent with \citet{cargill_active_2014}.
	%
	\par As stated in \autoref{subsec:electron_ion_heating}, we choose not to show the hot emission measure slopes for the ion heating case as they are not representative of the emission measure distribution hotward of the peak as evidenced by the left and bottom right panels of \autoref{fig:ion_em}. Instead, we compare the hot emission measure slopes of the electron heating and single-fluid cases, the bottom left and bottom right panels of \autoref{fig:histos}, respectively. In both cases, for $T_N<3000$ s, we see a strong dependence on $t_N$ while for $T_N\ge3000$ s, the slopes tend to be sharply peaked around a single value. In the electron heating case, distributions for $T_N<3000$ s tend to be more narrow than their single-fluid counterparts and centered at lower values (i.e. more shallow hot slopes). Most notably, for $T_N\ge4000$ s, the electron heating hot emission measure slopes are peaked between 3 and 3.5 while the single-fluid slopes are peaked at $\sim4.5$. 
	%
	\section{Discussion}
	\label{sec:discussion}
	%
	\par The main points we emphasize from the results presented in \autoref{sec:results} are,
	\begin{enumerate}
		\item Cool emission measure slopes resulting from electron and ion heating are very similar and are well described by $\mathrm{EM}\propto T^a$. As noted in \citet{cargill_active_2014}, using the relation $Q\propto T_N^{\beta}$ yields $2\lesssim a\lesssim5$, consistent with observations.\label{itm:cool}
		\item Hot emission from electron heating results in an enhanced hot shoulder while the equivalent ion heating cases show a relatively flat peak and a steep dropoff near $10^7$ K. This effect is exacerbated as $t_N$ increases.\label{itm:hot}
		\item Hot emission due to both electron and ion heating is poorly described by the scaling $\mathrm{EM}\propto T^{-b}$. In the former, this is due to the flat hot shoulder between $10^7$ and $10^{7.5}$ K. In the latter case, the relatively flat peak and steep drop off near $10^7$ K do not allow for a power-law description of the hot emission.\label{itm:deriv}
		\item Using a power-law to describe the hot side of the $\mathrm{EM}$ distribution, single-fluid models predict less hot-emission than two-fluid models in which only the electrons are heated. In particular, for $T_N\ge4000$ s, our modified two-fluid EBTEL model predicts $3\le b\le3.5$ while the original single-fluid EBTEL model predicts $b\sim4.5$.\label{itm:histos}
		\item Including NEI does not impact the cool emission measure slope. In the case of electron heating and the single-fluid case, NEI enhances the mid-range hot $\mathrm{EM}$, but leads to a lower temperature cutoff. The emission measure distribution in the case of ion heating is unaffected. \label{itm:nei}
	\end{enumerate}
	%
	\par We first focus on \autoref{itm:cool}. In the range $6.0\le\log{T}\le6.6$, the loop is undergoing both radiative and enthalpy-driven cooling. During this phase, the density is high and the temperature low relative to the heating and conductive cooling phase. Looking at the fourth term on the right-hand side of \autoref{eq:press_e} and \autoref{eq:col_freq}, the coupling term between the two species is roughly $\propto\bar{n}^2(\bar{T}_e-\bar{T}_i)/\bar{T}_e^{3/2}$; as density increases, so does the coupling strength. While the loop is also draining in this temperature range, the density has already increased such that $\bar{T}_e\approx\bar{T}_i$ and until the next heating event, there is nothing to drive the two species out of equilibrium. Thus, because the two-species are evolving together in this regime, we expect their emission measure distributions to be the same.
	%
	\par In \autoref{itm:hot}, we see quite the opposite situation. In the heating and conductive cooling phases, the density is relatively low and the electron (or ion) temperature relatively high. Because the heating pulses we have used are relatively short (100 s), the heated species quickly reaches high temperatures and cools significantly by thermal conduction before Coulomb collisions can bring the two species back into equilibrium. Since the emission measure depends on the electron temperature, this means that in the event that only the electrons are heated, the emission  ``sees'' the full range of temperatures produced by heating and conductive cooling.
	%
	\begin{figure}[t]
		\centering
		\includegraphics[width=\columnwidth]{figures/ion_ts_compare.pdf}
		\caption{Single triangular heating pulse with duration $\tau_H=100$ s and total energy $Q\approx10^{25}$ erg injected into only the ions in a loop of half-length $L=40$ Mm. \textbf{Top:} Ion temperature, electron temperature, and coronal number density. \textbf{Bottom:} Ion thermal conduction $(\tau_{C,i})$ and Coulomb collision $(\tau_{ei})$ timescales. The dotted black line at 100 s marks the end of the heating pulse.}
		\label{fig:ion_ts}
	\end{figure}
	%
	\par However, in the case of ion heating, in order for the emission measure to see the full range of temperatures resulting from the heating and conductive cooling by the ions, $\bar{T}_e=\bar{T}_i$ would have to hold for this entire phase. Instead, as the ions are impulsively heated, the electrons remain at a relatively low temperature, coupled only weakly to the ions because the loop has only just begun to fill. As the coronal density increases, the electrons come into equilibrium with the ions, but because thermal conduction is such an efficient cooling mechanism in the corona, the ions have now cooled far below the temperature to which they were initially heated. 
	\par This scenario is clearly illustrated by \autoref{fig:ion_ts}. In this test case, we have impulsively heated the ions with a triangular pulse lasting 100 s with total energy $10^{25}$ erg. In the top panel, we see that by the time the electrons come into equilibrium with the ions, the ions have cooled well below their peak temperature and the loop has just begun to fill. Additionally, the bottom panel shows that during the period in which the ions are at their hottest temperatures, $\tau_{C,i}\ll\tau_{ei}$, where $\tau_{C,i}$ is the ion thermal conduction timescale. Thus, while they are being heated, the ions are giving up nearly all of their energy to thermal conduction before they reach equilibrium with the electrons.
	\par The result is a severely truncated hot emission measure distribution as seen in \autoref{fig:ion_em}. Additionally, this effect is exacerbated at long $t_N$. For short $t_N$, the heating is essentially steady, meaning that the loop has little to no time to drain or cool between heating events. This keeps the density at a roughly constant, near-equilibrium value which inhibits rapid heating to high temperatures and keeps the electrons and ions in equilibrium. However, for longer $t_N$, the loop is allowed to drain significantly between each pulse. Thus, at the start of each heating event, the density is low, allowing the species to very quickly evolve out of equilibrium. 
	%
	\begin{figure}
		\centering
		\includegraphics[width=\columnwidth]{figures/{electron_ts_compare}.pdf}
		\label{fig:electron_ts}
		\caption{ Comparison between Coulomb collision timescale $\tau_{ei}$ and electron thermal conduction timescale $\tau_{C,e}$ for the single-pulse example shown in the top row of \autoref{fig:teff_test_case}. The vertical dotted line marks the end of the heating period.}
	\end{figure}
	\begin{figure}
		\includegraphics[width=\columnwidth]{figures/{electron_single_nt_compare}.pdf}
		\label{fig:ss_em}
		\caption{$n-T$ state space diagram for the single-pulse examples in \autoref{fig:teff_test_case}. In the cases of electron and ion heating, only $T_e$ is shown. The corresponding $\mathrm{EM}$ distributions are overlaid in red.}
	\end{figure}
	%
	\par To address \autoref{itm:deriv} and \autoref{itm:histos}, we note that the hot sides of the electron heating $\mathrm{EM}$ distributions in \autoref{fig:el_em} have two distinct phases at long $t_N$: the $\mathrm{EM}$ drops off steeply (compared to the single-fluid case) just after the peak and then there is a pronounced hot shoulder near $\log{T}\sim7.3$. These features are missing in the single-fluid case (\autoref{fig:single_em}) where the $\mathrm{EM}$ is nearly linear (in $\log{\mathrm{EM}},\log{T}$) hotward of the peak until the sharp cutoff near $\log{T}\sim7.4$. This is emphasized in the single-pulse $\mathrm{EM}$ distributions for electron heating, ion heating, and the single-fluid case in \autoref{fig:ss_em}. 
	%
	\par Recalling $\mathrm{EM}\sim n^2\tau_{cool}$, the steeper drop in the electron heating $\mathrm{EM}$ just after the peak indicates accelerated cooling relative to the single-fluid case. We attribute this additional cooling to the Coulomb coupling between the electron and ion populations. As seen in the top panel of \autoref{fig:electron_ts}, near $t=100$ s where the heating turns off, the Coulomb collision and thermal conduction timescales are comparable, meaning that conductive cooling is being assisted as the hotter electrons give up energy to the cooler ions. This enhanced cooling can be seen in the much steeper, negative slope in $T$ just after the heating ends in the electron heating $\mathrm{EM}$ distribution (solid) in \autoref{fig:ss_em} as compared to the single-fluid $\mathrm{EM}$ distribution (dot-dashed).
	%
	\par Regarding the hot shoulder at very high $T$ in the case of electron heating, we again refer to \autoref{fig:ss_em}. We note that the hot shoulder region is coincident in $T$ with the portion of the state space where the density is greater in the electron heating case than in the single-fluid case. Thus, the hot shoulder is a result of the loop filling faster in the case of electron heating such that more emission is deposited at these high temperatures. This extra hot emission consequently decreases the hot emission measure slope as calculated by our power-law fit even though the slope just hotward of the peak is steep relative to the single-fluid case.
	%
	\par In the case of ion heating, the emission measure never sees much of the high temperature ($>10^7$ K) regime because the ions have cooled significantly by thermal conduction before they reach equilibrium with the electrons (as illustrated by \autoref{fig:ion_ts}). However, looking at \autoref{fig:ss_em}, we note that for the mid-range hot temperatures just hotward of the peak, the emission due to ion heating exceeds that due to electron heating, tracking closely with the single-fluid case until the sharp cutoff just above $10^7$ K. The cooling in this case is determined entirely by thermal conduction and is not enhanced by Coulomb coupling. This is because, in the case of ion heating, for the early heating phases, Coulomb coupling is a source term and then becomes negligible as the electron and ion populations reach equilibrium.
	%
	\par Finally, \autoref{itm:nei} addresses the fact that NEI does not affect cool emission or emission due to ion heating, while it acts to enhance mid-range hot temperature emission and creates a lower-temperature cutoff in the single-fluid and electron heating cases as shown in \autoref{fig:teff_test_case}. As discussed in \citetalias{barnes_inference_2016} and \autoref{sec:intro}, if the heating occurs on a timescale faster than the ionization equilibration timescale, high temperatures will not be detectable because the charge states indicative of such temperatures will not have had time to form. Coolward emission is due to radiative and enthalpy-driven cooling and during this phase, the density is relatively high and the temperature is changing relatively slowly, meaning that ionization equilibrium can be assumed. 
	\par For hotward emission in the case of ion heating, we note that the effective heating timescale for the electrons is approximately $\tau_{ei}$, the coupling timescale. As seen in \autoref{fig:ion_ts}, for $Q\approx10^{25}$ erg, the electron temperature increases relatively slowly (compared to the heating timescale of the ions) and only gets above several MK once the density has increased significantly. Thus, ionization equilibrium can be assumed because the electrons undergo no direct impulsive heating. In the cases of electron heating and the single-fluid case, the electrons undergo direct impulsive heating when the density is relatively low. This is what leads to the lower-temperature cutoff in $EM_{eff}$: at these high temperatures and low densities, the ionization equilibration timescale is significantly longer than the heating timescale and so these very high temperatures are never seen. 
	%
	\par However, looking at the left panels in the first and third rows of \autoref{fig:teff_test_case}, we see that just after the heating ends at 100 s, $T_{eff}>T$ due to the fact that the thermal conduction timescale is shorter than the ionization equilibration timescale. This lag in the charge state due to the efficiency of thermal conduction leads to the mid-range hot temperature emission enhancement seen in the right panels of the first and third rows of \autoref{fig:teff_test_case}. 
	%
	\section{Conclusions}
	\label{sec:conclusions}
	%
	\par In this paper, we have used a modified two-fluid version of the popular EBTEL model to study the effect of preferentially heating the electrons or ions on the hot and cool emission measure slopes over a parameter space that includes the power-law index describing the distribution of event energies, $\alpha$, waiting time between successive heating events, $t_N$, and the scaling between the event energy and wait time, $\beta$. We have found that while there is little difference in the cool emission between the cases of electron and ion heating, the emission measure curves of the electron-heated loops have an enhanced hot shoulder due to faster loop filling times and steepened hot mid-range slope due to accelerated cooling by the Coulomb collisions while the ion-heated loops show a truncated emission measure distribution on the hot side. These differences become more prominent as $t_N$ increases. We note that given such a distinction in the $\mathrm{EM}$ distribution between the cases of electron and ion heating, the difference could be potentially observationally diagnosable by instruments such as MaGIXS, the Focusing Optics X-ray Solar Imager (FOXSI) \citep{krucker_focusing_2011}, or other future missions with adequate spectroscopic resolution in the hard X-rays.
	\par Furthermore, by comparing these results with emission measure distributions obtained from the original single-fluid EBTEL model, we have found that heating only the electrons and using a single power-law fit leads to significantly smaller hot emission measure slopes for equivalent values of $t_N$. Thus, using a single-fluid model to interpret observed hot emission measure distributions can potentially lead to a misdiagnosis of the heating frequency. Additionally, characterizing the hotward emission with a single power-law fit, as is common practice with cool emission, does not adequately capture all of the features of the hotward emission.
	%
	\par We note that in this study, we have constructed the most ideal emission measure curves by using the expression $\mathrm{EM}=n^2(2L)$; that is, we have not taken into account the many complications involved when computing emission measure distributions from observed spectral lines. For example, as we noted in \citetalias{barnes_inference_2016}, impulsive heating leads to NEI and a consequently lower effective temperature, meaning that the emission does not see the hottest temperatures during the conductive cooling phase. By computing test cases for electron heating, ion heating, and the single-fluid case, we have shown that NEI has the effect of steepening the hot emission measure distribution at very high temperatures and enhancing the mid-range hot temperature emission for the electron heating and single-fluid cases, but has no impact on the emission measure distribution in the case of ion heating. We stress that when interpreting observed hot emission in the context of simulation, two-fluid and non-equilibrium ionization effects should be properly taken into account in order to extract meaningful properties of the heating.
	%
	\section*{Acknowledgment}
	%
	All of the data analysis shown in this work was carried out using the IPython system for interactive scientific computing in Python as well as the NumPy and Scipy numerical and scientific Python libraries \citep{perez_ipython:_2007,van_der_walt_numpy_2011}. All plots were produced using the Matplotlib graphics environment \citep{hunter_matplotlib:_2007}.
	%
	%
	%Bibliography
	\bibliography{astrophys-abbrev.bib,references.bib}
	\bibliographystyle{apj}
	\clearpage
\end{document}

### 2016-03-25 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
removing outdated figures; heavy editing, cutting out some sections

@@
 	%
+	\par Several workers have modeled both steady and impulsive heating in coronal loops. 
+	%
 	\par Despite these difficulties, various attempts have been made to observe this faint high-temperature emission.
@@
 	%
-	\par One strategy for constraining the nanoflare model is analysis of modeled and observed emission measure distributions for signatures of impulsive heating in active region cores.
+	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release.
+Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating.
+In the case of high-frequency heating, $t_N$, the time between successive events, is such that $t_N\ll\tau_c$, where $\tau_c$ is the loop cooling time, and in the case of low-frequency heating $t_N\gg\tau_c$.
+Steady heating is just high-frequency heating in the limit $t_N\to0$.
+	%
+	\par One strategy for constraining the nanoflare model is analysis of modeled and observed emission measure distributions for signatures of impulsive heating in active region (AR) cores.
 As with cool emission, hot emission is also often described by a power-law relation of the form $\mathrm{EM}\propto T^{-b}$.
@@
 However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range.
-\citet{warren_systematic_2012}, using spectral measurements from EIS, provided hotward fits for $\mathrm{EM}$ reconstructions for a large number of active regions.
+\citet{warren_systematic_2012}, using spectral measurements from EIS, provided hotward fits for $\mathrm{EM}$ reconstructions for a large number of ARs.
 All measured slopes fell in the range $6.1<b<10.3$, with large uncertainties on each hotward fit.
 	%
-	\par An often overlooked consequence of impulsive heating in the corona is electron-ion non-equilibrium.
+	\par\hl{Cut, repeat of Paper 1} An often overlooked consequence of impulsive heating in the corona is electron-ion non-equilibrium.
 In a fully-ionized hydrogen plasma like the solar corona, interactions between electrons and ions are governed by binary Coulomb collisions.
@@
 	%
-	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares and nanoflare trains.
-In this second paper in our series on hot emission in active region cores, we use an efficient two-fluid hydrodynamic model to explore the effect of electron and ion heating on nanoflare-heated loops.
+	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares.
+In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of electron and ion heating on nanoflare-heated loops.
 In particular, we look at how the hot emission is affected by heating preferentially one species or the other as well as how this hot emission can vary with heating frequency and the power-law index that determines the event energy distribution.
@@
 	%%
-	where $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency and $\psi_{TR}$ is a term included to maintain charge and current and neutrality and is defined in the appendix of \citetalias{barnes_inference_2016}.
+	where $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency and $\psi_{TR}$ is a term included to maintain charge and current and neutrality.
 These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$.
+A full discrussion and derivation of these 0D two-fluid equations can be found in the appendix of \citetalias{barnes_inference_2016}.
 	%
@@
 Note that $(3~\alpha~\mathrm{values})\times(3~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 10 different types of heating functions.
-\hl{Adjust depending on what value of $\beta$ we use in the end.}}
+\hl{Adjust depending on what value of $\beta$ we use in the end.	}}
 		\label{fig:parameter_space}
@@
 	%
-	\par Recent observations have suggested that loops in active region cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}.
+	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}.
 Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim4.5\times10^{-3}$.
@@
 Note that if $H_i=H_0$ for all $i$, the uniform heating rate $H_0$ is $H_0=2t_{total}H_{eq}/N\tau$.
-Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the total amount of energy injected into the loop by one heating event for a loop heated by $N=20$ nanoflares in $t_{tot}=80000$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx7.2\times10^{24}$ erg, consistent with the energy budget of the Parker nanoflare model.
+Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the total amount of energy injected into the loop by one heating event for a loop heated by $N=20$ nanoflares in $t_{tot}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx7.2\times10^{24}$ erg, consistent with the energy budget of the Parker nanoflare model.
 	%
-	\par Determining the heating frequency in active region cores will help to place constraints on the source(s) of heat in the corona.
+	\par Determining the heating frequency in AR cores will help to place constraints on the source(s) of heat in the corona.
 We define the heating frequency in terms of the waiting time, $t_N$, between successive heating events.
-Following \citet{cargill_active_2014}, the range of waiting times is $250\le T_N\le5000$ s in increments of 250 s, for a total of 20 different possible heating frequencies.
-Additionally, $t_N$ can be written as $T_N=(T-N\tau_H)/N$, where we fix $T=80000$ s.
-Note that because $T$ and $\tau_H$ are fixed, as $t_N$ increases, $N$ decreases.
-Correspondingly, $Q_i$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant, regardless of $t_N$.
+Following \citet{cargill_active_2014}, the range of waiting times is $250\le t_N\le5000$ s in increments of 250 s, for a total of 20 different possible heating frequencies.
+Additionally, $t_N$ can be written as $t_N=(t_{total}-N\tau)/N$, where we fix $T=8\times10^4$ s.
+Note that because $t_{total}$ and $\tau$ are fixed, as $t_N$ increases, $N$ decreases.
+Correspondingly, $\varepsilon_i$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant, regardless of $t_N$.
 	%
@@
 		\includegraphics[width=\columnwidth]{figures/heating_functions.pdf}
-		\caption{\textbf{Top left}: uniform heating amplitudes for $T_N=1000$ s; \textbf{Top right:} uniform heating amplitudes for $T_N=5000$ s; \textbf{Bottom left:} power-law distributed heating amplitudes for $\alpha=-1.5$, $T_N=2000$ s; \textbf{Bottom right:} power-law distributed amplitudes for $\alpha=-1.5$ where the wait times depend on the event energies and the mean wait time for both values of $\beta$ is $\langle T_N\rangle=2000$ s.\hl{Adjust depending on what $\beta$ we use in the end.}}
+		\caption{\textbf{Top}: uniform heating amplitudes for $t_N=1000$ s; \textbf{Middle:} uniform heating amplitudes for $t_N=5000$ s; \textbf{Bottom:} Heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$.
+The events shown in red have wait times that depend on the previous event energy while the events shown in blue have uniform wait times.
+The mean wait time in both cases is $\langle T_N\rangle=2000$ s.}
 		\label{fig:heating_funcs}
+	\end{figure}
+%
+	%
+	\begin{figure}
+		\centering
+		\includegraphics[width=\columnwidth]{figures/heating_event_distributions.pdf}
+		\caption{Power-law distributions of heating events for indices $\alpha=-1.5,-2.0,-2.5$ for a given heating frequency, $t_N=2500$ s.
+For each frequency, $t_N$, we compute $N_R$ runs such that the total number of events simulated for each $t_N$ is $N\times N_R\sim10^4$.}
+		\label{fig:event_dist}
 	\end{figure}
@@
 Bursty, nanoflare heating is thought to arise from the stressing and subsequent relaxation of the coronal field.
-If a sufficient amount of time has elapsed since the last energy release event, the field will have had enough time to ``wind up'' such that the subsequent energy release is large.
-Conversely, if only a small amount of time has elapsed since the last event, the field will have not had time to become as stressed, resulting in a lower energy event.
+If a sufficient amount of energy is released into the loop, the field will need enough time to ``unravel'' and ``wind up'' again before the next event such that the subsequent waiting time is large.
+Conversely, if only a small amount of energy is released, the field will require a shorter unwinding time, resulting in a shorter interval between the subsequent events.
 Thus, this scaling provides a way to incorporate a more physically motivated heating function into a hydrodynamic model which cannot self-consistently determine the heat input based on the evolving magnetic field.
@@
 	\par We compute the peak heating rate per event in two different ways: 1) the heating rate is uniform such that $H_i=H_0$ for all $i$ and 2) $H_i$ is chosen from a power-law distribution with index $\alpha$ where $\alpha=-1.5,-2.0,$ or $-2.5$.
-For the second case, it should be noted that, when $T_N\approx5000$ s, $N\sim20$ events, meaning a single run does not accurately represent the distribution of index $\alpha$.
+For the second case, it should be noted that, when $t_N\approx5000$ s, $N\sim20$ events, meaning a single run does not accurately represent the distribution of index $\alpha$.
 Thus, a sufficiently large number of runs, $N_{R}$, are computed for each $t_N$ to ensure that the total number of events is $N_{tot}=N\times N_{R}\sim10^4$ such that the distribution is well-represented.
 \autoref{fig:parameter_space} shows the parameter space we will explore.
-For each set of parameters and waiting time $t_N$, we compute the resulting emission measure distribution for $N$ events in a period $T$.
+For each set of parameters and waiting time $t_N$, we compute the resulting emission measure distribution for $N$ events in a period $t_{total}$.
 This procedure is repeated $N_R$ times until $N\times N_R\sim10^4$ is satisfied.
@@
 We consider a temperature range of $4.0\le\log{T}\le8.5$ with bin sizes of $\Delta\log{T}=0.01$.
-At each iteration $i$, the coronal temperature range $[T_0,T_a]$ is calculated from $\bar{T}_e$ (see \autoref{appendix}).
+At each iteration $i$, the coronal temperature range $[T_0,T_a]$ is calculated from $\bar{T}_e$.
 For each bin that falls within $[T_0,T_a]$, $\bar{n}_i^2(2L)$ is added to that bin, where $\bar{n}_i$ is the spatially-averaged number density at iteration $i$.
@@
 	\par We first briefly consider the calculated cool emission measure slopes.
-Looking at the top right panels of \autoref{fig:el_em} and \autoref{fig:ion_em}, we note that in the cases of electron and ion heating, the cool emission measure slopes are consistent with both observational and modeling studies of cool emission in active region cores, having values that fall within the range $2\le a\le5$ \citep[and references therein]{bradshaw_diagnosing_2012}.
+Looking at the top right panels of \autoref{fig:el_em} and \autoref{fig:ion_em}, we note that in the cases of electron and ion heating, the cool emission measure slopes are consistent with both observational and modeling studies of cool emission in AR cores, having values that fall within the range $2\le a\le5$ \citep[and references therein]{bradshaw_diagnosing_2012}.
 Furthermore, the cool slopes computed using our new modified EBTEL model, with a heating function of the form $Q\propto T_N^{\beta}$, are consistent with those values reported in \citet{cargill_active_2014} and show a dependence on the waiting time $t_N$.
@@
 		\begin{minipage}[c]{0.49\textwidth}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{teff_electron_profiles}.pdf}
-			\label{fig:teff_el_em}}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{teff_ion_profiles}.pdf}
-			\label{fig:teff_ion_em}}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{teff_single_profiles}.pdf}
-			\label{fig:teff_single_em}}
 		\end{minipage}
 		\begin{minipage}[c]{0.49\textwidth}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{teff_electron_em}.pdf}
-			\label{fig:teff_el_derivs}}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{teff_ion_em}.pdf}
-			\label{fig:teff_ion_derivs}}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{teff_single_em}.pdf}
-			\label{fig:teff_single_derivs}}
 		\end{minipage}
-			\caption{Non-equilibrium ionization $T$ (solid), $T_{eff}$ (dashed) and $n$ (dot-dashed), profiles (\textbf{left column}) and  $\mathrm{EM}$ distributions (\textbf{right column}) for electron heating (\textbf{top row}), ion heating (\textbf{middle row}), and the single-fluid case (\textbf{bottom row}).
-In all cases, $L=40$ Mm and the loop is subject to a single pulse of energy $Q\approx10^{25}$ erg with a duration of $\tau_H=100$ s.
-The values printed on the $\mathrm{EM}$ plots are the resulting emission measure slopes for the cool (blue) and hot (red) slopes for the cases of $\mathrm{EM}$ and $\mathrm{EM}_{eff}$.}
+			\caption{Figures for the cases of non-equilibrium ionization.}
 			\label{fig:teff_test_case}
@@
 	%
-	\begin{figure}[t]
-		\centering
-		\includegraphics[width=\columnwidth]{figures/ion_ts_compare.pdf}
-		\caption{Single triangular heating pulse with duration $\tau_H=100$ s and total energy $Q\approx10^{25}$ erg injected into only the ions in a loop of half-length $L=40$ Mm.
-\textbf{Top:} Ion temperature, electron temperature, and coronal number density.
-\textbf{Bottom:} Ion thermal conduction $(\tau_{C,i})$ and Coulomb collision $(\tau_{ei})$ timescales.
-The dotted black line at 100 s marks the end of the heating pulse.}
-		\label{fig:ion_ts}
-	\end{figure}
-	%
 	\par However, in the case of ion heating, in order for the emission measure to see the full range of temperatures resulting from the heating and conductive cooling by the ions, $\bar{T}_e=\bar{T}_i$ would have to hold for this entire phase.
@@
 As the coronal density increases, the electrons come into equilibrium with the ions, but because thermal conduction is such an efficient cooling mechanism in the corona, the ions have now cooled far below the temperature to which they were initially heated.
-	\par This scenario is clearly illustrated by \autoref{fig:ion_ts}.
-In this test case, we have impulsively heated the ions with a triangular pulse lasting 100 s with total energy $10^{25}$ erg.
-In the top panel, we see that by the time the electrons come into equilibrium with the ions, the ions have cooled well below their peak temperature and the loop has just begun to fill.
-Additionally, the bottom panel shows that during the period in which the ions are at their hottest temperatures, $\tau_{C,i}\ll\tau_{ei}$, where $\tau_{C,i}$ is the ion thermal conduction timescale.
-Thus, while they are being heated, the ions are giving up nearly all of their energy to thermal conduction before they reach equilibrium with the electrons.
 	\par The result is a severely truncated hot emission measure distribution as seen in \autoref{fig:ion_em}.
@@
 	%
-	\begin{figure}
-		\centering
-		\includegraphics[width=\columnwidth]{figures/{electron_ts_compare}.pdf}
-		\label{fig:electron_ts}
-		\caption{ Comparison between Coulomb collision timescale $\tau_{ei}$ and electron thermal conduction timescale $\tau_{C,e}$ for the single-pulse example shown in the top row of \autoref{fig:teff_test_case}.
-The vertical dotted line marks the end of the heating period.}
-	\end{figure}
-	\begin{figure}
-		\includegraphics[width=\columnwidth]{figures/{electron_single_nt_compare}.pdf}
-		\label{fig:ss_em}
-		\caption{$n-T$ state space diagram for the single-pulse examples in \autoref{fig:teff_test_case}.
-In the cases of electron and ion heating, only $T_e$ is shown.
-The corresponding $\mathrm{EM}$ distributions are overlaid in red.}
-	\end{figure}
-	%
-	\par To address \autoref{itm:deriv} and \autoref{itm:histos}, we note that the hot sides of the electron heating $\mathrm{EM}$ distributions in \autoref{fig:el_em} have two distinct phases at long $t_N$: the $\mathrm{EM}$ drops off steeply (compared to the single-fluid case) just after the peak and then there is a pronounced hot shoulder near $\log{T}\sim7.3$.
-These features are missing in the single-fluid case (\autoref{fig:single_em}) where the $\mathrm{EM}$ is nearly linear (in $\log{\mathrm{EM}},\log{T}$) hotward of the peak until the sharp cutoff near $\log{T}\sim7.4$.
-This is emphasized in the single-pulse $\mathrm{EM}$ distributions for electron heating, ion heating, and the single-fluid case in \autoref{fig:ss_em}.
-	%
-	\par Recalling $\mathrm{EM}\sim n^2\tau_{cool}$, the steeper drop in the electron heating $\mathrm{EM}$ just after the peak indicates accelerated cooling relative to the single-fluid case.
-We attribute this additional cooling to the Coulomb coupling between the electron and ion populations.
-As seen in the top panel of \autoref{fig:electron_ts}, near $t=100$ s where the heating turns off, the Coulomb collision and thermal conduction timescales are comparable, meaning that conductive cooling is being assisted as the hotter electrons give up energy to the cooler ions.
-This enhanced cooling can be seen in the much steeper, negative slope in $T$ just after the heating ends in the electron heating $\mathrm{EM}$ distribution (solid) in \autoref{fig:ss_em} as compared to the single-fluid $\mathrm{EM}$ distribution (dot-dashed).
-	%
-	\par Regarding the hot shoulder at very high $T$ in the case of electron heating, we again refer to \autoref{fig:ss_em}.
-We note that the hot shoulder region is coincident in $T$ with the portion of the state space where the density is greater in the electron heating case than in the single-fluid case.
-Thus, the hot shoulder is a result of the loop filling faster in the case of electron heating such that more emission is deposited at these high temperatures.
-This extra hot emission consequently decreases the hot emission measure slope as calculated by our power-law fit even though the slope just hotward of the peak is steep relative to the single-fluid case.
-	%
-	\par In the case of ion heating, the emission measure never sees much of the high temperature ($>10^7$ K) regime because the ions have cooled significantly by thermal conduction before they reach equilibrium with the electrons (as illustrated by \autoref{fig:ion_ts}).
-However, looking at \autoref{fig:ss_em}, we note that for the mid-range hot temperatures just hotward of the peak, the emission due to ion heating exceeds that due to electron heating, tracking closely with the single-fluid case until the sharp cutoff just above $10^7$ K.
-The cooling in this case is determined entirely by thermal conduction and is not enhanced by Coulomb coupling.
-This is because, in the case of ion heating, for the early heating phases, Coulomb coupling is a source term and then becomes negligible as the electron and ion populations reach equilibrium.
-	%
 	\par Finally, \autoref{itm:nei} addresses the fact that NEI does not affect cool emission or emission due to ion heating, while it acts to enhance mid-range hot temperature emission and creates a lower-temperature cutoff in the single-fluid and electron heating cases as shown in \autoref{fig:teff_test_case}.
@@
 	\par For hotward emission in the case of ion heating, we note that the effective heating timescale for the electrons is approximately $\tau_{ei}$, the coupling timescale.
-As seen in \autoref{fig:ion_ts}, for $Q\approx10^{25}$ erg, the electron temperature increases relatively slowly (compared to the heating timescale of the ions) and only gets above several MK once the density has increased significantly.
+For $Q\approx10^{25}$ erg, the electron temperature increases relatively slowly (compared to the heating timescale of the ions) and only gets above several MK once the density has increased significantly.
 Thus, ionization equilibrium can be assumed because the electrons undergo no direct impulsive heating.
@@
 	%
-	All of the data analysis shown in this work was carried out using the IPython system for interactive scientific computing in Python as well as the NumPy and Scipy numerical and scientific Python libraries \citep{perez_ipython:_2007,van_der_walt_numpy_2011}.
+	\hl{Move this to results eventually.} All of the data analysis shown in this work was carried out using the IPython system for interactive scientific computing in Python as well as the NumPy and Scipy numerical and scientific Python libraries \citep{perez_ipython:_2007,van_der_walt_numpy_2011}.
 All plots were produced using the Matplotlib graphics environment \citep{hunter_matplotlib:_2007}.

### 2016-03-25 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
outline changes, correcting heating stats section, adding figures, correcting figures

@@
 	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares.
-In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of electron and ion heating on nanoflare-heated loops.
-In particular, we look at how the hot emission is affected by heating preferentially one species or the other as well as how this hot emission can vary with heating frequency and the power-law index that determines the event energy distribution.
-Additionally, we consider how NEI may affect hot emission measure slopes in the cases of electron and ion heating as well as the single-fluid case.
+In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of repeated impulsive heating events of varying frequency.
+In particular, we look at how the hot emission is affected by heating preferentially the electrons or the ions with events drawn from a power-law distribution.
+Additionally, we consider the effect of scaling the inter-event waiting time to the event energy and  how NEI may affect hot emission measure slopes.
 	%
@@
 $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent.
-Note that $(3~\alpha~\mathrm{values})\times(3~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 10 different types of heating functions.
+Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions.
 \hl{Adjust depending on what value of $\beta$ we use in the end.	}}
@@
 The events shown in red have wait times that depend on the previous event energy while the events shown in blue have uniform wait times.
-The mean wait time in both cases is $\langle T_N\rangle=2000$ s.}
+The mean wait time in both cases is $\langle t_N\rangle=2000$ s.}
 		\label{fig:heating_funcs}
@@
 		\includegraphics[width=\columnwidth]{figures/heating_event_distributions.pdf}
-		\caption{Power-law distributions of heating events for indices $\alpha=-1.5,-2.0,-2.5$ for a given heating frequency, $t_N=2500$ s.
+		\caption{Power-law distributions of heating events for indices $\alpha=-1.5,-2.0,-2.5$ for a given heating frequency, $t_N=5000$ s.
 For each frequency, $t_N$, we compute $N_R$ runs such that the total number of events simulated for each $t_N$ is $N\times N_R\sim10^4$.}

### 2016-03-25 hot_non-flaring_plasma_2/parameter_space_graphic.tex
outline changes, correcting heating stats section, adding figures, correcting figures

	\begin{tikzpicture}[node distance=2cm]
		%Draw the nodes
		\node (species) [ghost] {$\Sigma=\left\{
		\begin{array}{l}
			\mathrm{electron} \\
			\mathrm{ion} \\
			\mathrm{single}
		\end{array}
		\right.$};
		\node (ghost_ph) [ghost, below of=species] {};
		\node (alpha_pl) [ghost, left of=ghost_ph] {$\alpha=\left\{
		\begin{array}{l}
			-1.5 \\
			-2.0 \\
			-2.5
		\end{array}
		\right.$};
		\node (alpha_uni) [ghost, right of=ghost_ph] {uniform};
		\node (ghost_beta) [ghost, below of=alpha_pl]{};
		\node (beta_1) [ghost, right of=ghost_beta] {$\beta=1$};
		\node (beta_0) [ghost, left of=ghost_beta] {$\beta=0$};
		%Draw the arrows
		\draw [arrow] (species) -- (alpha_pl);
		\draw [arrow] (species) -- (alpha_uni);
		\draw [arrow] (alpha_pl) -- (beta_0);
		\draw [arrow] (alpha_pl) -- (beta_1);
		%\draw [arrow] (alpha_pl) -- (beta_2);	
	\end{tikzpicture}

### 2016-04-05 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
removing old figures and includes

@@
 	%
-	\par\hl{Cut, repeat of Paper 1} An often overlooked consequence of impulsive heating in the corona is electron-ion non-equilibrium.
-In a fully-ionized hydrogen plasma like the solar corona, interactions between electrons and ions are governed by binary Coulomb collisions.
-For $n\sim10^9~\mathrm{cm}^{-3}$ and $T\sim10^7~\mathrm{K}$, parameters typical of nanoflare heating, the collisional timescale, $\tau_{ei}=1/\nu_{ei}$, where $\nu_{ei}$ is the Coulomb collision frequency (see \autoref{eq:col_freq}) can be estimated as $\tau_{ei}\approx800$ s.
-Thus, any heating that occurs on a timescale less than 800 s, such as a nanoflare with a duration of $\tau_H\le100$ s, will result in electron-ion non-equilibrium.
-Chromospheric evaporation, the response from the transition region to the strong coronal heat flux, does lead to an increase in $n$ and thus a decrease in $\tau_{ei}$.
-However, we maintain that during this initial phase of impulsive heating, $\tau_{ei}\gg\tau_H$ still holds, with 800 s being an approximate upper bound on $\tau_{ei}$.
-	%
-	\par Additionally, while it is often assumed that the electrons are the direct recipients of the prescribed heating function, the degree to which the ions or electrons are preferentially heated in the solar corona is unknown.
-Thus, it is possible that the ions are preferentially heated, for instance, through ion-cyclotron wave resonances \citep{markovskii_intermittent_2004}.
-Ion cyclotron waves are excited by plasma instabilities in the lower corona.
-These waves then propagate upwards through the coronal plasma and wave particle interactions can occur for those ions whose gyrofrequencies have a resonance with the ion-cyclotron wave.
-Additionally, there is also evidence for ion heating via reconnection, both in laboratory plasmas and in particle-in-cell simulations \citep{ono_ion_1996,yoo_bulk_2014,drake_onset_2014}.
-Thus, ion heating in the solar corona should not be discounted as a possibility.
-	%
 	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares.
@@
 %
-	%
-	\begin{figure}
-		\centering
-		\includegraphics[width=\columnwidth]{figures/heating_event_distributions.pdf}
-		\caption{Power-law distributions of heating events for indices $\alpha=-1.5,-2.0,-2.5$ for a given heating frequency, $t_N=5000$ s.
-For each frequency, $t_N$, we compute $N_R$ runs such that the total number of events simulated for each $t_N$ is $N\times N_R\sim10^4$.}
-		\label{fig:event_dist}
-	\end{figure}
-%
 	\par According to the nanoflare heating model of \citet{parker_nanoflares_1988}, turbulent loop footpoint motions twist and stress the field, leading to a buildup and subsequent release of energy.
@@
 	\subsection{Heating Statistics}
-	\label{subsec:em_dist}
-	%
+	\label{subsec:heating_stats}
 	%
@@
 	%
+	\subsection{Non-equilibrium Ionization}
+	\label{subsec:nei}
+	%%
+	\par When considering the role of nanoflares in the production of hot plasma in AR cores, it is important to take non-equilibrium ionization (NEI) into account \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008}.
+In a steady heating scenario, the ionization state is an adequate measure of the electron plasma temperature.
+Because the heating timescale is long (effectively infinite), the ionization state has plenty of time to come into equilibrium with the electron temperature.
+	%
+	\par In a nanoflare train, when the heating frequency is high, the loop is not allowed to drain or cool sufficiently between events, meaning the ionization state is kept at or near equilibrium.
+However, as the heating frequency decreases, the loop is allowed to cool and drain more and more during the inter-event period.
+If the heating occurs on a short enough timescale, the ionization state will not be able to reach equilibrium with the electron plasma before the loop undergoes rapid cooling by thermal conduction.
+Furthermore, if the frequency is sufficiently low so as to allow the loop to drain during the inter-event period, the ionization equilibrium timescale will increase.
+Thus, in the context of intermediate- to low-frequency nanoflares, NEI should be considered.
+	%
+	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: https://github.com/rice-solar-physics/IonPopSolver} outlined in \citet{bradshaw_numerical_2009} to compute the non-equilibrium ionization states and the corresponding effective electron temperature, $T_{eff}$ that would be inferred by assuming ionization equilibrium.
+Using $T_eff$, we are then able to compute a corresponding NEI emission measure distribution.
+	%%
 	\section{Results}
@@
 	%
-	\subsection{Separate Electron and Ion Heating}
-	\label{subsec:electron_ion_heating}
+	\subsection{Emission Measure Distributions}
+	\label{subsec:em_dist}
 	%
@@
 		\centering
-		\begin{minipage}[c]{0.49\textwidth}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_electron_heating_dem}.pdf}
-			\label{fig:el_em_curves}}
-		\end{minipage}
-		%
-		\begin{minipage}[c]{0.49\textwidth}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_electron_heating_hs_compare}.pdf}
-			\label{fig:el_em_slopes}}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_electron_heating_dem_derivs}.pdf}
-			\label{fig:el_em_derivs}}
-		\end{minipage}
-		\caption{$\alpha=-2.5,~\beta=1,~L=40$ Mm, electron heating.
-\textbf{Left:} $\log{\mathrm{EM}}$ as a function of $\log{T}$ for all values of $t_N$.
-There is an artificial spacing of $\Delta\log{\mathrm{EM}}=0.2$ between each curve.
-The bold blue (red) lines on either side of the peak show the linear fit to the cool (hot) emission.
-\textbf{Top right:} Average slopes from power-law fits to all $N_{R}$ curves as a function of $t_N$.
-The error bars indicate one standard deviation from the distribution of $N_{R}$ fits.
-In the case of hot slopes, the absolute value is shown.
-The dashed, solid, and dot-dashed reference lines are placed at 2, 3, and 5 respectively.
-\textbf{Bottom right:} Derivative of $\log{\mathrm{EM}}$ with respect to $\log{T}$.
-The dotted reference lines are placed at -5.5, -2.5, 2, and 3.
-The legend is the same as the left panel.}
+		\caption{EM grids will go here, electron heating}
 		\label{fig:el_em}
@@
 		\centering
-		\begin{minipage}[c]{0.49\textwidth}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_ion_heating_dem}.pdf}
-			\label{fig:ion_em_curves}}
-		\end{minipage}
-		%
-		\begin{minipage}[c]{0.49\textwidth}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_ion_heating_hs_compare}.pdf}
-			\label{fig:ion_em_slopes}}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_ion_heating_dem_derivs}.pdf}
-			\label{fig:ion_em_derivs}}
-		\end{minipage}
-		\caption{Same as \autoref{fig:el_em}, but for the case in which all of the heating is given to the ions.}
+		\caption{EM grids will go here, ion heating}
 		\label{fig:ion_em}
@@
 	%
-	\subsection{Single-fluid}
-	\label{subsec:single_heating}
+	\subsection{Pre-nanoflare Density}
+	\label{subsec:pre_nanoflare_density}
 	%
@@
 		\centering
-		\begin{minipage}[c]{0.49\textwidth}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_single_heating_dem}.pdf}
-			\label{fig:single_em_curves}}
-		\end{minipage}
-		%
-		\begin{minipage}[c]{0.49\textwidth}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_single_heating_hs_compare}.pdf}
-			\label{fig:single_em_slopes}}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{ebtel_L40.0_tpulse100.0_alpha2.5-b1.0_single_heating_dem_derivs}.pdf}
-			\label{fig:single_em_derivs}}
-		\end{minipage}
-		\caption{Same as \autoref{fig:el_em}, but for the single-fluid case in which electron-ion equilibrium is assumed.}
-		\label{fig:single_em}
+		\caption{\hl{Maybe single EM grid will go here}}
 	\end{figure*}
 	%
-	\subsection{Non-equilibrium Ionization}
-	\label{subsec:non-eq_ion}
+	\subsection{Hot Plasma Diagnostics}
+	\label{subsec:diagnostics}
 	%
@@
 		\centering
-		\begin{minipage}[c]{0.49\textwidth}
-		\end{minipage}
-		\begin{minipage}[c]{0.49\textwidth}
-		\end{minipage}
-			\caption{Figures for the cases of non-equilibrium ionization.}
-			\label{fig:teff_test_case}
+		\caption{Diagnostics figures}
 	\end{figure*}
@@
 	%
-	\subsection{Full Parameter Space Comparison}
-	\label{subsec:all_params}
+	%\subsection{Full Parameter Space Comparison}
+	%\label{subsec:all_params}
 	%
@@
 		\centering
-		\begin{minipage}[c]{0.49\textwidth}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{el_cool_alpha_histo}.pdf}
-			\label{fig:el_cool_alpha_histo}}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{el_hot_tn_histo}.pdf}
-			\label{fig:el_hot_tn_histo}}
-		\end{minipage}
-		\begin{minipage}[c]{0.49\textwidth}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{ion_cool_alpha_histo}.pdf}
-			\label{fig:ion_cool_alpha_histo}}
-			\subfigure{%
-			\includegraphics[width=\columnwidth]{figures/{single_hot_tn_histo}.pdf}
-			\label{fig:single_cool_tn_histo}}
-		\end{minipage}
-			\caption{Histograms of emission measure slopes from the entire parameter space as described in \autoref{fig:parameter_space}.
-\textbf{Top left:} cool slopes grouped by heating function for the electron heating case; \textbf{Top right:} cool slopes grouped by heating function for the ion heating case; \textbf{Bottom left:} hot slopes grouped by $t_N$ for the electron heating case; \textbf{Bottom right:} hot slopes grouped by $t_N$ value for the single-fluid case.
-In the cases where the slopes are grouped by $t_N$, only $T_N=1000,2000,3000,4000,5000$ s are shown for aesthetic purposes.}
+		\caption{\hl{Put EM ratio histograms here, maybe include hot slope histograms somewhere too}}
 			\label{fig:histos}

### 2016-04-11 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
more planning/outline,updates to results section, figure captions

@@
 	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares.
-In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of repeated impulsive heating events of varying frequency.
-In particular, we look at how the hot emission is affected by heating preferentially the electrons or the ions with events drawn from a power-law distribution.
+In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of repeated impulsive heating events of varying frequency on the resulting emission measure distribution.
+In particular, we look at how the hot emission is affected by heating preferentially the electrons or the ions with events drawn from a power-law distribution versus uniform heating rates.
 Additionally, we consider the effect of scaling the inter-event waiting time to the event energy and how NEI may affect hot emission measure slopes.
-	%
-	\par\autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated.
-\autoref{sec:results} shows the resulting emission measure curves and slopes for the electron and ion heating cases as well as the equivalent single-fluid cases.
-In \autoref{sec:discussion}, we discuss the implications of two-fluid effects in the context of hot and cool emission measure slopes and the nanoflare heating model.
+We use an emission measure ratio, similar to that of \citet{brosius_pervasive_2014} to assess the relative importance of hot emission over the entire range of power-law indices and heating frequencies.
+\autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated.
+\autoref{sec:results} shows the resulting emission measure curves and slopes for the electron and ion heating cases \st{as well as the equivalent single-fluid cases}.
+In \autoref{sec:discussion}, we discuss the implications of two-fluid effects in the context of hot \st{and cool} emission measure slopes and the nanoflare heating model.
 Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.
@@
 However, because of the small cell sizes needed to resolve the transition region and consequently small timesteps demanded by thermal conduction, the use of such models in large parameter space explorations is made impractical by long computational runtimes \citep{bradshaw_influence_2013}.
-We use the popular 0D enthalpy-based thermal evolution of loops (EBTEL) model \citep{klimchuk_highly_2008,cargill_enthalpy-based_2012,cargill_enthalpy-based_2012-1,cargill_modelling_2015}.
+We use the popular 0D enthalpy-based thermal evolution of loops (EBTEL) model \citep{klimchuk_highly_2008,cargill_enthalpy-based_2012,cargill_enthalpy-based_2012-1,cargill_modelling_2015} in order to efficiently simulate the evolution of a coronal loop over a large parameter space.
 This model, which has been successfully benchmarked against the 1D hydrodynamic HYDRAD code of \citet{bradshaw_influence_2013}, computes, with very low computational overhead, time-dependent, spatially-averaged loop quantities.
@@
 	%%
-	where $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency and $\psi_{TR}$ is a term included to maintain charge and current and neutrality.
+	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency and $\psi_{TR}$ is a term included to maintain charge and current and neutrality.
 These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$.
-A full discrussion and derivation of these 0D two-fluid equations can be found in the appendix of \citetalias{barnes_inference_2016}.
-	%
-	\par\hl{Include some temperature and density profiles for nanoflare trains in here somehow? May need to move to next section...}
 	%
@@
 	\label{subsec:params}
-	%
-	\par\hl{Details about static parameters for all runs.} All events are modeled as triangular pulses of fixed duration $\tau=200$ s.
 	%
@@
 Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions.
-\hl{Adjust depending on what value of $\beta$ we use in the end.	}}
+\hl{Are we going to look at the single-fluid case?
+If not, remove if here and reconsider total number of heating functions.}}
 		\label{fig:parameter_space}
@@
 Following \citet{cargill_active_2014}, the range of waiting times is $250\le t_N\le5000$ s in increments of 250 s, for a total of 20 different possible heating frequencies.
-Additionally, $t_N$ can be written as $t_N=(t_{total}-N\tau)/N$, where we fix $T=8\times10^4$ s.
+Additionally, $t_N$ can be written as $t_N=(t_{total}-N\tau)/N$, where we fix $T=8\times10^4$ s and $\tau=200$ s.
 Note that because $t_{total}$ and $\tau$ are fixed, as $t_N$ increases, $N$ decreases.
@@
 	\par According to the nanoflare heating model of \citet{parker_nanoflares_1988}, turbulent loop footpoint motions twist and stress the field, leading to a buildup and subsequent release of energy.
-Following \citet{cargill_active_2014}, we let $\varepsilon_i\propto t_{N,i}^{\beta}$, where $\varepsilon_i,t_{N,i}$ are the total energy and waiting time following event $i$, respectively, and $\beta=1,2$ such that the event energy scales either linearly or quadratically with the waiting time.
+Following \citet{cargill_active_2014}, we let $\varepsilon_i\propto t_{N,i}^{\beta}$, where $\varepsilon_i,t_{N,i}$ are the total energy and waiting time following event $i$, respectively, and $\beta=1$ such that the event energy scales linearly with the waiting time.
 The reasoning for such an expression is as follows.
@@
 	%
+	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (electron or ion ), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$).
+	%
 	\par In our 0D model, the emission measure is calculated using the familiar expression $\mathrm{EM}=n^2(2L)$, where $L$ is the loop half-length.
@@
 ratio of loop length to loop width) of 10, we apply a correction factor 1/10 to all calculated $\mathrm{EM}$ curves.
-We do not attempt to apply an advanced forward modeling treatment here and instead reserve such an approach for a future paper.
-However, while effects due to NEI are neglected in our parameter space exploration, in \autoref{subsec:non-eq_ion} we consider the emission measure due to $T_{eff}$, the effective temperature due to NEI, for several test cases in order to diagnose how this might affect our calculated emission measure slopes.
+Furthermore, for each of the $N_R$ runs per $t_N$ value, we also compute the corresponding effective emission measure distribution, $\mathrm{EM}(T_{eff})$.
 	%
-	\par For each species, type of power-law heating function, and waiting time $t_N$, $N_{R}$ emission measure curves are calculated.
-Because drawing event amplitudes from a power-law distribution introduces random fluctuations into our model, we must be sure to account for the full range of effects due to the distribution.
-This is especially true in the low-frequency regime, when $T_N\ge\tau_{cool}$, the cooling timescale, and there are fewer events per run.
-In this case, one or two especially strong heating events can lead to an extremely enhanced hotward emission measure; conversely, a run with only small events will lead to a diminished hotward slope.
-Thus, the mean $\mathrm{EM}$ curve of each set of $N_{R}$ runs can be said to reasonably represent the expected hot emission for a given $t_N$.
-	%
-	\par To characterize the emission measure, we compute the slopes on both the cool and hot sides of the peak.
+	%\par To characterize the emission measure, we compute the slopes on both the cool and hot sides of the peak.
 To be consistent with past observational and computational studies of cool emission \citep[see][and references therein]{bradshaw_diagnosing_2012}, we fit the cool slope on the interval $6.0\le\log{T}\le6.6$.
@@
 		\centering
-		\caption{EM grids will go here, electron heating}
+		\includegraphics[width=2\columnwidth]{figures/em_grid_electron_a25.pdf}
+		\caption{Emission measure distributions for varying waiting-times, $t_N$ in the case where only the electrons are heated.
+The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (blue).
+The dotted lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}
 		\label{fig:el_em}
@@
 		\centering
-		\caption{EM grids will go here, ion heating}
+		\includegraphics[width=2\columnwidth]{figures/em_grid_ion_a25.pdf}
+		\caption{Same as \autoref{fig:el_em}, but for the case where only the ions are heated.}
 		\label{fig:ion_em}
@@
 	%
+	\begin{figure*}
+		\centering
+		\includegraphics[width=2\columnwidth]{figures/nT_sample_curves_tn1500_electron.pdf}
+		\caption{Example temperature and density profiles for an intermediate heating frequency, $t_N=1500$ s for several different heating function types.}
+	\end{figure*}
+	%
 	\par \autoref{fig:single_em} shows the same results as \autoref{fig:el_em} and \autoref{fig:ion_em}, but for the single-fluid case in which electron-ion equilibrium is assumed at all times.
@@
 	%
+	\subsection{Hot Plasma Diagnostics}
+	\label{subsec:diagnostics}
+	%%
 	\begin{figure*}
 		\centering
-		\caption{\hl{Maybe single EM grid will go here}}
+		\subfigure[]{%
+		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_electron_T0.pdf}
+		}
+		\subfigure[]{%
+		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_electron_T0.pdf}
+		}
+		\caption{Electron heating emission measure ratio for an EIS/MaGIXS line pair}
 	\end{figure*}
-	%
-	\subsection{Hot Plasma Diagnostics}
-	\label{subsec:diagnostics}
-	%
+	%%
 	\begin{figure*}
 		\centering
+		\subfigure[]{%
+		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_ion_T0.pdf}
+		}
+		\subfigure[]{%
+		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_ion_T0.pdf}
+		}
 		\caption{Diagnostics figures}
 	\end{figure*}
-	%
+	%%
 	\par As mentioned in \autoref{sec:intro}, NEI can make it difficult to observe emission signatures from nanoflare-heated plasma because the heating timescale is shorter than the ionization timescale such that the charge state of the plasma is not representative of the plasma temperature.
@@
 Interestingly, in both the electron-heating (first row) and single-fluid (third row) cases, $b_{eff}<b$ though we note that in the electron-heating case (first row), a power-law fit does not adequately describe the hot side of the $\mathrm{EM}$ distribution.
-	%
-	%\subsection{Full Parameter Space Comparison}
-	%\label{subsec:all_params}
-	%
-	\begin{figure*}
-		\centering
-		\caption{\hl{Put EM ratio histograms here, maybe include hot slope histograms somewhere too}}
-			\label{fig:histos}
-	\end{figure*}
 	%

### 2016-04-14 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
updating results section with descriptions, captions for new figures

@@
 Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim4.5\times10^{-3}$.
-In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored.
-Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by
+\hl{In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored.} Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by
 	\begin{equation}
@@
 	\par We compute the peak heating rate per event in two different ways: 1) the heating rate is uniform such that $H_i=H_0$ for all $i$ and 2) $H_i$ is chosen from a power-law distribution with index $\alpha$ where $\alpha=-1.5,-2.0,$ or $-2.5$.
-For the second case, it should be noted that, when $t_N\approx5000$ s, $N\sim20$ events, meaning a single run does not accurately represent the distribution of index $\alpha$.
+For the second case, it should be noted that, when $t_N\approx5000$ s, $N\sim16$ events, meaning the events from a single run do not accurately represent the distribution of index $\alpha$.
 Thus, a sufficiently large number of runs, $N_{R}$, are computed for each $t_N$ to ensure that the total number of events is $N_{tot}=N\times N_{R}\sim10^4$ such that the distribution is well-represented.
@@
 This procedure is repeated $N_R$ times until $N\times N_R\sim10^4$ is satisfied.
+Thus, when $t_N=5000$ s and $N\sim15$, $N_R=625$, meaning the model is run 625 times with a heating frequency of $t_N=5000$ s in order to properly fill out the event energy distribution.
 	%
@@
 	%
-	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: https://github.com/rice-solar-physics/IonPopSolver} outlined in \citet{bradshaw_numerical_2009} to compute the non-equilibrium ionization states and the corresponding effective electron temperature, $T_{eff}$ that would be inferred by assuming ionization equilibrium.
+	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to compute the non-equilibrium ionization states and the corresponding effective electron temperature, $T_{eff}$ that would be inferred by assuming ionization equilibrium.
 Using $T_eff$, we are then able to compute a corresponding NEI emission measure distribution.
@@
 	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (electron or ion ), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$).
+All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}.
+All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.
 	%
-	\par In our 0D model, the emission measure is calculated using the familiar expression $\mathrm{EM}=n^2(2L)$, where $L$ is the loop half-length.
+	\par In order to compactly summarize all of the data in each run of our model, we calculate the resulting emission measure distribution using the familiar expression $\mathrm{EM}=n^2(2L)$, where $L$ is the loop half-length.
 We consider a temperature range of $4.0\le\log{T}\le8.5$ with bin sizes of $\Delta\log{T}=0.01$.
 At each iteration $i$, the coronal temperature range $[T_0,T_a]$ is calculated from $\bar{T}_e$.
-For each bin that falls within $[T_0,T_a]$, $\bar{n}_i^2(2L)$ is added to that bin, where $\bar{n}_i$ is the spatially-averaged number density at iteration $i$.
+For each bin that falls within $[T_0,T_a]$, $\bar{n}_i^2(2L)$ is added to that bin, where $\bar{n}_i$ is the spatially-averaged number density at time $t_i$.
 The emission measure in each bin is then averaged over the entire simulation period.
@@
 ratio of loop length to loop width) of 10, we apply a correction factor 1/10 to all calculated $\mathrm{EM}$ curves.
-Furthermore, for each of the $N_R$ runs per $t_N$ value, we also compute the corresponding effective emission measure distribution, $\mathrm{EM}(T_{eff})$.
+Furthermore, each emission measure distribution we also compute the corresponding effective emission measure distribution, $\mathrm{EM}(T_{eff})$, using $T_{eff}$, the effective temperature calculated by including effects due to NEI.
 	%
+	\par As noted in \autoref{subsec:heating_stats}, for each heating frequency $t_N$, we compute $N_R$ runs such that there are $N_R$ $\mathrm{EM}(T)$ distributions for each $t_N$.
+Thus, the $\mathrm{EM}(T)$ that we show for each $t_N$ is the average computed over all $N_R$ of these emission measure distributions.
 	%\par To characterize the emission measure, we compute the slopes on both the cool and hot sides of the peak.
@@
 		\caption{Emission measure distributions for varying waiting-times, $t_N$ in the case where only the electrons are heated.
-The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (blue).
+The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).
 The dotted lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}
@@
 	\end{figure*}
+	%
+	\par First, we look at the resulting emission measure distributions for the case in which only the electrons are heated.
+\autoref{fig:el_em} shows $\mathrm{EM}(T)$ for six different values of $t_N$ and three different types of heating functions: uniform heating events, events chosen from a power-law distribution of index $\alpha=-2.5$, and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event.
+The dotted lines in each frame show the corresponding emission measure distribution constructed from $T_{eff}$, $\mathrm{EM}(T_{eff})$.
+	%
+	\par As $t_N$ increases, $\mathrm{EM}$ is allowed to extend to both lower and 
 	%
@@
 	%
-	\hl{Move this to results eventually.} All of the data analysis shown in this work was carried out using the IPython system for interactive scientific computing in Python as well as the NumPy and Scipy numerical and scientific Python libraries \citep{perez_ipython:_2007,van_der_walt_numpy_2011}.
-All plots were produced using the Matplotlib graphics environment \citep{hunter_matplotlib:_2007}.
+	\hl{Acknowledge some things here.} 
 	%

### 2016-05-04 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
minor changes

@@
 However, the detection of such emission has proved difficult due to a combination of the efficiency of thermal conduction, non-equilibrium ionization, and inadequate instrument sensitivity.
-This second paper in our series on hot non-flaring plasma in active regions aims to show how the assumption of electron-ion equilibrium leads to misleading conclusions regarding the hot emission.
+In this second paper in our series on ``hot'' non-flaring plasma in active regions, we investigate the influence of repeating nanoflares of varying frequency on the resulting emission measure di .
 We have used an efficient two-fluid hydrodynamic model to carry out a parameter exploration in preferentially heated species, heating event frequency, and the power-law index determining the distribution of event energies.
@@
 		\caption{Total Parameter space covered.
-$\Sigma$ indicates the species that is heated, where ``single'' indicates a single-fluid model.
+``single'' indicates a single-fluid model.
 $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent.
@@
 	where $t_{total}$ is the total simulation time.
-Note that if $H_i=H_0$ for all $i$, the uniform heating rate $H_0$ is $H_0=2t_{total}H_{eq}/N\tau$.
+Note that if $H_i=H_0$ for all $i$, the uniform heating rate $H_0=2t_{total}H_{eq}/N\tau$.
 Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the total amount of energy injected into the loop by one heating event for a loop heated by $N=20$ nanoflares in $t_{tot}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx7.2\times10^{24}$ erg, consistent with the energy budget of the Parker nanoflare model.

### 2016-05-05 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
hot, cool slope sections in intro; still unsure about scope relative to P1

@@
 	\title{Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains}
+	\shorttitle{``Hot'' Non-flaring Plasmas II. Nanoflare Trains}
 	\author{W. T. Barnes}
@@
 	%
-	\par \citet{cargill_implications_1994} and \citet{cargill_nanoflare_2004} have predicted that emission measure distributions resulting from nanoflare models should be wide and have a faint, high-temperature (8-10 MK) component and thus a steep hotward slope, the so-called ``smoking gun'' of nanoflare heating.
+	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release.
+Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating.
+In the case of high-frequency heating, $\langle t_N\rangle$, the time between successive events, is such that $\langle t_N\rangle\ll\tau_{cool}$, where $\tau_{cool}$ is the loop cooling time, and in the case of low-frequency heating $\langle t_N\rangle\gg\tau_{cool}$ \citep{cargill_modelling_2015}.
+Steady heating is just high-frequency heating in the limit $\langle t_N\rangle\to0$.
+\hl{Discuss past heating frequency studies}
+	%
+	\par One strategy for constraining potential heating models is analysis of modeled and observed emission measure distributions in active region (AR) cores.
+Originally proposed by \citet{jordan_structure_1975}, it is well-known that the emission measure, $\mathrm{EM}(T)=\int n^2\mathrm{d}h$, scales as $\mathrm{EM}(T)\sim T^a$ over a temperature range $10^6\lesssim T\lesssim T_m$, where $T_m$ is the temperature at which $\mathrm{EM}(T)$ peaks.
+Observations have shown that $2\lesssim a\lesssim5$, with $T_m\approx10^{6.5-6.6}$ \citep{warren_constraints_2011,warren_systematic_2012,winebarger_using_2011,tripathi_emission_2011,schmelz_cold_2012,del_zanna_evolution_2015}.
+	%
+	\par Hydrodynamic models of nanoflare-heated loops have found similar results when calculating emission measure slopes.
+While \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$.
+\citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<\langle t_N\rangle<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the observed emission measure slopes be found.
+This is consistent with the findings of \citet{ugarte-urra_determining_2014} who estimated an inter-event period of 1400 s using an event detection algorithm on filtered SDO/AIA 94 \ang images of AR cores.
+\hl{Steady-heating counter arguments?}
+	%
+	\par\hl{Hot slope calculations, predictions} A similar scaling has been claimed for hot emission such that $\mathrm{EM}\propto T^{-b}$.
+Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $T_m\lesssim\log{T}\lesssim7.2$.
+However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}.
+\citet{warren_systematic_2012}, using spectral measurements from EIS, provided hotward fits for $\mathrm{EM}$ reconstructions for a large number of ARs.
+All measured slopes fell in the range $6.1<b<10.3$, with large uncertainties on each hotward fit.
+\hl{more refs here?
+Summarize in a sentence or two and provide many refs, don't want to repeat paper 1}
+	%
+	\par \citet{cargill_implications_1994,cargill_nanoflare_2004} have predicted that emission measure distributions resulting from nanoflare models should be wide and have a faint, high-temperature (8-10 MK) component and thus a steep hotward slope, the so-called ``smoking gun'' of nanoflare heating.
 Unfortunately, observing this high-temperature emission is difficult and in some cases impossible.
@@
 	%
-	\par The second reason for this difficulty is non-equilibrium ionization (NEI).
-It is usually assumed that the observed emission lines, because of their known formation temperatures, are a direct indicator of the plasma temperature.
-However, if the heating (or cooling) timescale is shorter than the ionization equilibration timescale, the time it takes for the ion population to settle into the assumed charge state, an equilibrium assumption can lead to a misdiagnosis of the plasma temperature.
-This makes signatures of hot, nanoflare-heated plasma especially difficult to detect if the high temperatures persist for less than the ionization timescale \citep{bradshaw_explosive_2006,bradshaw_what_2011,reale_nonequilibrium_2008}.
-	%
-	\par Several workers have modeled both steady and impulsive heating in coronal loops. 
-	%
-	\par Despite these difficulties, various attempts have been made to observe this faint high-temperature emission.
-Using the broadband X-Ray Telescope (XRT) \citep{golub_x-ray_2007} on board the \textit{Hinode} spacecraft \citep{kosugi_hinode_2007}, \citet{schmelz_hinode_2009} and \citet{reale_evidence_2009} show a faint hot component in the reconstructed $\mathrm{DEM}$ curves.
-However, since the channels on such broadband instruments can often be polluted by low-temperature emission, the reliability of such measurements depends on the filtering technique used.
-Additionally, \citet{winebarger_defining_2012} showed that combinations of measurements from XRT and the Extreme-ultraviolet Imaging Spectrometer (EIS) \citep{culhane_euv_2007}, also on  \textit{Hinode}, leave a ``blind spot'' in the $\mathrm{EM}-T$ space conincident with the range where evidence for nanoflare heating is likely to be found.
-	%
-	\par Unambiguous observational evidence of nanoflare heating must come from pure spectroscopic measurements \citep[see][]{brosius_pervasive_2014}.
-Additionally, new instruments with higher spatial and temporal resolution, such as \textit{IRIS} \citep{de_pontieu_interface_2014} and the \textit{Hi-C} sounding rocket \citep{cirtain_energy_2013} have provided encouraging results for impulsive heating \citep{testa_observing_2013,testa_evidence_2014}.
-Future missions like the Marshall Grazing Incidence X-ray Spectrometer (MaGIXS) \citep{kobayashi_marshall_2011,winebarger_new_2014}, with a wavelength range of 6-24 \ang and a temperature range of $6.2<\log{T}<7.2$, aim to probe this previously poorly-resolved portion of the coronal spectrum in hopes of better quantifying the presence of faint, high-temperature plasma.
-	%
-	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release.
-Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating.
-In the case of high-frequency heating, $t_N$, the time between successive events, is such that $t_N\ll\tau_c$, where $\tau_c$ is the loop cooling time, and in the case of low-frequency heating $t_N\gg\tau_c$.
-Steady heating is just high-frequency heating in the limit $t_N\to0$.
-	%
-	\par One strategy for constraining the nanoflare model is analysis of modeled and observed emission measure distributions for signatures of impulsive heating in active region (AR) cores.
-As with cool emission, hot emission is also often described by a power-law relation of the form $\mathrm{EM}\propto T^{-b}$.
-Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $6.6\lesssim\log{T}\lesssim7.2$.
-However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range.
-\citet{warren_systematic_2012}, using spectral measurements from EIS, provided hotward fits for $\mathrm{EM}$ reconstructions for a large number of ARs.
-All measured slopes fell in the range $6.1<b<10.3$, with large uncertainties on each hotward fit.
-	%
 	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares.
+We found that emission signatures of the heating are likely to be found in the temperature range $4\lesssim T\lesssim 10$ MK.
 In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of repeated impulsive heating events of varying frequency on the resulting emission measure distribution.

### 2016-05-09 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
updates to intro

@@
 	%
-	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release.
-Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating.
-In the case of high-frequency heating, $\langle t_N\rangle$, the time between successive events, is such that $\langle t_N\rangle\ll\tau_{cool}$, where $\tau_{cool}$ is the loop cooling time, and in the case of low-frequency heating $\langle t_N\rangle\gg\tau_{cool}$ \citep{cargill_modelling_2015}.
-Steady heating is just high-frequency heating in the limit $\langle t_N\rangle\to0$.
-\hl{Discuss past heating frequency studies}
+	\par \citet{cargill_implications_1994,cargill_nanoflare_2004} have predicted that emission measure distributions resulting from nanoflare models should be wide and have a faint, high-temperature (8-10 MK) component, the so-called ``smoking gun'' of nanoflare heating.
+Though many workers \citep{reale_evidence_2009,schmelz_hinode_2009,miceli_x-ray_2012,testa_hinode/eis_2012,del_zanna_elemental_2014,petralia_thermal_2014,schmelz_hot_2015} have claimed evidence of this hot, faint component of the emission measure, poor spectral resolution \citep{testa_temperature_2011,winebarger_defining_2012} and non-equilibrium ionization \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008} have made a positive detection of nanoflare heating difficult.
+However, \citet{brosius_pervasive_2014}, using obsservations from the \textit{EUNIS-13} sounding rocket, identified relatively faint emission from Fe XIX in a non-flaring active region (AR), suggesting temperatures of $\sim8.9$ MK.
 	%
@@
 	%
+	\par A similar scaling has been claimed for hot emission such that $\mathrm{EM}\propto T^{-b}$.
+Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $T_m\lesssim\log{T}\lesssim7.2$.
+However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}.
+\citet{warren_systematic_2012}, find $7\lesssim b\lesssim10$, with uncertainties of $\pm2.5-3$, for 15 AR cores thoguh \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$.
+	%
+	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release.
+Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating.
+In the case of high-frequency heating, $\langle t_N\rangle$, the time between successive events, is such that $\langle t_N\rangle\ll\tau_{cool}$, where $\tau_{cool}$ is the loop cooling time, and in the case of low-frequency heating $\langle t_N\rangle\gg\tau_{cool}$ \citep{cargill_modelling_2015}.
+Steady heating is just high-frequency heating in the limit $\langle t_N\rangle\to0$.
+\hl{Why heating frequency difficult?
+Need for modeling.}
+	%
 	\par Hydrodynamic models of nanoflare-heated loops have found similar results when calculating emission measure slopes.
 While \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$.
-\citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<\langle t_N\rangle<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the observed emission measure slopes be found.
-This is consistent with the findings of \citet{ugarte-urra_determining_2014} who estimated an inter-event period of 1400 s using an event detection algorithm on filtered SDO/AIA 94 \ang images of AR cores.
+\citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<\langle t_N\rangle<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the full range of observed emission measure slopes be found.
+This is consistent with the findings of \citet{ugarte-urra_determining_2014} who estimated an inter-event period of 1400 s from filtered SDO/AIA \citep{pesnell_solar_2012,lemen_atmospheric_2012} 94 \ang images of AR cores using an event detection algorithm.
 \hl{Steady-heating counter arguments?}
 	%
-	\par\hl{Hot slope calculations, predictions} A similar scaling has been claimed for hot emission such that $\mathrm{EM}\propto T^{-b}$.
-Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $T_m\lesssim\log{T}\lesssim7.2$.
-However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}.
-\citet{warren_systematic_2012}, using spectral measurements from EIS, provided hotward fits for $\mathrm{EM}$ reconstructions for a large number of ARs.
-All measured slopes fell in the range $6.1<b<10.3$, with large uncertainties on each hotward fit.
-\hl{more refs here?
-Summarize in a sentence or two and provide many refs, don't want to repeat paper 1}
-	%
-	\par \citet{cargill_implications_1994,cargill_nanoflare_2004} have predicted that emission measure distributions resulting from nanoflare models should be wide and have a faint, high-temperature (8-10 MK) component and thus a steep hotward slope, the so-called ``smoking gun'' of nanoflare heating.
-Unfortunately, observing this high-temperature emission is difficult and in some cases impossible.
-The reason for this difficulty is twofold.
-First, thermal conduction is a very efficient cooling mechanism at high temperatures and large spatial temperature gradients.
-When a loop is heated impulsively, its temperature rises quickly while the increase in density lags behind.
-By the time the density has increased sufficiently (due to chromospheric evaporation brought about by the response of the transition region to the strong downward coronal heat flux) to allow for an appreciable amount of emission (recalling $\mathrm{EM}\propto n^2$), thermal conduction has cooled the loop far below its initial hot temperature, making a direct detection of $\sim10$ MK plasma very difficult.
+	\par\hl{Heating frequency and emssion $T>T_m$}
 	%

### 2016-05-16 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
complete draft of intro, methods section; corrections to parameter space graphic

@@
 Steady heating is just high-frequency heating in the limit $\langle t_N\rangle\to0$.
-\hl{Why heating frequency difficult?
-Need for modeling.}
 	%
-	\par Hydrodynamic models of nanoflare-heated loops have found similar results when calculating emission measure slopes.
+	\par The frequency of energy release in the solar corona is an important piece of evidence for determining the yet unknown coronal heating mechanism(s).
+However, measurement of the heating frequency, through both direct and indirect means, has proved challenging.
+With regard to the direct evidence of reconnection-driven (DC) heating, only recently have observations provided sufficient resolution to resolve magnetic field braiding \citep{cirtain_energy_2013}, a supposed precursor to bursty energy release.
+Additionally, while the resulting AR core emission measure distribution holds many clues as to how the coronal plasma is heated and cools, reconstructing these $\mathrm{EM}$ from spectroscropic and narrow-band observations is non-trivial, with differrent inversion methods often giving significantly different results \citep{landi_monte_2012,aschwanden_benchmark_2015}.
+Efforts to measure the heating frequency through intensity fluctuations in AR cores have proved similarly difficult \citep{ugarte-urra_determining_2014}.
+	%
+	\par Hydrodynamic loop models, combined with sophisticated forward modeling, provide an accurate method for assessing a wide variety of heating scenarios and calculating observables.
+Such models of nanoflare-heated loops have found emission measure slopes consistent with those derived from observations.
 While \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$.
 \citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<\langle t_N\rangle<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the full range of observed emission measure slopes be found.
-This is consistent with the findings of \citet{ugarte-urra_determining_2014} who estimated an inter-event period of 1400 s from filtered SDO/AIA \citep{pesnell_solar_2012,lemen_atmospheric_2012} 94 \ang images of AR cores using an event detection algorithm.
-\hl{Steady-heating counter arguments?}
-	%
-	\par\hl{Heating frequency and emssion $T>T_m$}
 	%
@@
 We found that emission signatures of the heating are likely to be found in the temperature range $4\lesssim T\lesssim 10$ MK.
-In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of repeated impulsive heating events of varying frequency on the resulting emission measure distribution.
-In particular, we look at how the hot emission is affected by heating preferentially the electrons or the ions with events drawn from a power-law distribution versus uniform heating rates.
-Additionally, we consider the effect of scaling the inter-event waiting time to the event energy and how NEI may affect hot emission measure slopes.
-We use an emission measure ratio, similar to that of \citet{brosius_pervasive_2014} to assess the relative importance of hot emission over the entire range of power-law indices and heating frequencies.
+We now turn our attention to repeated impulsive events on a single strand.
+	%
+	\par In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of repeated impulsive heating events of varying frequency on the resulting $\mathrm{EM}(T)$.
+In particular, we look at how the hot emission is affected by heating preferentially the electrons or the ions, with events drawn from a power-law distribution versus uniform heating rates.
+Additionally, we investigate the effect of scaling the inter-event waiting time to the event energy and as well as how NEI may affect the presence of hot emission.
+We use an emission measure ratio, similar to that of \citet{brosius_pervasive_2014}, to assess the relative importance of hot emission over the entire range of power-law indices and heating frequencies.
 \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated.
-\autoref{sec:results} shows the resulting emission measure curves and slopes for the electron and ion heating cases \st{as well as the equivalent single-fluid cases}.
-In \autoref{sec:discussion}, we discuss the implications of two-fluid effects in the context of hot \st{and cool} emission measure slopes and the nanoflare heating model.
+\autoref{sec:results} shows the resulting emission measure distributions and diagnostics for the entire parameter space.
+In \autoref{sec:discussion}, we discuss the impacts of two-fluid effects, pre-nanoflare density, and NEI on these calculated observables and how they may be interpreted in the context of nanoflare heating.
 Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.

### 2016-05-16 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
updating pdf

@@
 Though many workers \citep{reale_evidence_2009,schmelz_hinode_2009,miceli_x-ray_2012,testa_hinode/eis_2012,del_zanna_elemental_2014,petralia_thermal_2014,schmelz_hot_2015} have claimed evidence of this hot, faint component of the emission measure, poor spectral resolution \citep{testa_temperature_2011,winebarger_defining_2012} and non-equilibrium ionization \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008} have made a positive detection of nanoflare heating difficult.
-However, \citet{brosius_pervasive_2014}, using obsservations from the \textit{EUNIS-13} sounding rocket, identified relatively faint emission from Fe XIX in a non-flaring active region (AR), suggesting temperatures of $\sim8.9$ MK.
+However, \citet{brosius_pervasive_2014}, using observations from the \textit{EUNIS-13} sounding rocket, identified relatively faint emission from Fe XIX in a non-flaring active region (AR), suggesting temperatures of $\sim8.9$ MK.
 	%
@@
 	\par A similar scaling has been claimed for hot emission such that $\mathrm{EM}\propto T^{-b}$.
-Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $T_m\lesssim\log{T}\lesssim7.2$.
+Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $T_m\lesssim T\lesssim10^{7.2}$.
 However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}.
-\citet{warren_systematic_2012}, find $7\lesssim b\lesssim10$, with uncertainties of $\pm2.5-3$, for 15 AR cores thoguh \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$.
+\citet{warren_systematic_2012}, find $7\lesssim b\lesssim10$, with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$.
 	%

### 2016-06-17 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
figure updates, minor text updates

@@
 These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$.
+In the cases where we treat the plasma as a single-fluid, we use the original EBTEL model as described in \citet{klimchuk_highly_2008,cargill_enthalpy-based_2012}.
+	%
+	\par The loop is heated by a prescribed heating function, applied to either the electrons ($\bar{Q}_e$) or the ions ($\bar{Q}_i$).
+Both species cool through a combination of thermal conduction ($F_{ce,0},\,F_{ci,0}$) and an enthalpy flux to the lower atmosphere, with the electrons also undergoing radiative cooling ($\mathcal{R_C}$).
+In the case of conductive cooling, a flux limiter, $F=(1/2)fnk_BTV_e$, is imposed to mitigate runaway cooling in a low-density, high-temperature plasma.
+In all cases we use a saturation limit of $f=1$.
+See \citetalias{barnes_inference_2016} for a discussion of how $f$ is likely to effect the presence of hot emission in a nanoflare-heated plasma.
 	%
@@
 		\centering
-		\include{parameter_space_graphic}
-		\caption{Total Parameter space covered.
-``single'' indicates a single-fluid model.
-$\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent.
-Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions.
-\hl{Are we going to look at the single-fluid case?
-If not, remove if here and reconsider total number of heating functions.}}
-		\label{fig:parameter_space}
+		\includegraphics[width=\columnwidth]{figures/heating_functions.pdf}
+		\caption{\textbf{Top}: uniform heating amplitudes for $t_N=1000$ s; \textbf{Middle:} uniform heating amplitudes for $t_N=5000$ s; \textbf{Bottom:} Heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$.
+The events shown in red have wait times that depend on the previous event energy while the events shown in blue have uniform wait times.
+The mean wait time in both cases is $\langle t_N\rangle=2000$ s.}
+		\label{fig:heating_funcs}
 	\end{figure}
@@
 	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}.
-Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim4.5\times10^{-3}$.
+Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim3.6\times10^{-3}$.
 \hl{In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored.} Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by
@@
 		\centering
-		\includegraphics[width=\columnwidth]{figures/heating_functions.pdf}
-		\caption{\textbf{Top}: uniform heating amplitudes for $t_N=1000$ s; \textbf{Middle:} uniform heating amplitudes for $t_N=5000$ s; \textbf{Bottom:} Heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$.
-The events shown in red have wait times that depend on the previous event energy while the events shown in blue have uniform wait times.
-The mean wait time in both cases is $\langle t_N\rangle=2000$ s.}
-		\label{fig:heating_funcs}
+		\include{parameter_space_graphic}
+		\caption{Total Parameter space covered.
+``single'' indicates a single-fluid model.
+$\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent.
+Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions.
+\hl{Are we going to look at the single-fluid case?
+If not, remove if here and reconsider total number of heating functions.}}
+		\label{fig:parameter_space}
 	\end{figure}
@@
 	%
-	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (electron or ion ), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$).
+	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$).
 All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}.
@@
 		\subfigure[]{%
-		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_electron_T0.pdf}
+		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_electron_T2.pdf}
 		}
 		\subfigure[]{%
-		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_electron_T0.pdf}
+		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_electron_T2.pdf}
 		}
@@
 		\subfigure[]{%
-		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_ion_T0.pdf}
+		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_ion_T2.pdf}
 		}
 		\subfigure[]{%
-		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_ion_T0.pdf}
+		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_ion_T2.pdf}
 		}

### 2016-06-23 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex

@@
 		\label{eq:heating_rate_constraint}
-		H_{eq} = \frac{1}{t_{total}}\sum_{i=1}^N\int_{t_i}^{t_i+\tau}\mathrm{d}t~h_i(t) = \frac{\tau}{2t_{total}}\sum_{i=1}^NH_i,
+		H_{eq} = \frac{1}{t_{total}}\sum_{i=1}^N\int_{t_i}^{t_i+\tau}\mathrm{d}t~Q(t) = \frac{\tau}{2t_{total}}\sum_{i=1}^NH_i,
 	\end{equation}
 	where $t_{total}$ is the total simulation time.
-Note that if $H_i=H_0$ for all $i$, the uniform heating rate $H_0=2t_{total}H_{eq}/N\tau$.
-Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the total amount of energy injected into the loop by one heating event for a loop heated by $N=20$ nanoflares in $t_{tot}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx7.2\times10^{24}$ erg, consistent with the energy budget of the Parker nanoflare model.
+Note that if $H_i=H_0$ for all $i$, the heating rate for each event is $H_i=H_0=2t_{total}H_{eq}/N\tau$.
+Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the average energy per event for a loop heated by $N=20$ nanoflares in $t_{total}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx5.8\times10^{24}$ erg, consistent with the energy budget of the Parker nanoflare model.
 	%
-	\par Determining the heating frequency in AR cores will help to place constraints on the source(s) of heat in the corona.
-We define the heating frequency in terms of the waiting time, $t_N$, between successive heating events.
+	\par We define the heating frequency in terms of the waiting time, $t_N$, between successive heating events.
 Following \citet{cargill_active_2014}, the range of waiting times is $250\le t_N\le5000$ s in increments of 250 s, for a total of 20 different possible heating frequencies.
-Additionally, $t_N$ can be written as $t_N=(t_{total}-N\tau)/N$, where we fix $T=8\times10^4$ s and $\tau=200$ s.
+Additionally, $t_N$ can be written as $t_N=(t_{total}-N\tau)/N$, where we fix $t_{total}=8\times10^4$ s and $\tau=200$ s.
 Note that because $t_{total}$ and $\tau$ are fixed, as $t_N$ increases, $N$ decreases.
-Correspondingly, $\varepsilon_i$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant, regardless of $t_N$.
+Correspondingly, $\varepsilon_i=LA\tau H_i/2$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant, independent of $t_N$.
 	%
@@
 	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$).
+In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s.
+The average interval between subsequent events is $t_N$ (in the uniform and power-law case, $t_N,i=t_N$ exactly for all $i$).
+We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$.
+In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016}.
+The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$.
 All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}.
 All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.
-	%
-	\par In order to compactly summarize all of the data in each run of our model, we calculate the resulting emission measure distribution using the familiar expression $\mathrm{EM}=n^2(2L)$, where $L$ is the loop half-length.
-We consider a temperature range of $4.0\le\log{T}\le8.5$ with bin sizes of $\Delta\log{T}=0.01$.
-At each iteration $i$, the coronal temperature range $[T_0,T_a]$ is calculated from $\bar{T}_e$.
-For each bin that falls within $[T_0,T_a]$, $\bar{n}_i^2(2L)$ is added to that bin, where $\bar{n}_i$ is the spatially-averaged number density at time $t_i$.
-The emission measure in each bin is then averaged over the entire simulation period.
-When measured observationally, $\mathrm{EM}(T)$ is a line-of-sight quantity.
-Assuming an aspect ratio (i.e.
-ratio of loop length to loop width) of 10, we apply a correction factor 1/10 to all calculated $\mathrm{EM}$ curves.
-Furthermore, each emission measure distribution we also compute the corresponding effective emission measure distribution, $\mathrm{EM}(T_{eff})$, using $T_{eff}$, the effective temperature calculated by including effects due to NEI.
-	%
-	\par As noted in \autoref{subsec:heating_stats}, for each heating frequency $t_N$, we compute $N_R$ runs such that there are $N_R$ $\mathrm{EM}(T)$ distributions for each $t_N$.
-Thus, the $\mathrm{EM}(T)$ that we show for each $t_N$ is the average computed over all $N_R$ of these emission measure distributions.
-	%\par To characterize the emission measure, we compute the slopes on both the cool and hot sides of the peak.
-To be consistent with past observational and computational studies of cool emission \citep[see][and references therein]{bradshaw_diagnosing_2012}, we fit the cool slope on the interval $6.0\le\log{T}\le6.6$.
-Contrastingly, past studies of hot emission are less abundant; thus, the ``hot'' region where the $\mathrm{EM}$ is thought to follow a power-law is far less constrained.
-In order to best describe the steepness of the emission measure hotward of the peak, we choose to fit $\mathrm{EM}$ between the temperatures at which the emission measure is $99\%$ and $92\%$ of the peak value.
-We have no physical reason for choosing these particular bounds, but note that on this interval, the mean hotward emission is reasonably well-described by a power-law relationship.
-Fitting too close to the wide peak leads to misleadingly shallow slopes while fitting too close to the steep drop near $\log{T}\sim7.5$ results in steep slopes not particularly representative of the hotward emission.
-We perform the fit using the Levenberg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}.
-	%
+	%%
 	\subsection{Emission Measure Distributions}
@@
 		\centering
-		\includegraphics[width=2\columnwidth]{figures/em_grid_electron_a25.pdf}
-		\caption{Emission measure distributions for varying waiting-times, $t_N$ in the case where only the electrons are heated.
+		\includegraphics[width=2\columnwidth]{figures/em_grid_single_a25.pdf}
+		\caption{Emission measure distributions for waiting-times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case.
 The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).
 The dotted lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}
+		\label{fig:single_em}
+	\end{figure*}
+	%
+	\begin{figure*}[t]
+		\centering
+		\includegraphics[width=2\columnwidth]{figures/em_grid_electron_a25.pdf}
+		\caption{Same as \autoref{fig:single_em}, but for the case where only the electrons are heated.}
 		\label{fig:el_em}
 	\end{figure*}
-	%
-	\par First, we look at the resulting emission measure distributions for the case in which only the electrons are heated.
-\autoref{fig:el_em} shows $\mathrm{EM}(T)$ for six different values of $t_N$ and three different types of heating functions: uniform heating events, events chosen from a power-law distribution of index $\alpha=-2.5$, and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event.
-The dotted lines in each frame show the corresponding emission measure distribution constructed from $T_{eff}$, $\mathrm{EM}(T_{eff})$.
-	%
-	\par As $t_N$ increases, $\mathrm{EM}$ is allowed to extend to both lower and 
 	%
@@
 		\includegraphics[width=2\columnwidth]{figures/em_grid_ion_a25.pdf}
-		\caption{Same as \autoref{fig:el_em}, but for the case where only the ions are heated.}
+		\caption{Same as \autoref{fig:single_em}, but for the case where only the ions are heated.}
 		\label{fig:ion_em}
@@
 	%
-	\par \autoref{fig:el_em} and \autoref{fig:ion_em} show the results of our emission measure study for the two distinct cases where only the electrons are heated and only the ions are heated with $\alpha=-2.5,\beta=1$ for a loop half-length of $40$ Mm, consistent with \citetalias{barnes_inference_2016}.
-The panels on the left show the mean $\mathrm{EM}$ for all $t_N$, where the average is taken over all $N_{R}$ runs.
-There is an artifical spacing of $\Delta\log{\mathrm{EM}}=0.2$ between each curve so that they can be easily distinguished from each other.
-The blue (red) lines indicate the cool (hot) power-law fits, where the slopes of the lines are the averages taken over all $N_{R}$ runs.
-We note that the $\mathrm{EM}$, for all $t_N$, peaks at approximately 4 MK ($10^{6.6}$ K), consistent with the constraints laid out in \autoref{subsec:params}.
-The top right panels show these average slope values as a function of $t_N$.
-The error bars indicate one standard deviation as calculated from the distribution of all $N_{R}$ runs.
+	\par In our first set of results, we compare $\mathrm{EM}(T)$ for three different types of heating functions, across six different heating frequencies.
+\autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions in the single-fluid case, electron heating case, and ion heating case, respectively.
+Each panel in each figure corresponds to a different waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a power-law distribution of index $\alpha=-2.5$ (blue), and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event (green).
+Furthermore, the dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$.
 	%
-	\par Lastly, the bottom right panels show the first derivative as a function of temperature, $d\log{\mathrm{EM}}/d\log{T}$, computed using central differences.
-The color scheme and line styles correspond to the emission mesure curves in the left panel.
-As in \citetalias{barnes_inference_2016}, we compute the derivative in an effort to better assess at what temperatures the emission measure is not well described by a power-law.
+	\par Recall from \autoref{subsec:heating_stats} that for those heating functions which choose peak heating rates from a power-law distribution, for each $t_N$, we run the model $N_R\sim(t_N+200)/8$ times.
+Thus, for each point in our parameter space, we produce $N_R$ $\mathrm{EM}(T)$ curves.
+In order to present our results compactly, the panels of \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} each show the average over all $N_R$ curves.
+In this way, we account for the variations that may occur because of a lack/excess of strong heating events due to limited sampling from the distribution.
 	%
-	\par We first briefly consider the calculated cool emission measure slopes.
-Looking at the top right panels of \autoref{fig:el_em} and \autoref{fig:ion_em}, we note that in the cases of electron and ion heating, the cool emission measure slopes are consistent with both observational and modeling studies of cool emission in AR cores, having values that fall within the range $2\le a\le5$ \citep[and references therein]{bradshaw_diagnosing_2012}.
-Furthermore, the cool slopes computed using our new modified EBTEL model, with a heating function of the form $Q\propto T_N^{\beta}$, are consistent with those values reported in \citet{cargill_active_2014} and show a dependence on the waiting time $t_N$.
+	\par We look first at the $\mathrm{EM}(T)$ for the single-fluid case, \autoref{fig:single_em}.
+Looking at all six panels, we note that as $t_N$ increases, $\mathrm{EM}(T)$ widens towards both cooler and hotter temperatures.
+$\mathrm{EM}(T)$ extends toward cooler temperatures because as $t_N$ increases and there is more time between successive heating events, the loop is allowed more time to cool both by radiation and enthalpy flux.
+$\mathrm{EM}(T)$ extends towards hotter temperatures for similar, but more subtle reasons.
+As $t_N\to0$, we approach the steady heating case in which conductive and radiative cooling exactly balance the heating.
+As $t_N$ increases and becomes comparable to and greater than a cooling time, the loop beceomes increasingly tenuous at the time of the subsequent heating event, allowing the loop to reach much hotter temperatures as radiative cooling is very inefficient at low densities.
+In this way, $\mathrm{EM}(T)$ can ``see'' this greater range of temperatures, both hot and cool, provided it is allowed to undergo a typical heating and cooling cycle.
+The more curtailed this cycle is by continued reheatings, the more narrow $\mathrm{EM}(T)$ will be.
 	%
-	\par Additionally, looking at the bottom right panels of \autoref{fig:el_em} and \autoref{fig:ion_em}, we see that, within the range $6.0\le\log{T}\le6.6$, the $\mathrm{EM}$ is reasonably well-described by a power-law, where $2\lesssim d\log{\mathrm{EM}/d\log{T}}\lesssim3$.
-Comparing the cases of electron and ion heating for both the cool slopes and $d\log{\mathrm{EM}/d\log{T}}$ on $6.0\le\log{T}\le6.6$, there are no substantial differences for all values of $t_N$ considered.
+	\par\hl{Describe differences between different heating function types} Looking at the different curves in each panel of \autoref{fig:single_em}, it is important to note that, although all widen as $t_N$, the way each extends higher and lower temperatures is very different.
 	%
-	\par This is not the case for the hot emission measure.
-Looking first at the case of electron heating in \autoref{fig:el_em}, we note that there is a pronounced ``hot shoulder'' in the emission measure (left panel) just above $10^7$ K for $T_N\gtrsim2000$ s.
-This feature is even more evident when looking at the derivative of $\mathrm{EM}$ in the bottom right panel of \autoref{fig:el_em}.
-The peak between $10^7$ and $10^{7.5}$ K shows how the $\mathrm{EM}$ flattens out around $10^7$ K, indicating an enhanced hot emission measure.
-Considering the large range of values of $d\log{\mathrm{EM}}/d\log{T}$ on the interval over which the fit was performed, we acknowledge that a single power-law fit is not a good description of the hot emission measure in the case of electron heating.
+	\par\hl{Address electron and ion cases and how they differ from the single-fluid case in the ways discussed above.}
 	%
-	\par Contrastingly, we have not calculated the hot emission measure slopes for the case of ion heating.
-Looking at the left panel of \autoref{fig:ion_em}, for $T_N\gtrsim1000$ s, the $\mathrm{EM}$ peak is wide with a sharp cutoff just above $10^7$ K.
-There is no substantial emission measure component above $10^7$ K and, consequently, no hot shoulder as in the electron heating case.
-Applying the fitting procedure outlined above to the hot emission in the case of ion heating yields meaningful results for only a few short $t_N$.
-Thus, as in the case of electron heating, the resulting hot emission measure from ion heating is also not well described by a power-law.
-The lower right panel of \autoref{fig:ion_em} further highlights this by showing that around $10^7$ K, $d\log{\mathrm{EM}}/d\log{T}\to-\infty$.
-	%
+	\par\hl{Describe differences between IEQ and NEI solutions.}
+	%%%%%%%%%%%%%
 	\subsection{Pre-nanoflare Density}
@@
 	\end{figure*}
+	%
+	\par\hl{Mostly discussing differences between power-law and uniform on hot side and scaling/non-scaling on the cool side. Lead into this paragraph from the previous paragraph}
 	%
@@
 	\label{subsec:diagnostics}
+	%%
+	%\par To characterize the emission measure, we compute the slopes on both the cool and hot sides of the peak.
+To be consistent with past observational and computational studies of cool emission \citep[see][and references therein]{bradshaw_diagnosing_2012}, we fit the cool slope on the interval $6.0\le\log{T}\le6.6$.
+Contrastingly, past studies of hot emission are less abundant; thus, the ``hot'' region where the $\mathrm{EM}$ is thought to follow a power-law is far less constrained.
+In order to best describe the steepness of the emission measure hotward of the peak, we choose to fit $\mathrm{EM}$ between the temperatures at which the emission measure is $99\%$ and $92\%$ of the peak value.
+We have no physical reason for choosing these particular bounds, but note that on this interval, the mean hotward emission is reasonably well-described by a power-law relationship.
+Fitting too close to the wide peak leads to misleadingly shallow slopes while fitting too close to the steep drop near $\log{T}\sim7.5$ results in steep slopes not particularly representative of the hotward emission.
+We perform the fit using the Levenberg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}.
+	%
+	\par We first briefly consider the calculated cool emission measure slopes.
+Looking at the top right panels of \autoref{fig:el_em} and \autoref{fig:ion_em}, we note that in the cases of electron and ion heating, the cool emission measure slopes are consistent with both observational and modeling studies of cool emission in AR cores, having values that fall within the range $2\le a\le5$ \citep[and references therein]{bradshaw_diagnosing_2012}.
+Furthermore, the cool slopes computed using our new modified EBTEL model, with a heating function of the form $Q\propto T_N^{\beta}$, are consistent with those values reported in \citet{cargill_active_2014} and show a dependence on the waiting time $t_N$.
+	%
+	\par Additionally, looking at the bottom right panels of \autoref{fig:el_em} and \autoref{fig:ion_em}, we see that, within the range $6.0\le\log{T}\le6.6$, the $\mathrm{EM}$ is reasonably well-described by a power-law, where $2\lesssim d\log{\mathrm{EM}/d\log{T}}\lesssim3$.
+Comparing the cases of electron and ion heating for both the cool slopes and $d\log{\mathrm{EM}/d\log{T}}$ on $6.0\le\log{T}\le6.6$, there are no substantial differences for all values of $t_N$ considered.
+	%
+	\par This is not the case for the hot emission measure.
+Looking first at the case of electron heating in \autoref{fig:el_em}, we note that there is a pronounced ``hot shoulder'' in the emission measure (left panel) just above $10^7$ K for $T_N\gtrsim2000$ s.
+This feature is even more evident when looking at the derivative of $\mathrm{EM}$ in the bottom right panel of \autoref{fig:el_em}.
+The peak between $10^7$ and $10^{7.5}$ K shows how the $\mathrm{EM}$ flattens out around $10^7$ K, indicating an enhanced hot emission measure.
+Considering the large range of values of $d\log{\mathrm{EM}}/d\log{T}$ on the interval over which the fit was performed, we acknowledge that a single power-law fit is not a good description of the hot emission measure in the case of electron heating.
+	%
+	\par Contrastingly, we have not calculated the hot emission measure slopes for the case of ion heating.
+Looking at the left panel of \autoref{fig:ion_em}, for $T_N\gtrsim1000$ s, the $\mathrm{EM}$ peak is wide with a sharp cutoff just above $10^7$ K.
+There is no substantial emission measure component above $10^7$ K and, consequently, no hot shoulder as in the electron heating case.
+Applying the fitting procedure outlined above to the hot emission in the case of ion heating yields meaningful results for only a few short $t_N$.
+Thus, as in the case of electron heating, the resulting hot emission measure from ion heating is also not well described by a power-law.
+The lower right panel of \autoref{fig:ion_em} further highlights this by showing that around $10^7$ K, $d\log{\mathrm{EM}}/d\log{T}\to-\infty$.
+	%
+	%
+	\begin{figure*}
+		\centering
+		\includegraphics[width=2\columnwidth]{figures/em_slope_varying_bounds.pdf}
+		\caption{\textbf{Left:} EM slope as a function of upper bound on fit interval for both the hot (red) and cool (blue) side of $EM(T)$.
+\textbf{Right:} Emission measure distribution with overlaid hot and cool fit lines for varying fit intervals.}
+	\end{figure*}
 	%%

### 2016-06-23 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
filled out first portion of results section

@@
 The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).
-The dotted lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}
+The solid lines in the power-law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates one standard deviation from the mean.
+The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}
 		\label{fig:single_em}
@@
 	%
-	\par We look first at the $\mathrm{EM}(T)$ for the single-fluid case, \autoref{fig:single_em}.
-Looking at all six panels, we note that as $t_N$ increases, $\mathrm{EM}(T)$ widens towards both cooler and hotter temperatures.
-$\mathrm{EM}(T)$ extends toward cooler temperatures because as $t_N$ increases and there is more time between successive heating events, the loop is allowed more time to cool both by radiation and enthalpy flux.
+	\par We look first at $\mathrm{EM}(T)$ for the single-fluid case, \autoref{fig:single_em}.
+Looking at all six panels, we note that as $t_N$ increases, $\mathrm{EM}(T)$ widens, extending to both cooler ($<4$ MK) and hotter ($>4$ MK) temperatures.
+$\mathrm{EM}(T)$ extends toward cooler temperatures because as $t_N$ increases and there is more time between successive heating events, the loop is allowed more time to cool both by radiation and enthalpy-driven cooling.
 $\mathrm{EM}(T)$ extends towards hotter temperatures for similar, but more subtle reasons.
 As $t_N\to0$, we approach the steady heating case in which conductive and radiative cooling exactly balance the heating.
-As $t_N$ increases and becomes comparable to and greater than a cooling time, the loop beceomes increasingly tenuous at the time of the subsequent heating event, allowing the loop to reach much hotter temperatures as radiative cooling is very inefficient at low densities.
+As $t_N$ increases and becomes comparable to and greater than a cooling time, the loop beceomes increasingly tenuous at the time of the subsequent heating event, allowing the loop to reach much hotter temperatures since radiative cooling is very inefficient at low densities and the heat flux saturates.
 In this way, $\mathrm{EM}(T)$ can ``see'' this greater range of temperatures, both hot and cool, provided it is allowed to undergo a typical heating and cooling cycle.
@@
 	%
-	\par\hl{Describe differences between different heating function types} Looking at the different curves in each panel of \autoref{fig:single_em}, it is important to note that, although all widen as $t_N$, the way each extends higher and lower temperatures is very different.
+	\par Looking at the different curves in each panel of \autoref{fig:single_em}, it is important to note that, although $\mathrm{EM}(T)$ for all three types of heating functions widen with increasing wait time, their dependence on $t_N$ is quite different.
+The uniform (red) and power-law (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the power-law, $\beta=1$ curve (green) extends to cooler temperatures much more rapidly.
+For example, at $t_N=1500$ s, both the uniform and power-law cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK.
+Contrastingly, on the hot side, the power-law and $\beta=1$ curves evolve nearly identically with increasing $t_N$ while the unfiorm heating case shows a cutoff at much lower temperatures, particularly for $t_N\le2500$ s.
 	%
-	\par\hl{Address electron and ion cases and how they differ from the single-fluid case in the ways discussed above.}
+	\par The $\mathrm{EM}(T)$ curves for the different types of heating functions shown in \autoref{fig:el_em}, in which only the electrons are heated, evolve similarly to those shown in \autoref{fig:single_em}.
+This is particularly true on the cool side where the density is sufficiently high, allowing the electrons and the ions to equilibrate such that there is no discernible difference compared to the single-fluid case.
+On the hot side, for $t_N\le750$ s, the electron and single-fluid cases are quite similar.
+However, for $t_N\ge1500$ s, $\mathrm{EM}(T)$ steepens just above 4 MK and then flattens out near 10 MK.
+This change in shape is most obvious in the uniform heating case where a distinct ``hot shoulder'' forms just above 10 MK.
+In the power-law cases, this feature is less pronounced and the $\mathrm{EM}(T)$ extends to slightly higher temperatures.
 	%
-	\par\hl{Describe differences between IEQ and NEI solutions.}
-	%%%%%%%%%%%%%
+	\par In \autoref{fig:ion_em} in which only the ions are heated, the cool side of the $\mathrm{EM}(T)$ is very similar to both the single-fluid and electron heating cases because the electron and ion populations are in equilibrium during this portion of the loop's evolution.
+On the hot side, for intermediate to low heating frequencies (i.e.
+$t_N\ge1500$ s), the $\mathrm{EM}(T)$ in the uniform heating case is truncated below 10 MK and in the power-law cases extends to just above 10 MK for the lowest heating frequency ($t_N=5000$ s).
+This cutoff at lower temperatures is due to the fact that electrons cannot ``see'' the ions until they have cooled well below their peak temperature.
+This is discussed in \citetalias{barnes_inference_2016} though in the single-pulse cases, the cutoff occured at lower temperatures.
+Additionally, in both the uniform and power-law cases, the peak of the $\mathrm{EM}(T)$ is wider for these low frequencies compared to those cases shown in \autoref{fig:single_em} and \autoref{fig:el_em}.
+	%
+	\par The dashed lines in the panels of \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the corresponding $\mathrm{EM}(T_{eff})$ for each heating function type.
+Only the mean $\mathrm{EM}(T_{eff})$ over $N_R$ runs is shown for these results.
+In all three figures, for the intermediate to high frequencies (i.e.
+$t_N\le1500$ s), there is no discernible difference between $\mathrm{EM}(T)$ and $\mathrm{EM}(T_{eff})$.
+Furthermore, both of the power-law cases show little deviation from ionization equilibrium in the emission measure for even the lowest heating frequencies in the single-fluid, electron heating, and ion heating cases.
+For $t_N\ge2500$ s in the uniform heating case, in both \autoref{fig:single_em} and \autoref{fig:el_em}, $\mathrm{EM}(T_{eff})$ is truncated at slightly lower temperatures as compared to $\mathrm{EM}(T)$.
+This hot emission is relocated to cooler temperatures, resulting in a ``bump'' in the emission measure distribution near 10 MK.
+None of the panels of \autoref{fig:ion_em} show any significant difference between $\mathrm{EM}(T)$ and $\mathrm{EM}(T_{eff})$.
+This is because the electrons are essentially heated on a timescale dictated by the Coulomb collision frequency which is slow enough to ensure ionization equilibrium during the entire heating phase.
+	%
 	\subsection{Pre-nanoflare Density}
@@
 		\centering
-		\includegraphics[width=2\columnwidth]{figures/nT_sample_curves_tn1500_electron.pdf}
-		\caption{Example temperature and density profiles for an intermediate heating frequency, $t_N=1500$ s for several different heating function types.}
+		\includegraphics[width=2\columnwidth]{figures/nT_sample_curves_tn2500_electron.pdf}
+		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for an intermediate heating frequency, $t_N=2500$ s for uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).}
 	\end{figure*}
 	%
-	\par\hl{Mostly discussing differences between power-law and uniform on hot side and scaling/non-scaling on the cool side. Lead into this paragraph from the previous paragraph}
+	\par\hl{Mostly discussing differences between power-law and uniform on hot side and scaling/non-scaling on the cool side.
+Lead into this paragraph from the previous paragraph.
+Questions to answer: why do power-law cases extend to hotter temperatures for equivalent $t_N$?
+Why do power-law cases show little to no deviation from IEQ?}
 	%

### 2016-06-25 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
adding description of varying fit interval figure

@@
 However, the detection of such emission has proved difficult due to a combination of the efficiency of thermal conduction, non-equilibrium ionization, and inadequate instrument sensitivity.
-In this second paper in our series on ``hot'' non-flaring plasma in active regions, we investigate the influence of repeating nanoflares of varying frequency on the resulting emission measure di .
+In this second paper in our series on ``hot'' non-flaring plasma in active regions, we investigate the influence of repeating nanoflares of varying frequency on the resulting emission measure distribution .
 We have used an efficient two-fluid hydrodynamic model to carry out a parameter exploration in preferentially heated species, heating event frequency, and the power-law index determining the distribution of event energies.
-By computing the emission measure distributions and calculating their ``hotward'' slopes, we have concluded that not treating the electron and ion populations separately leads to a mischaracterization of the hot emission.
-Additionally, we find that, while emission due to separate electron and ion heating differs greatly hotward of the peak, the respective coolward emission measure slopes are similar such that a distinction between the heating of one species over another based on this criteria alone is not possible.
+We compute the emission measure distribution for each point in our multi-dimensional heating parameter space in an effort to understand how each of these variables impacts the observed emission.
+Additionally, we calculate several observables and compare their efficacy in capturing the character of both the hot and cool parts of the emission measure distribution.
 	\end{abstract}
@@
 Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim3.6\times10^{-3}$.
-\hl{In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored.} Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by
+In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored.
+Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by
 	\begin{equation}
@@
 $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent.
-Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions.
-\hl{Are we going to look at the single-fluid case?
-If not, remove if here and reconsider total number of heating functions.}}
+Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions.}
 		\label{fig:parameter_space}
@@
 	%
-	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to compute the non-equilibrium ionization states and the corresponding effective electron temperature, $T_{eff}$ that would be inferred by assuming ionization equilibrium.
-Using $T_eff$, we are then able to compute a corresponding NEI emission measure distribution.
+	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results.
+Given a temperature ($T(t)$) and density ($n(t)$) profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$ that would be inferred by assuming ionization equilibrium.
+Using $T_{eff}$, we are then able to compute a corresponding NEI emission measure distribution.
 	%%
@@
 The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).
-The solid lines in the power-law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates one standard deviation from the mean.
+The solid lines in the power-law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean.
 The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}
@@
 The uniform (red) and power-law (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the power-law, $\beta=1$ curve (green) extends to cooler temperatures much more rapidly.
-For example, at $t_N=1500$ s, both the uniform and power-law cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK.
+For example, at $t_N=1500$ s, both the uniform and power-law cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK \citep{cargill_active_2014}.
 Contrastingly, on the hot side, the power-law and $\beta=1$ curves evolve nearly identically with increasing $t_N$ while the unfiorm heating case shows a cutoff at much lower temperatures, particularly for $t_N\le2500$ s.
@@
 		\includegraphics[width=2\columnwidth]{figures/nT_sample_curves_tn2500_electron.pdf}
-		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for an intermediate heating frequency, $t_N=2500$ s for uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).}
+		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for the case in which only the electrons are heated and an intermediate heating frequency of $t_N=2500$ s.
+The three curves shown in each panel correspond to uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).}
+		\label{fig:nT_sample_profiles}
 	\end{figure*}
@@
 	%
-	\par \autoref{fig:single_em} shows the same results as \autoref{fig:el_em} and \autoref{fig:ion_em}, but for the single-fluid case in which electron-ion equilibrium is assumed at all times.
-To compute these $\mathrm{EM}$ curves, we have used the original, single-fluid EBTEL model as described in \citet{klimchuk_highly_2008} and \citet{cargill_enthalpy-based_2012}.
-The equivalent parameter space that was investigated with the modified two-fluid EBTEL model is explored with the single-fluid EBTEL code as well.
+	\par In the single-fluid and electron heating cases, while $\mathrm{EM}(T)$ in the uniform and power-law heating cases generally agree for low-frequency heating ($t_N=5000$ s), for intermediate frequencies ($t_N\approx750-2500$ s), the power-law cases show an enhanced high-temperature component compared to the uniform case as seen in \autoref{fig:single_em} and \autoref{fig:el_em}.
 	% 
-	\par We compute the hot and cool emission measure slopes in the same manner as the electron and ion heating cases.
-We first note that the cool emission measure slopes are comparable to those in both the electron and ion heating cases.
-In particular, we find $2\lesssim a\lesssim5$ for all values of $t_N$ as expected.
-Again, we confirm the validity of our linear fit to the cool emission by computing the derivative $d\log{\mathrm{EM}}/d\log{T}$ in the lower right panel of \autoref{fig:single_em}.
-For $T_N\gtrsim2000$ s, the slope is bounded between 2 and 3 on the interval $6.0\le\log{T}\le6.6$.
+	\par\autoref{fig:nT_sample_profiles} shows sample heating, temperature, and density profiles for an intermediate heating frequency ($t_N=2500$ s), in the case where only the electrons are heated, for the three different types of heating functions.
+In the uniform heating rate case (red), each event has a max heating rate of $H_0$ such that the loop undergoes $N\approx30$ identical heating and cooling cycles, each time reaching a maximum temperature and density of $T_{max,0}$ and $n_{max,0}$, respectively.
+Recall from \autoref{eq:heating_rate_constraint} that the total energy injected into the loop is constrained such that $H_0=(1/N)\sum_{i=1}^NH_i$.
+In the case where the heating rates are distributed according to a power-law, there will be many events where $H_i<H_0$ and a few events where $H_i\gg H_0$.
 	%
-	\par The hot emission measure in the single-fluid case differs significantly from the two-fluid case.
-In contrast to the electron heating case in \autoref{fig:el_em}, the $\mathrm{EM}$ curves in the left panel of \autoref{fig:single_em} show no hot shoulder.
-This is further confirmed by the lower right panel; the derivative, in contrast to the electron heating case, shows no peak near $10^7$ K.
-For low $t_N$, $d\log{\mathrm{EM}}/d\log{T}$ is monotonically decreasing for $\log{T}\gtrsim6.6$.
-For $T_N\ge3000$ s, $d\log{\mathrm{EM}}/d\log{T}$ is relatively flat for $\log{T}\ge7.0$, indicating that a power-law provides a good description of the hot emission in this region.
-This is confirmed by noting the agreement between the fit lines and the $\mathrm{EM}$ curves in the left panel.
-	%
-	\par Comparing the top right panels of \autoref{fig:single_em} and \autoref{fig:el_em} further highlights the enhanced hot emission in the electron case.
-For high $t_N$, the hot emission slopes in the electron case converge to a value just above 3; for the single-fluid case, the hot slopes converge to approximately 4.5.
-Thus, while a single power-law is not a good descriptor for the hot emission in the case of electron heating, the slope still captures the enhanced hot shoulder relative to the weaker hot emission of the single-fluid case.
-Additionally, comparing the single-fluid case to the ion heating case in \autoref{fig:ion_em}, it is obvious that the single-fluid case shows a great deal more hot emission as the $\mathrm{EM}$ curves in the left panel of \autoref{fig:single_em} extend well above $10^7$ K while those in the left panel of \autoref{fig:ion_em} show a steep cutoff at temperatures just above the peak.
+	\par The effect of these few higher energy events can be seen where the peak temperature of event $i$ is greater than $T_{max,0}$ in the two power-law cases (blue and green curves) in the middle panel of \autoref{fig:nT_sample_profiles}
 	%
@@
 	%%
-	%\par To characterize the emission measure, we compute the slopes on both the cool and hot sides of the peak.
-To be consistent with past observational and computational studies of cool emission \citep[see][and references therein]{bradshaw_diagnosing_2012}, we fit the cool slope on the interval $6.0\le\log{T}\le6.6$.
-Contrastingly, past studies of hot emission are less abundant; thus, the ``hot'' region where the $\mathrm{EM}$ is thought to follow a power-law is far less constrained.
-In order to best describe the steepness of the emission measure hotward of the peak, we choose to fit $\mathrm{EM}$ between the temperatures at which the emission measure is $99\%$ and $92\%$ of the peak value.
-We have no physical reason for choosing these particular bounds, but note that on this interval, the mean hotward emission is reasonably well-described by a power-law relationship.
-Fitting too close to the wide peak leads to misleadingly shallow slopes while fitting too close to the steep drop near $\log{T}\sim7.5$ results in steep slopes not particularly representative of the hotward emission.
-We perform the fit using the Levenberg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}.
-	%
-	\par We first briefly consider the calculated cool emission measure slopes.
-Looking at the top right panels of \autoref{fig:el_em} and \autoref{fig:ion_em}, we note that in the cases of electron and ion heating, the cool emission measure slopes are consistent with both observational and modeling studies of cool emission in AR cores, having values that fall within the range $2\le a\le5$ \citep[and references therein]{bradshaw_diagnosing_2012}.
-Furthermore, the cool slopes computed using our new modified EBTEL model, with a heating function of the form $Q\propto T_N^{\beta}$, are consistent with those values reported in \citet{cargill_active_2014} and show a dependence on the waiting time $t_N$.
-	%
-	\par Additionally, looking at the bottom right panels of \autoref{fig:el_em} and \autoref{fig:ion_em}, we see that, within the range $6.0\le\log{T}\le6.6$, the $\mathrm{EM}$ is reasonably well-described by a power-law, where $2\lesssim d\log{\mathrm{EM}/d\log{T}}\lesssim3$.
-Comparing the cases of electron and ion heating for both the cool slopes and $d\log{\mathrm{EM}/d\log{T}}$ on $6.0\le\log{T}\le6.6$, there are no substantial differences for all values of $t_N$ considered.
-	%
-	\par This is not the case for the hot emission measure.
-Looking first at the case of electron heating in \autoref{fig:el_em}, we note that there is a pronounced ``hot shoulder'' in the emission measure (left panel) just above $10^7$ K for $T_N\gtrsim2000$ s.
-This feature is even more evident when looking at the derivative of $\mathrm{EM}$ in the bottom right panel of \autoref{fig:el_em}.
-The peak between $10^7$ and $10^{7.5}$ K shows how the $\mathrm{EM}$ flattens out around $10^7$ K, indicating an enhanced hot emission measure.
-Considering the large range of values of $d\log{\mathrm{EM}}/d\log{T}$ on the interval over which the fit was performed, we acknowledge that a single power-law fit is not a good description of the hot emission measure in the case of electron heating.
-	%
-	\par Contrastingly, we have not calculated the hot emission measure slopes for the case of ion heating.
-Looking at the left panel of \autoref{fig:ion_em}, for $T_N\gtrsim1000$ s, the $\mathrm{EM}$ peak is wide with a sharp cutoff just above $10^7$ K.
-There is no substantial emission measure component above $10^7$ K and, consequently, no hot shoulder as in the electron heating case.
-Applying the fitting procedure outlined above to the hot emission in the case of ion heating yields meaningful results for only a few short $t_N$.
-Thus, as in the case of electron heating, the resulting hot emission measure from ion heating is also not well described by a power-law.
-The lower right panel of \autoref{fig:ion_em} further highlights this by showing that around $10^7$ K, $d\log{\mathrm{EM}}/d\log{T}\to-\infty$.
-	%
-	%
+	\par\hl{Discuss usefullness of hot slope versus cool slope via figure; discuss advantages of em ratio; discuss em ratio figures; break into subsections?}
+	%%
 	\begin{figure*}
@@
 		\includegraphics[width=2\columnwidth]{figures/em_slope_varying_bounds.pdf}
-		\caption{\textbf{Left:} EM slope as a function of upper bound on fit interval for both the hot (red) and cool (blue) side of $EM(T)$.
-\textbf{Right:} Emission measure distribution with overlaid hot and cool fit lines for varying fit intervals.}
+		\caption{Power-law fits to a sample emission measure distribution constructed from a loop plasma in which only the electrons were heated by events chosen from a power-law distribution with $\alpha=-2.5$ and equally spaced by an interval of $t_N=5000$ s.
+\textbf{Left:} $\mathrm{EM}(T)$ slope as a function of upper bound on fit interval for both the hot (red) and cool (blue) side of $\mathrm{EM}(T)$.
+The shading denotes the uncertainty of the fit.
+The bottom axis corresponds to the varying upper limit on the fit to the cool side while the top axis corresponds to the varying upper limit on the fit to the hot side.
+\textbf{Right:} $\mathrm{EM}(T)$ with the overlaid hot (red) and cool (blue) fit lines whose slopes correspond to those shown on the left.
+The cool power-law fits describe describe $\mathrm{EM}(T)$ for $T<4$ MK quite well while a similar fit on the hot side fails to accurately describe the shape of the emission measure distribution for $T>4$ MK.}
+		\label{fig:em_slope_varying_bounds}
 	\end{figure*}
@@
 		}
-		\caption{Electron heating emission measure ratio for an EIS/MaGIXS line pair}
+		\caption{Electron heating emission measure ratio for an EIS/MaGIXS line pair.\hl{Need a more descriptive caption here!}}
 	\end{figure*}
@@
 	%%
-	\par As mentioned in \autoref{sec:intro}, NEI can make it difficult to observe emission signatures from nanoflare-heated plasma because the heating timescale is shorter than the ionization timescale such that the charge state of the plasma is not representative of the plasma temperature.
-In order to diagnose how NEI might affect hot emission measure slopes, we use $n$ and $T_e$ profiles from our modified EBTEL code along with the method outlined by \citet{bradshaw_numerical_2009} to compute $T_{eff}$, the temperature that would be measured based on the actual ionization states.
-An effective emission measure distribution, $\mathrm{EM}_{eff}$, can then be calculated.
-Following \citetalias{barnes_inference_2016}, we use iron (Fe) and the ionization states Fe IX through FeXXV.
 	%
-	\par As the calculation of $T_{eff}$ is significantly more expensive than an EBTEL calculation, we do not compute $\mathrm{EM}_{eff}$ for the entire parameter space and instead consider only a small number of single-pulse test cases of duration $\tau_H=100$ s and peak heating rate $H_0=0.8$ erg cm$^{-3}$ s$^{-1}$.
-\autoref{fig:teff_test_case} shows temperature and density profiles (left column)  and emission measure distributions (right column) for the cases where NEI is (dashed) and is not (solid) included.
-These profiles are computed for all preferentially-heated species (electron, ion, single-fluid).
-For all three species, we note that including NEI in the calculation of the cool slope makes essentially no difference .
+	\par We now examine several observables often used to characterize the emission measure distribution.
+The most common observable is the emission measure slope $a$ such that $\mathrm{EM}\propto T^a$ for $10^{5.5}\le T\le10^{6.6}$ K.
+Both observational and modeling studies have found that $2<a<5$ \citep[see Table 3 of][]{bradshaw_diagnosing_2012} and in particular, \citet{cargill_active_2014} found that a heating function of the form $t_N\propto\varepsilon$ was needed in order to account for this range of slopes.
+Additionally, a similar scaling of $\mathrm{EM}\propto T^{-b}$ for $10^{6.6}\le T\le10^{7.0}$ has been claimed though measurements of $b$ have been subject to large uncertainties \citep{warren_systematic_2012}.
 	%
-	\par As in \autoref{fig:ion_em}, we do not compute the hot slope for the case of ion heating.
-Looking at the right panel in the middle row of \autoref{fig:teff_test_case}, we see that the inclusion of NEI in the case of ion heating has little to no effect on the emission measure.
-This is confirmed by the left panel of the middle row which shows that the difference between $T$ and $T_{eff}$ is relatively small and only occurs at low densities.
-Conversely, in the single-fluid and electron-heating cases, $T$ and $T_{eff}$ differ greatly during the heating phase and NEI has two distinct effects on the $\mathrm{EM}$: it leads to an overestimation of the amount of emission in the mid-range hot temperatures ($7.0\lesssim\log{T}\lesssim7.2$) and causes a steeper cutoff in the emission at lower temperatures (before $\log{T}\approx7.25$) compared to the case where NEI is not included.
-Interestingly, in both the electron-heating (first row) and single-fluid (third row) cases, $b_{eff}<b$ though we note that in the electron-heating case (first row), a power-law fit does not adequately describe the hot side of the $\mathrm{EM}$ distribution.
-	%
-	\par To compare the effects of varying $\alpha$, $\beta$, and $t_N$ for each species (i.e.
-electron, ion, single-fluid), we construct histograms of hot and cool emission measure slopes for each parameter space point.
-Recall that in the case where the distributions of heating event energies are non-uniform, we have $N_{R}$ emission measure slopes to properly account for the statistical spread in hot emission measure slopes due to power-law distributions.
-	%
+	\par\autoref{fig:em_slope_varying_bounds} shows an example of how both $T^a$ and $T^{-b}$ can be fit to the cool and hot sides of $\mathrm{EM}(T)$, respectively.
+We fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}.
+We fix the lower limit on each interval such that $T_{c,min}=10^{5.7}$ K and $T_{h,min} = 10^{6.7}$  K and vary the upper limits over $10^{6.1}<T_{c,max}<10^{6.5}$ and $10^{6.8}<T_{h,max}<10^{7.2}$.
+The left panel of \autoref{fig:em_slope_varying_bounds} shows the $a$ (blue) and $b$ (red) as a function upper limit of the fit interval, $T_{c,max}$ (bottom axis) and $T_{h,max}$ (top axis), respectively.
+The shading denotes the uncertainty of the fit.
+The right panel of \autoref{fig:em_slope_varying_bounds} shows the resulting fit lines superimposed on the emission measure distribution.
+	%%%%%%%%%
 	\par As seen in \autoref{fig:histos}, these histograms, denoted by type of slope (i.e.
@@
 Additionally, the bin widths are calculated using the well-known Freedman-Diaconis formula \citep{freedman_histogram_1981}.
-	%
-	\par Concerning the distributions of cool slopes grouped by type of heating function (bottom row of \autoref{fig:histos}), we note that there are no discernible differences between the cases of electron and ion heating.
-In both cases, all heating functions except for those where $\beta=1$ are peaked sharply between 2 and 2.5.
-In the case where $\beta=1$ (for all $\alpha$), the distribution is peaked between 2.5 and 3, with the width of the distribution increasing as $\alpha$ steepens.
-This larger range of cool emission measure slopes for the case of $\beta=1$ is consistent with \citet{cargill_active_2014}.
-	%
-	\par As stated in \autoref{subsec:electron_ion_heating}, we choose not to show the hot emission measure slopes for the ion heating case as they are not representative of the emission measure distribution hotward of the peak as evidenced by the left and bottom right panels of \autoref{fig:ion_em}.
-Instead, we compare the hot emission measure slopes of the electron heating and single-fluid cases, the bottom left and bottom right panels of \autoref{fig:histos}, respectively.
-In both cases, for $T_N<3000$ s, we see a strong dependence on $t_N$ while for $T_N\ge3000$ s, the slopes tend to be sharply peaked around a single value.
-In the electron heating case, distributions for $T_N<3000$ s tend to be more narrow than their single-fluid counterparts and centered at lower values (i.e.
-more shallow hot slopes).
-Most notably, for $T_N\ge4000$ s, the electron heating hot emission measure slopes are peaked between 3 and 3.5 while the single-fluid slopes are peaked at $\sim4.5$.
 	%
@@
 	%
-	\par However, looking at the left panels in the first and third rows of \autoref{fig:teff_test_case}, we see that just after the heating ends at 100 s, $T_{eff}>T$ due to the fact that the thermal conduction timescale is shorter than the ionization equilibration timescale.
-This lag in the charge state due to the efficiency of thermal conduction leads to the mid-range hot temperature emission enhancement seen in the right panels of the first and third rows of \autoref{fig:teff_test_case}.
-	%
 	\section{Conclusions}
@@
 	%
-	\hl{Acknowledge some things here.} 
+	WTB was provided travel support to the Coronal Loops Workshop VII held in Cambridge, UK, July 21-23, 2015, at which a preliminary version of this work was presented, by NSF award number 1536094.
+This work was supported in part by the Big-Data Private-Cloud Research Cyberinfrastructure MRI-award funded by NSF under grant CNS-1338099 and by Rice University.
 	%

### 2016-06-27 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
finshing section discussing emission measure ratio histograms

@@
 Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating.
-In the case of high-frequency heating, $\langle t_N\rangle$, the time between successive events, is such that $\langle t_N\rangle\ll\tau_{cool}$, where $\tau_{cool}$ is the loop cooling time, and in the case of low-frequency heating $\langle t_N\rangle\gg\tau_{cool}$ \citep{cargill_modelling_2015}.
-Steady heating is just high-frequency heating in the limit $\langle t_N\rangle\to0$.
+In the case of high-frequency heating, $t_N$, the time between successive events, is such that $t_N\ll\tau_{cool}$, where $\tau_{cool}$ is the loop cooling time, and in the case of low-frequency heating $t_N\gg\tau_{cool}$ \citep{cargill_modelling_2015}.
+Steady heating is just high-frequency heating in the limit $t_N\to0$.
 	%
@@
 While \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$.
-\citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<\langle t_N\rangle<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the full range of observed emission measure slopes be found.
+\citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<t_N<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the full range of observed emission measure slopes be found.
 	%
@@
 		\includegraphics[width=2\columnwidth]{figures/nT_sample_curves_tn2500_electron.pdf}
-		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for the case in which only the electrons are heated and an intermediate heating frequency of $t_N=2500$ s.
+		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for the case in which only the electrons are heated with an intermediate heating frequency of $t_N=2500$ s.
 The three curves shown in each panel correspond to uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).}
@@
 	%%
-	\par\hl{Discuss usefullness of hot slope versus cool slope via figure; discuss advantages of em ratio; discuss em ratio figures; break into subsections?}
+	\subsubsection{Emission Measure Slope}
+	\label{subsubsec:em_slope}
 	%%
@@
 		\includegraphics[width=2\columnwidth]{figures/em_slope_varying_bounds.pdf}
-		\caption{Power-law fits to a sample emission measure distribution constructed from a loop plasma in which only the electrons were heated by events chosen from a power-law distribution with $\alpha=-2.5$ and equally spaced by an interval of $t_N=5000$ s.
+		\caption{Fits to a sample emission measure distribution constructed from a loop plasma in which only the electrons were heated by events chosen from a power-law distribution with $\alpha=-2.5$ and equally spaced by an interval of $t_N=5000$ s.
 \textbf{Left:} $\mathrm{EM}(T)$ slope as a function of upper bound on fit interval for both the hot (red) and cool (blue) side of $\mathrm{EM}(T)$.
@@
 		\label{fig:em_slope_varying_bounds}
-	\end{figure*}
-	%%
-	\begin{figure*}
-		\centering
-		\subfigure[]{%
-		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_electron_T2.pdf}
-		}
-		\subfigure[]{%
-		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_electron_T2.pdf}
-		}
-		\caption{Electron heating emission measure ratio for an EIS/MaGIXS line pair.\hl{Need a more descriptive caption here!}}
-	\end{figure*}
-	%%
-	\begin{figure*}
-		\centering
-		\subfigure[]{%
-		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_ion_T2.pdf}
-		}
-		\subfigure[]{%
-		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_ion_T2.pdf}
-		}
-		\caption{Diagnostics figures}
 	\end{figure*}
@@
 The right panel of \autoref{fig:em_slope_varying_bounds} shows the resulting fit lines superimposed on the emission measure distribution.
-	%%%%%%%%%
-	\par As seen in \autoref{fig:histos}, these histograms, denoted by type of slope (i.e.
-hot or cool) and species, are constructed in one of two ways: each distinct histogram (denoted by linestyle and/or color) is either representative of a distinct heating function (e.g.
-top row of \autoref{fig:histos}) or a distinct value of $t_N$ (e.g.
-bottom row of \autoref{fig:histos}).
-In the four panels of \autoref{fig:histos}, we choose to separate the cool emission measure slopes by type of heating function and the hot emission measure slopes by $t_N$.
-This means, for example, that the dot-dashed blue $\alpha=-1.5,\beta=1$ histogram in the upper left panel of \autoref{fig:histos} encapsulates cool emission measure slopes for $250\le T_N\le5000$ s while the solid blue $T_N=2000$ s histogram in the lower left panel includes emission measure slopes for all 10 types of heating functions (as listed in \autoref{fig:parameter_space} and the legend in the upper left panel of \autoref{fig:histos}).
-All histograms are normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$.
-Additionally, the bin widths are calculated using the well-known Freedman-Diaconis formula \citep{freedman_histogram_1981}.
 	%
+	\par From the left panel of \autoref{fig:em_slope_varying_bounds}, we see that, while $a$ is relatively insensitive to the fit interval, $b$ varies between approximately 2 and 4.5 depending on the choice of bounds of the fit interval.
+Furthermore, the uncertainty in the fitting procedure for $b$ is relatively large, with the average uncertainty over the entire range of $T_{h,max}$ being $\bar{\sigma}_b\approx0.17$.
+Contrastingly, we find that $a\approx2.3$ with little variation over all values of $T_{c,max}$ considered here and that $\bar{\sigma}_a\approx0.018$, nearly an order of magnitude smaller than $\bar{\sigma}_b$.
+The overlaid fit lines in the right panel of \autoref{fig:em_slope_varying_bounds} similarly show that while $\log{\mathrm{EM}}$ is roughly linear over $5.7<\log{T}<6.5$, this is not the case for the interval $6.7<\log{T}<7.2$.
+In particular, a function of the form $T^{-b}$ cannot describe the hot shoulder in the emission measure distribution near $10^{7.1}$ K.
+	%
+	\subsubsection{Emission Measure Ratio}
+	\label{subsubsec:em_ratio}
+	%%
+	\par\hl{Lead in with how EM ratio is better, i.e. not masquerading as a fit, just a single point; discussion of results from Brosius, how lines were chosen, then discuss histograms and types.}
+	%%
+	\begin{figure*}
+		\centering
+		\subfigure[]{%
+		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_electron_T2.pdf}
+		}
+		\subfigure[]{%
+		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_electron_T2.pdf}
+		}
+		\caption{Histograms of emission measure ratios for all heating function types and heating frequencies for the case in which only the electrons are heated.
+In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the well-known Freedman-Diaconis formula \citep{freedman_histogram_1981}.
+\textbf{Left:} Emission measure ratios separated by heating function type.
+\textbf{Right:} Emission measure ratios separated by waiting time, $t_N$.
+For aesthetic purposes, we only show five values of $t_N$.}
+		\label{fig:em_ratio_hist_el}
+	\end{figure*}
+	%%
+	\begin{figure*}
+		\centering
+		\subfigure[]{%
+		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_ion_T2.pdf}
+		}
+		\subfigure[]{%
+		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_ion_T2.pdf}
+		}
+		\caption{Same as \autoref{fig:em_ratio_hist_el}, but for the case where only the ions are heated.}
+		\label{fig:em_ratio_hist_ion}
+	\end{figure*}
+	%%
+	\par\citet{brosius_pervasive_2014}, using observations of an active region from the EUNIS-13 sounding rocket, found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside, providing possible evidence for impulsive heating.
+As a proxy for this intensity ratio and an alternative to the hot emission measure slope $b$, we propose using an emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$.
+Unlike an emission measure slope, a simple emission measure ratio gives information about the emission at only a single ``hot'' temperature relative to the cool side.
+Here, we choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}\approx2\times10^6$ K, the latter slightly higher than the formation temperature of Fe XII such that the emission measure ratio is less sensitive to variations in the cool emission and thus a more accurate measure of the amount of hot plasma.
+	%
+	\par The emission measure ratio provides a way to compactly compare every point in our multidimensional parameter space while acknowledging that we are reducing $8\times10^4$ s of loop evolution to a single value.
+The left panel of \autoref{fig:em_ratio_hist_el} shows the case in which only the electrons are heated, where each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function.
+This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$.
+We see that the emission measure ratio is largely insensitive to $\alpha$ and is peaked sharply at approximately $0.25$; the distribution peaks at slightly higher values for the $\beta=1$ case though the overall shape of the distribution is the same.
+Here we have not included the uniform heating case due to small number statistics (i.e.
+$<20$ emssion measure ratios).
+The right panel of \autoref{fig:em_ratio_hist_el} shows these same emission measure ratios, but now separated by $t_N$.
+For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e.
+uniform, all $\alpha$ and all $\beta$), but for only those runs where $t_N=3000$ s.
+Note that we choose to only show results for five values of $t_N$ for aesthetic purposes.
+We find that for $t_N\le3000$ s, the emission measure ratios are largely clustered below 0.5, with $t_N=2000,3000,4000$ s peaking between $\sim0.3-0.45$.
+It seems that the value of the emission measure ratio is more sensitive to the heating frequency for $t_N>4000$ s.
+	%
+	\par Similarly, we compute this same emission measure ratio for the case in which only the ions are heated.
+The left panel of \autoref{fig:em_ratio_hist_ion} shows histograms for each type of heating function.
+Similar to the electron heating results, we find that the $\beta=0$ distributions peak at lower values compared to the $\beta=1$ distributions and that in the $\beta=0$ case, the distribution of emission measures ratios is relatively insensitive to $\alpha$.
+However, unlike the electron heating case, the distributions in all cases are much wider and peak at higher values, $\sim0.5$ for $\beta=0$ and $>1$ for $\beta=1$.
+Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$.
+The right panel of \autoref{fig:em_ratio_hist_ion} shows the same emission measure ratios now grouped by waiting time where again we only show five values of $t_N$.
+With the exception of the $t_N=2000$ s and $t_N=3000 s$ group, the distributions for each value of $t_N$ are much more spread out (as compared \autoref{fig:em_ratio_hist_el}).
+In particular, $t_N=5000$ s peaks above 1.0 and extends past 1.5 while $t_N=1000$ peaks near 0 and drops off very steeply before 0.5.
+In general, the emission measure ratio appears to be more sensitive to $t_N$ compared to the electron heating case.
+	%%
 	\section{Discussion}
 	\label{sec:discussion}
+	%%
+	\par\hl{Probably cut most of this..}
 	%

### 2016-06-27 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex

@@
 Unlike an emission measure slope, a simple emission measure ratio gives information about the emission at only a single ``hot'' temperature relative to the cool side.
-Here, we choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}\approx2\times10^6$ K, the latter slightly higher than the formation temperature of Fe XII such that the emission measure ratio is less sensitive to variations in the cool emission and thus a more accurate measure of the amount of hot plasma.
+Here, we choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}\approx2\times10^6$ K, the latter slightly higher than the formation temperature of Fe XII such that the emission measure ratio is less sensitive to variations in the cool emission.
 	%
@@
 The left panel of \autoref{fig:em_ratio_hist_el} shows the case in which only the electrons are heated, where each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function.
-This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$.
-We see that the emission measure ratio is largely insensitive to $\alpha$ and is peaked sharply at approximately $0.25$; the distribution peaks at slightly higher values for the $\beta=1$ case though the overall shape of the distribution is the same.
-Here we have not included the uniform heating case due to small number statistics (i.e.
-$<20$ emssion measure ratios).
-The right panel of \autoref{fig:em_ratio_hist_el} shows these same emission measure ratios, but now separated by $t_N$.
-For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e.
-uniform, all $\alpha$ and all $\beta$), but for only those runs where $t_N=3000$ s.
-Note that we choose to only show results for five values of $t_N$ for aesthetic purposes.
-We find that for $t_N\le3000$ s, the emission measure ratios are largely clustered below 0.5, with $t_N=2000,3000,4000$ s peaking between $\sim0.3-0.45$.
-It seems that the value of the emission measure ratio is more sensitive to the heating frequency for $t_N>4000$ s.
+This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$.
+We see that the emission measure ratio is largely insensitive to $\alpha$ and is peaked sharply at approximately $0.25$; the distribution peaks at slightly higher values for the $\beta=1$ case though overall shape of the distribution is the same.
+\hl{Discuss right panel of electron histogram figure}
 	%
-	\par Similarly, we compute this same emission measure ratio for the case in which only the ions are heated.
-The left panel of \autoref{fig:em_ratio_hist_ion} shows histograms for each type of heating function.
-Similar to the electron heating results, we find that the $\beta=0$ distributions peak at lower values compared to the $\beta=1$ distributions and that in the $\beta=0$ case, the distribution of emission measures ratios is relatively insensitive to $\alpha$.
-However, unlike the electron heating case, the distributions in all cases are much wider and peak at higher values, $\sim0.5$ for $\beta=0$ and $>1$ for $\beta=1$.
-Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$.
-The right panel of \autoref{fig:em_ratio_hist_ion} shows the same emission measure ratios now grouped by waiting time where again we only show five values of $t_N$.
-With the exception of the $t_N=2000$ s and $t_N=3000 s$ group, the distributions for each value of $t_N$ are much more spread out (as compared \autoref{fig:em_ratio_hist_el}).
-In particular, $t_N=5000$ s peaks above 1.0 and extends past 1.5 while $t_N=1000$ peaks near 0 and drops off very steeply before 0.5.
-In general, the emission measure ratio appears to be more sensitive to $t_N$ compared to the electron heating case.
+	\par\hl{Now discuss ion heating results, left and right panels}
 	%%

### 2016-06-27 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
finishing up pre nanoflare density section, draft 1

--- 2016-06-27 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
@@
 	%
-	\par\hl{Mostly discussing differences between power-law and uniform on hot side and scaling/non-scaling on the cool side.
-Lead into this paragraph from the previous paragraph.
-Questions to answer: why do power-law cases extend to hotter temperatures for equivalent $t_N$?
-Why do power-law cases show little to no deviation from IEQ?}
-	%
 	\par In the single-fluid and electron heating cases, while $\mathrm{EM}(T)$ in the uniform and power-law heating cases generally agree for low-frequency heating ($t_N=5000$ s), for intermediate frequencies ($t_N\approx750-2500$ s), the power-law cases show an enhanced high-temperature component compared to the uniform case as seen in \autoref{fig:single_em} and \autoref{fig:el_em}.
@@
 	%
-	\par The effect of these few higher energy events can be seen where the peak temperature of event $i$ is greater than $T_{max,0}$ in the two power-law cases (blue and green curves) in the middle panel of \autoref{fig:nT_sample_profiles}
+	\par These few high energy events allow for $T\gg T_{max,0}$ in the case where the events are chosen from a power-law distribution(blue and green curves) as seen in the middle panel of \autoref{fig:nT_sample_profiles}.
+Because these events are injected into a plasma that is already sufficiently dense due to the relatively short draining and cooling times, the emission measure is able to ``see'' these hot temperatures, resulting in a $>10$ MK component of $\mathrm{EM}(T)$ (see lower left panel of \autoref{fig:single_em} and \autoref{fig:el_em}).
+Contrastingly, in the uniform case, $T_{max,0}<10$ MK such that $\mathrm{EM}(T)$ has a steep cutoff right at 10 MK.
+Additionally, we note that the only effect of the longer wait times in the $\beta=1$ case as compared to the $\beta=0$ power-law case is an extended cool emission measure; the hot part of $\mathrm{EM}(T)$ for both power-law cases is nearly identical.
+This provides further evidence for these two portions of the emission measure distribution being largely independent as they are determined by separate phases of the loop evolution.
+	%
+	\par Another important discrepancy between the uniform and power-law cases is the impact of NEI on the hot part of $\mathrm{EM}(T)$.
+Recall from \autoref{subsec:params} that the uniform heating rate $H_0=2t_{total}H_{eq}/N\tau=2H_{eq}(t_N/\tau+1)$.
+From the top panel of \autoref{fig:nT_sample_profiles} we see that in the power-law case, the heating rate can be as high as $H_i\sim0.3$ erg cm$^{-3}$ s$^{-1}$.
+In terms of a uniform heating rate, this corresponds to a waiting time of $t_N\approx8100$ s.
+So even for the lowest heating frequency in the uniform case, the heating rate is still much lower.
+Furthermore, for low $t_N$, between each event the loop is allowed to drain to its equilibrium value (as determined by the background heating) such that events with a heating rate $H_0\approx0.2$ erg cm$^{-3}$ s$^{-1}$ are injected into a low-density loop, meaning that the ionization state will not be able to keep pace with the subsequently rapid rise in temperature, resulting in $\mathrm{EM}(T_{eff})$ having a lower temperature cutoff.
+On the other hand, when the heating events are selected from a power-law, events with $H_i>0.2$ erg cm$^{-3}$ s$^{-1}$ can be injected into a much higher density loop (because lower values of $t_N$ prevent longer draining times), allowing the ionization state to be relatively representative of the electron temperature such that $\mathrm{EM}(T)\approx\mathrm{EM}(T_{eff})$.
 	%
@@
 	%%
-	\par\hl{Lead in with how EM ratio is better, i.e. not masquerading as a fit, just a single point; discussion of results from Brosius, how lines were chosen, then discuss histograms and types.}
-	%%
 	\begin{figure*}
@@
 \textbf{Right:} Emission measure ratios separated by waiting time, $t_N$.
-For aesthetic purposes, we only show five values of $t_N$.}
+For aesthetic purposes, only five values of $t_N$ are shown.}
 		\label{fig:em_ratio_hist_el}
@@
 	%%
-	\par\hl{Probably cut most of this..}
-	%
-	\par The main points we emphasize from the results presented in \autoref{sec:results} are,
-	\begin{enumerate}
-		\item Cool emission measure slopes resulting from electron and ion heating are very similar and are well described by $\mathrm{EM}\propto T^a$.
-As noted in \citet{cargill_active_2014}, using the relation $Q\propto T_N^{\beta}$ yields $2\lesssim a\lesssim5$, consistent with observations.\label{itm:cool}
-		\item Hot emission from electron heating results in an enhanced hot shoulder while the equivalent ion heating cases show a relatively flat peak and a steep dropoff near $10^7$ K.
-This effect is exacerbated as $t_N$ increases.\label{itm:hot}
-		\item Hot emission due to both electron and ion heating is poorly described by the scaling $\mathrm{EM}\propto T^{-b}$.
-In the former, this is due to the flat hot shoulder between $10^7$ and $10^{7.5}$ K.
-In the latter case, the relatively flat peak and steep drop off near $10^7$ K do not allow for a power-law description of the hot emission.\label{itm:deriv}
-		\item Using a power-law to describe the hot side of the $\mathrm{EM}$ distribution, single-fluid models predict less hot-emission than two-fluid models in which only the electrons are heated.
-In particular, for $T_N\ge4000$ s, our modified two-fluid EBTEL model predicts $3\le b\le3.5$ while the original single-fluid EBTEL model predicts $b\sim4.5$.\label{itm:histos}
-		\item Including NEI does not impact the cool emission measure slope.
-In the case of electron heating and the single-fluid case, NEI enhances the mid-range hot $\mathrm{EM}$, but leads to a lower temperature cutoff.
-The emission measure distribution in the case of ion heating is unaffected.
-\label{itm:nei}
-	\end{enumerate}
-	%
-	\par We first focus on \autoref{itm:cool}.
-In the range $6.0\le\log{T}\le6.6$, the loop is undergoing both radiative and enthalpy-driven cooling.
-During this phase, the density is high and the temperature low relative to the heating and conductive cooling phase.
-Looking at the fourth term on the right-hand side of \autoref{eq:press_e} and \autoref{eq:col_freq}, the coupling term between the two species is roughly $\propto\bar{n}^2(\bar{T}_e-\bar{T}_i)/\bar{T}_e^{3/2}$; as density increases, so does the coupling strength.
-While the loop is also draining in this temperature range, the density has already increased such that $\bar{T}_e\approx\bar{T}_i$ and until the next heating event, there is nothing to drive the two species out of equilibrium.
-Thus, because the two-species are evolving together in this regime, we expect their emission measure distributions to be the same.
-	%
-	\par In \autoref{itm:hot}, we see quite the opposite situation.
-In the heating and conductive cooling phases, the density is relatively low and the electron (or ion) temperature relatively high.
-Because the heating pulses we have used are relatively short (100 s), the heated species quickly reaches high temperatures and cools significantly by thermal conduction before Coulomb collisions can bring the two species back into equilibrium.
-Since the emission measure depends on the electron temperature, this means that in the event that only the electrons are heated, the emission  ``sees'' the full range of temperatures produced by heating and conductive cooling.
-	%
-	\par However, in the case of ion heating, in order for the emission measure to see the full range of temperatures resulting from the heating and conductive cooling by the ions, $\bar{T}_e=\bar{T}_i$ would have to hold for this entire phase.
-Instead, as the ions are impulsively heated, the electrons remain at a relatively low temperature, coupled only weakly to the ions because the loop has only just begun to fill.
-As the coronal density increases, the electrons come into equilibrium with the ions, but because thermal conduction is such an efficient cooling mechanism in the corona, the ions have now cooled far below the temperature to which they were initially heated.
-	\par The result is a severely truncated hot emission measure distribution as seen in \autoref{fig:ion_em}.
-Additionally, this effect is exacerbated at long $t_N$.
-For short $t_N$, the heating is essentially steady, meaning that the loop has little to no time to drain or cool between heating events.
-This keeps the density at a roughly constant, near-equilibrium value which inhibits rapid heating to high temperatures and keeps the electrons and ions in equilibrium.
-However, for longer $t_N$, the loop is allowed to drain significantly between each pulse.
-Thus, at the start of each heating event, the density is low, allowing the species to very quickly evolve out of equilibrium.
-	%
-	\par Finally, \autoref{itm:nei} addresses the fact that NEI does not affect cool emission or emission due to ion heating, while it acts to enhance mid-range hot temperature emission and creates a lower-temperature cutoff in the single-fluid and electron heating cases as shown in \autoref{fig:teff_test_case}.
-As discussed in \citetalias{barnes_inference_2016} and \autoref{sec:intro}, if the heating occurs on a timescale faster than the ionization equilibration timescale, high temperatures will not be detectable because the charge states indicative of such temperatures will not have had time to form.
-Coolward emission is due to radiative and enthalpy-driven cooling and during this phase, the density is relatively high and the temperature is changing relatively slowly, meaning that ionization equilibrium can be assumed.
-	\par For hotward emission in the case of ion heating, we note that the effective heating timescale for the electrons is approximately $\tau_{ei}$, the coupling timescale.
-For $Q\approx10^{25}$ erg, the electron temperature increases relatively slowly (compared to the heating timescale of the ions) and only gets above several MK once the density has increased significantly.
-Thus, ionization equilibrium can be assumed because the electrons undergo no direct impulsive heating.
-In the cases of electron heating and the single-fluid case, the electrons undergo direct impulsive heating when the density is relatively low.
-This is what leads to the lower-temperature cutoff in $EM_{eff}$: at these high temperatures and low densities, the ionization equilibration timescale is significantly longer than the heating timescale and so these very high temperatures are never seen.
 	%
@@
 	%
-	\par In this paper, we have used a modified two-fluid version of the popular EBTEL model to study the effect of preferentially heating the electrons or ions on the hot and cool emission measure slopes over a parameter space that includes the power-law index describing the distribution of event energies, $\alpha$, waiting time between successive heating events, $t_N$, and the scaling between the event energy and wait time, $\beta$.
-We have found that while there is little difference in the cool emission between the cases of electron and ion heating, the emission measure curves of the electron-heated loops have an enhanced hot shoulder due to faster loop filling times and steepened hot mid-range slope due to accelerated cooling by the Coulomb collisions while the ion-heated loops show a truncated emission measure distribution on the hot side.
-These differences become more prominent as $t_N$ increases.
-We note that given such a distinction in the $\mathrm{EM}$ distribution between the cases of electron and ion heating, the difference could be potentially observationally diagnosable by instruments such as MaGIXS, the Focusing Optics X-ray Solar Imager (FOXSI) \citep{krucker_focusing_2011}, or other future missions with adequate spectroscopic resolution in the hard X-rays.
-	\par Furthermore, by comparing these results with emission measure distributions obtained from the original single-fluid EBTEL model, we have found that heating only the electrons and using a single power-law fit leads to significantly smaller hot emission measure slopes for equivalent values of $t_N$.
-Thus, using a single-fluid model to interpret observed hot emission measure distributions can potentially lead to a misdiagnosis of the heating frequency.
-Additionally, characterizing the hotward emission with a single power-law fit, as is common practice with cool emission, does not adequately capture all of the features of the hotward emission.
-	%
-	\par We note that in this study, we have constructed the most ideal emission measure curves by using the expression $\mathrm{EM}=n^2(2L)$; that is, we have not taken into account the many complications involved when computing emission measure distributions from observed spectral lines.
-For example, as we noted in \citetalias{barnes_inference_2016}, impulsive heating leads to NEI and a consequently lower effective temperature, meaning that the emission does not see the hottest temperatures during the conductive cooling phase.
-By computing test cases for electron heating, ion heating, and the single-fluid case, we have shown that NEI has the effect of steepening the hot emission measure distribution at very high temperatures and enhancing the mid-range hot temperature emission for the electron heating and single-fluid cases, but has no impact on the emission measure distribution in the case of ion heating.
-We stress that when interpreting observed hot emission in the context of simulation, two-fluid and non-equilibrium ionization effects should be properly taken into account in order to extract meaningful properties of the heating.
 	%

### 2016-06-28 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
finished out draft of results section, one round of corrections, some ideas for conclusions; first draft to PC

@@
 However, measurement of the heating frequency, through both direct and indirect means, has proved challenging.
-With regard to the direct evidence of reconnection-driven (DC) heating, only recently have observations provided sufficient resolution to resolve magnetic field braiding \citep{cirtain_energy_2013}, a supposed precursor to bursty energy release.
-Additionally, while the resulting AR core emission measure distribution holds many clues as to how the coronal plasma is heated and cools, reconstructing these $\mathrm{EM}$ from spectroscropic and narrow-band observations is non-trivial, with differrent inversion methods often giving significantly different results \citep{landi_monte_2012,aschwanden_benchmark_2015}.
+With regard to direct evidence of reconnection-driven (DC) heating, only recently have observations provided sufficient resolution to resolve magnetic field braiding \citep{cirtain_energy_2013}, a possible precursor to bursty energy release.
+Additionally, while the resulting AR core emission measure distribution holds many clues as to how the coronal plasma is heated and cools, reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with differrent inversion methods often giving significantly different results \citep{landi_monte_2012,aschwanden_benchmark_2015}.
 Efforts to measure the heating frequency through intensity fluctuations in AR cores have proved similarly difficult \citep{ugarte-urra_determining_2014}.
@@
 	%
-	\par We define our heating function in terms of a series of discrete heating events plus a static background heating to ensure that the loop does not drop to unphysically low temperatures and densities between events.
-Thus, for loop half-length $L$ and cross-sectional area $A$, for a triangular heating pulse of duration $\tau$, the total  event energy is $\varepsilon=LAH\tau/2$, where $H$ is the heating rate.
-Each run will consist of $N$ heating events, each with peak amplitude $H_i$, and a steady background value of $H_{bg}=3.5\times10^{-5}$ erg cm$^{-3}$ s$^{-1}$.
-	%
 	\begin{figure}
@@
 		\includegraphics[width=\columnwidth]{figures/heating_functions.pdf}
-		\caption{\textbf{Top}: uniform heating amplitudes for $t_N=1000$ s; \textbf{Middle:} uniform heating amplitudes for $t_N=5000$ s; \textbf{Bottom:} Heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$.
+		\caption{\textbf{Top}: Uniform heating amplitudes for $t_N=1000$ s; \textbf{Middle:} Uniform heating amplitudes for $t_N=5000$ s; \textbf{Bottom:} Heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$.
 The events shown in red have wait times that depend on the previous event energy while the events shown in blue have uniform wait times.
-The mean wait time in both cases is $\langle t_N\rangle=2000$ s.}
+The mean wait time in both cases is $t_N=2000$ s.}
 		\label{fig:heating_funcs}
@@
 	%
+	\par We define our heating function in terms of a series of discrete heating events plus a static background heating to ensure that the loop does not drop to unphysically low temperatures and densities between events.
+For a triangular heating pulse of duration $\tau$ injected into a loop of half-length $L$ and cross-sectional area $A$, the total  event energy is $\varepsilon=LAH\tau/2$, where $H$ is the heating rate.
+Each model run will consist of $N$ heating events, each with peak amplitude $H_i$, and a steady background heating of $H_{bg}=3.5\times10^{-5}$ erg cm$^{-3}$ s$^{-1}$.
+	%
 	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}.
-Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim3.6\times10^{-3}$.
+Using our modified two-fluid EBTEL model, we have estimated the time-averaged volumetric heating rate needed to kepp a loop of half-length $L=40$ Mm at $\bar{T}\approx4$ MK as  $H_{eq}\sim3.6\times10^{-3}$.
 In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored.
@@
 Note that because $t_{total}$ and $\tau$ are fixed, as $t_N$ increases, $N$ decreases.
-Correspondingly, $\varepsilon_i=LA\tau H_i/2$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant, independent of $t_N$.
+Correspondingly, $\varepsilon_i=LA\tau H_i/2$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant.
 	%
@@
 	\par According to the nanoflare heating model of \citet{parker_nanoflares_1988}, turbulent loop footpoint motions twist and stress the field, leading to a buildup and subsequent release of energy.
-Following \citet{cargill_active_2014}, we let $\varepsilon_i\propto t_{N,i}^{\beta}$, where $\varepsilon_i,t_{N,i}$ are the total energy and waiting time following event $i$, respectively, and $\beta=1$ such that the event energy scales linearly with the waiting time.
+Following \citet{cargill_active_2014}, we let $\varepsilon_i\propto t_{N,i}^{\beta}$, where $\varepsilon_i,t_{N,i}$ are the total energy of event $i$ and waiting time following event $i$, respectively, and $\beta=1$ such that the event energy scales linearly with the waiting time.
 The reasoning for such an expression is as follows.
@@
 This procedure is repeated $N_R$ times until $N\times N_R\sim10^4$ is satisfied.
-Thus, when $t_N=5000$ s and $N\sim15$, $N_R=625$, meaning the model is run 625 times with a heating frequency of $t_N=5000$ s in order to properly fill out the event energy distribution.
+Thus, when $t_N=5000$ s and $N\sim16$, $N_R=625$, meaning the model is run 625 times with a heating frequency of $t_N=5000$ s in order to properly fill out the event energy distribution.
 	%
@@
 	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results.
-Given a temperature ($T(t)$) and density ($n(t)$) profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$ that would be inferred by assuming ionization equilibrium.
-Using $T_{eff}$, we are then able to compute a corresponding NEI emission measure distribution.
+Given a temperature ($T(t)$) and density ($n(t)$) profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$, that would be inferred by assuming ionization equilibrium.
+Using $T_{eff}$, we are then able to compute a corresponding NEI emission measure distribution, $\mathrm{EM}(T_{eff})$.
 	%%
@@
 In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s.
-The average interval between subsequent events is $t_N$ (in the uniform and power-law case, $t_N,i=t_N$ exactly for all $i$).
+The average interval between subsequent events is $t_N$ (in the uniform and $\beta=0$ cases, $t_{N,i}=t_N$ exactly for all $i$).
 We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$.
@@
 The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).
-The solid lines in the power-law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean.
-The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}
+The solid lines in the two power-law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean.
+The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.
+The standard deviation is not included in the NEI results.}
 		\label{fig:single_em}
@@
 \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions in the single-fluid case, electron heating case, and ion heating case, respectively.
-Each panel in each figure corresponds to a different waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a power-law distribution of index $\alpha=-2.5$ (blue), and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event (green).
+Each panel in each figure corresponds to a different waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a power-law distribution of index $\alpha=-2.5$ ($\beta=0$ case, blue), and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event ($\beta=1$ case, green).
+Note that in all three figures, we show the results for only a single power-law index, $\alpha=2.5$.
 Furthermore, the dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$.
 	%
-	\par Recall from \autoref{subsec:heating_stats} that for those heating functions which choose peak heating rates from a power-law distribution, for each $t_N$, we run the model $N_R\sim(t_N+200)/8$ times.
+	\par Recall from \autoref{subsec:heating_stats} that for those heating functions which choose peak heating rates from a power-law distribution, for each $t_N$, we run the model $N_R$ times.
 Thus, for each point in our parameter space, we produce $N_R$ $\mathrm{EM}(T)$ curves.
-In order to present our results compactly, the panels of \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} each show the average over all $N_R$ curves.
+In order to present our results compactly, the solid lines in \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} each show the mean $\mathrm{EM}(T)$ over all $N_R$ curves.
+The shading represents $1\sigma$ from the mean.
 In this way, we account for the variations that may occur because of a lack/excess of strong heating events due to limited sampling from the distribution.
@@
 	\par Looking at the different curves in each panel of \autoref{fig:single_em}, it is important to note that, although $\mathrm{EM}(T)$ for all three types of heating functions widen with increasing wait time, their dependence on $t_N$ is quite different.
-The uniform (red) and power-law (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the power-law, $\beta=1$ curve (green) extends to cooler temperatures much more rapidly.
-For example, at $t_N=1500$ s, both the uniform and power-law cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK \citep{cargill_active_2014}.
-Contrastingly, on the hot side, the power-law and $\beta=1$ curves evolve nearly identically with increasing $t_N$ while the unfiorm heating case shows a cutoff at much lower temperatures, particularly for $t_N\le2500$ s.
+The uniform (red) and $\beta=0$ (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the $\beta=1$ curves (green) extend to cooler temperatures much more rapidly.
+For example, at $t_N=1500$ s, both the uniform and $\beta=0$ cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK \citep{cargill_active_2014}.
+Contrastingly, on the hot side, the $\beta=0$ and $\beta=1$ curves evolve nearly identically with increasing $t_N$ while the unfiorm heating case shows a cutoff at much lower temperatures, particularly for $t_N\le2500$ s.
 	%
@@
 On the hot side, for $t_N\le750$ s, the electron and single-fluid cases are quite similar.
-However, for $t_N\ge1500$ s, $\mathrm{EM}(T)$ steepens just above 4 MK and then flattens out near 10 MK.
+However, for $t_N\ge1500$ s, in the electron heating case, $\mathrm{EM}(T)$ steepens just above 4 MK and then flattens out near 10 MK.
 This change in shape is most obvious in the uniform heating case where a distinct ``hot shoulder'' forms just above 10 MK.
-In the power-law cases, this feature is less pronounced and the $\mathrm{EM}(T)$ extends to slightly higher temperatures.
+In the power-law cases, this feature is less pronounced though $\mathrm{EM}(T)$ extends to slightly higher temperatures.
 	%
@@
 This is discussed in \citetalias{barnes_inference_2016} though in the single-pulse cases, the cutoff occured at lower temperatures.
-Additionally, in both the uniform and power-law cases, the peak of the $\mathrm{EM}(T)$ is wider for these low frequencies compared to those cases shown in \autoref{fig:single_em} and \autoref{fig:el_em}.
+Additionally, in both the uniform and power-law cases, the peak of $\mathrm{EM}(T)$ is wider for these low frequencies compared to those cases shown in the lower right panels of \autoref{fig:single_em} and \autoref{fig:el_em}.
 	%
@@
 Contrastingly, in the uniform case, $T_{max,0}<10$ MK such that $\mathrm{EM}(T)$ has a steep cutoff right at 10 MK.
-Additionally, we note that the only effect of the longer wait times in the $\beta=1$ case as compared to the $\beta=0$ power-law case is an extended cool emission measure; the hot part of $\mathrm{EM}(T)$ for both power-law cases is nearly identical.
-This provides further evidence for these two portions of the emission measure distribution being largely independent as they are determined by separate phases of the loop evolution.
+Additionally, we note that the only effect of the longer wait times in the $\beta=1$ case as compared to the $\beta=0$ case is an extended cool emission measure at intermediation frequencies (e.g.
+$t_N=2500$ s); the hot part of $\mathrm{EM}(T)$ for both power-law cases is nearly identical.
+In this way, the hot and cool sides of the emission measure distribution are largely isolated from one another as they are determined by separate phases of the loop evolution.
 	%
@@
 So even for the lowest heating frequency in the uniform case, the heating rate is still much lower.
-Furthermore, for low $t_N$, between each event the loop is allowed to drain to its equilibrium value (as determined by the background heating) such that events with a heating rate $H_0\approx0.2$ erg cm$^{-3}$ s$^{-1}$ are injected into a low-density loop, meaning that the ionization state will not be able to keep pace with the subsequently rapid rise in temperature, resulting in $\mathrm{EM}(T_{eff})$ having a lower temperature cutoff.
-On the other hand, when the heating events are selected from a power-law, events with $H_i>0.2$ erg cm$^{-3}$ s$^{-1}$ can be injected into a much higher density loop (because lower values of $t_N$ prevent longer draining times), allowing the ionization state to be relatively representative of the electron temperature such that $\mathrm{EM}(T)\approx\mathrm{EM}(T_{eff})$.
+Furthermore, for $t_N=5000$ s, the lowest heating frequency considered here, the loop is allowed to drain to its equilibrium value (as determined by the background heating) between each event such that events with a heating rate $H_0\approx0.2$ erg cm$^{-3}$ s$^{-1}$ are injected into a low-density loop, meaning that the ionization state will not be able to keep pace with the subsequently rapid rise in temperature, resulting in $\mathrm{EM}(T_{eff})$ having a lower temperature cutoff.
+On the other hand, when the heating events are selected from a power-law distribution, events with $H_i>0.2$ erg cm$^{-3}$ s$^{-1}$ can be injected into a much higher density loop (because lower values of $t_N$ prevent longer draining times).
+This allows the ionization state to be relatively representative of the electron temperature such that $\mathrm{EM}(T)\approx\mathrm{EM}(T_{eff})$.
 	%
@@
 	\par\autoref{fig:em_slope_varying_bounds} shows an example of how both $T^a$ and $T^{-b}$ can be fit to the cool and hot sides of $\mathrm{EM}(T)$, respectively.
-We fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}.
+We select a single sample run from our parameter space in which only the electrons are heated by the events chosen from a power-law distribution of $\alpha=-2.5$ and spaced uniformly by an interval of $t_N=5000$ s.
+We calculate the resulting $\mathrm{EM}(T)$ and fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}.
 We fix the lower limit on each interval such that $T_{c,min}=10^{5.7}$ K and $T_{h,min} = 10^{6.7}$  K and vary the upper limits over $10^{6.1}<T_{c,max}<10^{6.5}$ and $10^{6.8}<T_{h,max}<10^{7.2}$.
-The left panel of \autoref{fig:em_slope_varying_bounds} shows the $a$ (blue) and $b$ (red) as a function upper limit of the fit interval, $T_{c,max}$ (bottom axis) and $T_{h,max}$ (top axis), respectively.
+The left panel of \autoref{fig:em_slope_varying_bounds} shows $a$ (blue) and $b$ (red) as a function upper limit of the fit interval, $T_{c,max}$ (bottom axis) and $T_{h,max}$ (top axis), respectively.
 The shading denotes the uncertainty of the fit.
@@
 	%%
-	\par\citet{brosius_pervasive_2014}, using observations of an active region from the EUNIS-13 sounding rocket, found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside, providing possible evidence for impulsive heating.
+	\par\citet{brosius_pervasive_2014}, using observations of an active region from the \textit{EUNIS-13} sounding rocket, found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside, providing possible evidence for impulsive heating.
 As a proxy for this intensity ratio and an alternative to the hot emission measure slope $b$, we propose using an emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$.
-Unlike an emission measure slope, a simple emission measure ratio gives information about the emission at only a single ``hot'' temperature relative to the cool side.
-Here, we choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}\approx2\times10^6$ K, the latter slightly higher than the formation temperature of Fe XII such that the emission measure ratio is less sensitive to variations in the cool emission and thus a more accurate measure of the amount of hot plasma.
+Unlike an emission measure slope, a simple emission measure ratio gives information about the emission at only a single ``hot'' temperature relative to a single ``cool'' temperature.
+We choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}\approx2\times10^6$ K, the latter slightly higher (closer to $T_{peak}\approx4$ MK) than the formation temperature of Fe XII such that the emission measure ratio is less sensitive to variations in the cool emission and thus a more accurate measure of the amount of hot plasma.
 	%
@@
 The left panel of \autoref{fig:em_ratio_hist_el} shows the case in which only the electrons are heated, where each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function.
-This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$.
+This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$ and $t_{N,i}=t_N$ for all $i$ (i.e.
+$\beta=0$).
 We see that the emission measure ratio is largely insensitive to $\alpha$ and is peaked sharply at approximately $0.25$; the distribution peaks at slightly higher values for the $\beta=1$ case though the overall shape of the distribution is the same.
@@
 We find that for $t_N\le3000$ s, the emission measure ratios are largely clustered below 0.5, with $t_N=2000,3000,4000$ s peaking between $\sim0.3-0.45$.
-It seems that the value of the emission measure ratio is more sensitive to the heating frequency for $t_N>4000$ s.
+For $t_N>4000$ s, the emission measure ratio seems to be more sensitive to the heating frequency .
 	%
-	\par Similarly, we compute this same emission measure ratio for the case in which only the ions are heated.
+	\par Similarly, we compute the same emission measure ratio for the case in which only the ions are heated.
 The left panel of \autoref{fig:em_ratio_hist_ion} shows histograms for each type of heating function.
-Similar to the electron heating results, we find that the $\beta=0$ distributions peak at lower values compared to the $\beta=1$ distributions and that in the $\beta=0$ case, the distribution of emission measures ratios is relatively insensitive to $\alpha$.
+Similar to the electron heating results, we find that the $\beta=0$ distributions peak at lower values compared to the $\beta=1$ distributions and that in the $\beta=0$ case, the distribution of emission measure ratios is relatively insensitive to $\alpha$.
 However, unlike the electron heating case, the distributions in all cases are much wider and peak at higher values, $\sim0.5$ for $\beta=0$ and $>1$ for $\beta=1$.
@@
 The right panel of \autoref{fig:em_ratio_hist_ion} shows the same emission measure ratios now grouped by waiting time where again we only show five values of $t_N$.
-With the exception of the $t_N=2000$ s and $t_N=3000 s$ group, the distributions for each value of $t_N$ are much more spread out (as compared \autoref{fig:em_ratio_hist_el}).
+With the exception of the $t_N=2000$ s and $t_N=3000$ s group, the distributions for each value of $t_N$ are much more spread out (as compared \autoref{fig:em_ratio_hist_el}).
 In particular, $t_N=5000$ s peaks above 1.0 and extends past 1.5 while $t_N=1000$ peaks near 0 and drops off very steeply before 0.5.
@@
 	%%
+	\begin{enumerate}
+	\item \hl{$>10$ MK present in nanoflare train runs relative to single pulse results from paper I}
+	\item \hl{consistency of results with Cargill (2014) on the cool side; unsuitability of the hot emission measure slope}
+	\item \hl{importance of density preconditioning in departures from IEQ} 
+	\item \hl{emission measure ratio results in light of Brosius et al, 2014}
+	\item \hl{can we say something about possible heating frequencies? likelihood of electron heating over ion heating?}
+	\end{enumerate}
 	%
@@
 	\bibliographystyle{apj}
+	%\bibliography{hot_non-flaring_plasma_2.bbl}
 	\clearpage

### 2016-07-20 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
removing periods after St Andrews
adding PC edits in intro, small changes to methodology

@@
 	\affil{Space and Atmospheric Physics, The Blackett Laboratory, Imperial College, London SW7 2BW}
-	\affil{School of Mathematics and Statistics, University of St. Andrews, St. Andrews, Scotland KY16 9SS}
+	\affil{School of Mathematics and Statistics, University of St Andrews, St Andrews, Scotland KY16 9SS}
 	\and
@@
 	%
-	\par Heating of the solar corona by nanoflares, first proposed by \citet{parker_nanoflares_1988}, has become one of the most favored and contentious coronal heating models  \citep{cargill_implications_1994,cargill_nanoflare_2004,klimchuk_solving_2006}.
-The term \textit{nanoflare} has now become synonomous with impulsive heating in the energy range $10^{24}-10^{27}$ erg, with no specific assumption regarding the underlying physical mechanism; though its origin is almost certainly magnetic.
+	\par The concept of heating the solar corona by nanoflares, first proposed by \citet{parker_nanoflares_1988}, has been developed extensively over the past two decades \citep[e.g.][]{cargill_implications_1994,cargill_nanoflare_2004,klimchuk_solving_2006}.
+The term \textit{nanoflare} has now become synonomous with impulsive heating in the energy range $10^{24}-10^{27}$ erg, with no specific assumption regarding the underlying physical mechanism (for example, small-scale magnetic reconnection or hydromagnetic wave dissipation).
 	%
-	\par \citet{cargill_implications_1994,cargill_nanoflare_2004} have predicted that emission measure distributions resulting from nanoflare models should be wide and have a faint, high-temperature (8-10 MK) component, the so-called ``smoking gun'' of nanoflare heating.
-Though many workers \citep{reale_evidence_2009,schmelz_hinode_2009,miceli_x-ray_2012,testa_hinode/eis_2012,del_zanna_elemental_2014,petralia_thermal_2014,schmelz_hot_2015} have claimed evidence of this hot, faint component of the emission measure, poor spectral resolution \citep{testa_temperature_2011,winebarger_defining_2012} and non-equilibrium ionization \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008} have made a positive detection of nanoflare heating difficult.
-However, \citet{brosius_pervasive_2014}, using observations from the \textit{EUNIS-13} sounding rocket, identified relatively faint emission from Fe XIX in a non-flaring active region (AR), suggesting temperatures of $\sim8.9$ MK.
+	In active region (AR) cores such as those we discuss in this paper, one strategy for constraining potential heating models is the analysis of the emission measure distribution as a function of temperature, $\mathrm{EM}(T)=\int n^2\mathrm{d}h$.
+\citet{cargill_implications_1994,cargill_nanoflare_2004} predicted that $\mathrm{EM}(T)$ resulting from nanoflare heating should be wide, with a maximum value at $T=T_m\sim10^{6.5}$ K and have a faint, high-temperature (8-10 MK) component.
+Below $T_m$, there is a scaling $\mathrm{EM}(T)\sim T^a$ over a temperature range $10^6\lesssim T\lesssim T_m$, a result first discussed by \citet{jordan_structure_1975}.
+Observations from the \textit{Hinode} spacecraft \citep{kosugi_hinode_2007} have shown that $2\lesssim a\lesssim5$, with $T_m\approx10^{6.5-6.6}$ \citep{warren_constraints_2011,warren_systematic_2012,winebarger_using_2011,tripathi_emission_2011,schmelz_cold_2012,del_zanna_evolution_2015}.
 	%
-	\par One strategy for constraining potential heating models is analysis of modeled and observed emission measure distributions in active region (AR) cores.
-Originally proposed by \citet{jordan_structure_1975}, it is well-known that the emission measure, $\mathrm{EM}(T)=\int n^2\mathrm{d}h$, scales as $\mathrm{EM}(T)\sim T^a$ over a temperature range $10^6\lesssim T\lesssim T_m$, where $T_m$ is the temperature at which $\mathrm{EM}(T)$ peaks.
-Observations have shown that $2\lesssim a\lesssim5$, with $T_m\approx10^{6.5-6.6}$ \citep{warren_constraints_2011,warren_systematic_2012,winebarger_using_2011,tripathi_emission_2011,schmelz_cold_2012,del_zanna_evolution_2015}.
+	\par The emission component above $T_m$ has been the subject of less study, but is likely to be important as the so-called ``smoking gun'' of nanoflare heating since its properties may bear a close link to the actual heating.
+While many workers \citep{reale_evidence_2009,schmelz_hinode_2009,miceli_x-ray_2012,testa_hinode/eis_2012,del_zanna_elemental_2014,petralia_thermal_2014,schmelz_hot_2015} have claimed evidence of this hot, faint component of the emission measure, poor spectral resolution \citep{testa_temperature_2011,winebarger_defining_2012} and non-equilibrium ionization \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008} have made a positive detection of nanoflare heating difficult.
+However, \citet{brosius_pervasive_2014} used observations from the \textit{EUNIS-13} sounding rocket to identify relatively faint emission from Fe XIX in a non-flaring active region (AR), suggesting temperatures of $\sim8.9$ MK.
 	%
-	\par A similar scaling has been claimed for hot emission such that $\mathrm{EM}\propto T^{-b}$.
-Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $T_m\lesssim T\lesssim10^{7.2}$.
-However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}.
+	\par A scaling has been claimed for hot emission with $T>T_m$ such that $\mathrm{EM}\propto T^{-b}$, with $b>0$.
+This fit is usually done in the range $T_m\lesssim T\lesssim10^{7.2}$.
+However, measured values of these ``hotward" slopes are poorly constrained due to both the low magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}.
 \citet{warren_systematic_2012}, find $7\lesssim b\lesssim10$, with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$.
+It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with differrent inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013,aschwanden_benchmark_2015}.
 	%
-	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release.
-Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating.
-In the case of high-frequency heating, $t_N$, the time between successive events, is such that $t_N\ll\tau_{cool}$, where $\tau_{cool}$ is the loop cooling time, and in the case of low-frequency heating $t_N\gg\tau_{cool}$ \citep{cargill_modelling_2015}.
+	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release along a single magnetic strand, where the observed loop comprises many such strands.
+Nanoflare heating can be classified as being either a \textit{high-} or \textit{low-frequency}.
+In the case of high-frequency (HF) heating, $t_N$, the time between successive events, is such that $t_N\ll\tau_{cool}$, where $\tau_{cool}$ is a characteristic loop cooling time, and in the case of low-frequency (LF) heating $t_N\gg\tau_{cool}$ \citep{mulu-moore_can_2011,warren_constraints_2011,bradshaw_diagnosing_2012,reep_diagnosing_2013,cargill_modelling_2015}.
 Steady heating is just high-frequency heating in the limit $t_N\to0$.
+While a determination of $t_N$ is of great importance, its measurement is challenging.
+For example, while direct observations of possible reconnection-associated heating through short timescale changes in loop structure and emission is feasible, as demonsrated by the Hi-C rocket flight \citep{cirtain_energy_2013,cargill_solar_2013}, longer duration observations are required to constrain $t_N$.
+The previously-mentioned difficulties in reconstructing $\mathrm{EM}(T)$ must also be bourne in mind.
+Efforts to measure the heating frequency using narrow-band observations of intensity fluctuations in AR cores  have proved similarly difficult \citep{ugarte-urra_determining_2014}.
 	%
-	\par The frequency of energy release in the solar corona is an important piece of evidence for determining the yet unknown coronal heating mechanism(s).
-However, measurement of the heating frequency, through both direct and indirect means, has proved challenging.
-With regard to direct evidence of reconnection-driven (DC) heating, only recently have observations provided sufficient resolution to resolve magnetic field braiding \citep{cirtain_energy_2013}, a possible precursor to bursty energy release.
-Additionally, while the resulting AR core emission measure distribution holds many clues as to how the coronal plasma is heated and cools, reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with differrent inversion methods often giving significantly different results \citep{landi_monte_2012,aschwanden_benchmark_2015}.
-Efforts to measure the heating frequency through intensity fluctuations in AR cores have proved similarly difficult \citep{ugarte-urra_determining_2014}.
-	%
-	\par Hydrodynamic loop models, combined with sophisticated forward modeling, provide an accurate method for assessing a wide variety of heating scenarios and calculating observables.
-Such models of nanoflare-heated loops have found emission measure slopes consistent with those derived from observations.
-While \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$.
+	\par The use of hydrodynamic loop models, combined with sophisticated forward modeling, is a useful method for assessing a wide variety of heating scenarios.
+Such models of nanoflare-heated loops have found emission measure slopes consistent with those derived from observations in the temperature range $T<T_m$.
+For example, while \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$.
 \citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<t_N<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the full range of observed emission measure slopes be found.
 	%
-	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares.
-We found that emission signatures of the heating are likely to be found in the temperature range $4\lesssim T\lesssim 10$ MK.
-We now turn our attention to repeated impulsive events on a single strand.
+	\par An analogous approach can be used to investigate the properties of the ``hot" coronal component expected from nanoflare heating, and is the subject of the present series of papers.
+In \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we looked at the hot plasma properties due to a single isolated nanoflare.
+The effects of heating pulse duration, changes to conductive cooling due to heat flux limiting, differential heating of electrons and ions, and non-equilibrium ionization (NEI) were studied.
+It was shown that signatures of nanoflare heating are likely to be found in the temperature range $4\lesssim T\lesssim 10$ MK.
+The prospect of measurable signatures above $10$ MK was found to be diminished for short heating pulses (with duration $<100$ s), NEI, and differential heating of the ions rather than the electrons.
+It is important to stress for a single nanoflare that while the ``hot'' plasma is present, it cannot actually be detected.
+\hl{EXPAND/MODIFY??}
 	%
-	\par In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of repeated impulsive heating events of varying frequency on the resulting $\mathrm{EM}(T)$.
-In particular, we look at how the hot emission is affected by heating preferentially the electrons or the ions, with events drawn from a power-law distribution versus uniform heating rates.
-Additionally, we investigate the effect of scaling the inter-event waiting time to the event energy and as well as how NEI may affect the presence of hot emission.
-We use an emission measure ratio, similar to that of \citet{brosius_pervasive_2014}, to assess the relative importance of hot emission over the entire range of power-law indices and heating frequencies.
+	\par However, nanoflare heating requires that we consider a ``train'' of nanoflares along a magnetic strand \hl{(REFERENCES??)}.
+While a single nanoflare in the LF heating scenario will always occur in a plasma of characteristic AR density ($\sim10^9$ cm$^{-3}$), with significant consequences.
+In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$.
+Preferential species heating, NEU, power-law nanoflare distributions, and the effects of a variable $t_N$ between events are considered and an emission measure ratio metric, similar to that discussed in \citet{brosius_pervasive_2014}, is used to characterize the various results.
 \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated.
@@
 	\begin{align}
-		\frac{d}{dt}\bar{p}_e &= \frac{\gamma - 1}{L}\left\lbrack\psi_{TR} - (\mathcal{R}_{TR} + \mathcal{R}_C)\right\rbrack + \\ &k_B\bar{n}\nu_{ei}(\bar{T}_i - \bar{T}_e) + (\gamma - 1)\bar{Q}_e,\label{eq:ebtel2fl_pe}\\
-		\frac{d}{dt}\bar{p}_i &= -\frac{\gamma - 1}{L}\psi_{TR} + k_B\bar{n}\nu_{ei}(\bar{T}_e - \bar{T}_i) +\\ &(\gamma - 1)\bar{Q}_i,\label{eq:ebtel2fl_pi}\\
+		\frac{d}{dt}\bar{p}_e &= \frac{\gamma - 1}{L}\left\lbrack\psi_{TR} - (\mathcal{R}_{TR} + \mathcal{R}_C)\right\rbrack + \nonumber\\ &k_B\bar{n}\nu_{ei}(\bar{T}_i - \bar{T}_e) + (\gamma - 1)\bar{Q}_e,\label{eq:ebtel2fl_pe}\\
+		\frac{d}{dt}\bar{p}_i &= -\frac{\gamma - 1}{L}\psi_{TR} + k_B\bar{n}\nu_{ei}(\bar{T}_e - \bar{T}_i) +\nonumber\\ &(\gamma - 1)\bar{Q}_i,\label{eq:ebtel2fl_pi}\\
 		\frac{d}{dt}\bar{n} &= \frac{c_2(\gamma - 1)}{c_3\gamma Lk_B\bar{T}_e}\left(\psi_{TR} - F_{ce,0} - \mathcal{R}_{TR}\right),\label{eq:ebtel2fl_n}
@@
 	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency and $\psi_{TR}$ is a term included to maintain charge and current and neutrality.
+Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional corrections detailed in Appendix 1 of \citetalias{barnes_inference_2016}.
 These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$.
@@
 	%
-	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}.
-Using our modified two-fluid EBTEL model, we have estimated the time-averaged volumetric heating rate needed to kepp a loop of half-length $L=40$ Mm at $\bar{T}\approx4$ MK as  $H_{eq}\sim3.6\times10^{-3}$.
+	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{m}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}.
+Using our modified two-fluid EBTEL model, we have estimated the time-averaged volumetric heating rate needed to keep a loop of half-length $L=40$ Mm at $\bar{T}\approx4$ MK as  $H_{eq}\sim3.6\times10^{-3}$.
 In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored.
-Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by
+Thus, to maintain an emission measure peaked about $T_{m}$, for triangular pulses, the individual event heating rates are constrained by
 	\begin{equation}
@@
 	%
-	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$).
+	\par We now show the results of our loop simulations for each point in our multidimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$).
 In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s.
@@
 	\bibliography{astrophys-abbrev.bib,references.bib}
-	\bibliographystyle{apj}
+	\bibliographystyle{aasjournal}
 	%\bibliography{hot_non-flaring_plasma_2.bbl}

### 2016-07-22 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex

@@
-\documentclass[apj]{emulateapj}
+\documentclass[preprint2,linenumbers]{aastex}
 
@@
 \usetikzlibrary{shapes.geometric, arrows}
-\usepackage[tight]{subfigure}
-\usepackage[breaklinks,colorlinks,citecolor=blue]{hyperref}
 \usepackage[all]{hypcap}
@@
 \usepackage{enumitem}
-%use for editing/highlighting
-\usepackage{color,soul}
-%\usepackage{lineno}
 
@@
 	\shorttitle{``Hot'' Non-flaring Plasmas II. Nanoflare Trains}
-	\author{W. T. Barnes}
-	\affil{Department of Physics \& Astronomy, Rice University, Houston, TX 77251-1892}
-	\email{will.t.barnes@rice.edu}
-	\author{P. J. Cargill}
-	\affil{Space and Atmospheric Physics, The Blackett Laboratory, Imperial College, London SW7 2BW}
-	\affil{School of Mathematics and Statistics, University of St Andrews, St Andrews, Scotland KY16 9SS}
+	\author{W. T. Barnes\altaffilmark{1}}
+	\author{P. J. Cargill\altaffilmark{2,3}}
 	\and
-	\author{S. J. Bradshaw}
-	\affil{Department of Physics \& Astronomy, Rice University, Houston, TX 77251-1892}
+	\author{S. J. Bradshaw\altaffilmark{1}}
+	%affiliations
+	\altaffiltext{1}{Department of Physics \& Astronomy, Rice University, Houston, TX 77251-1892; will.t.barnes@rice.edu, stephen.bradshaw@rice.edu}
+	\altaffiltext{2}{Space and Atmospheric Physics, The Blackett Laboratory, Imperial College, London SW7 2BW; p.cargill@imperial.ac.uk}
+	\altaffiltext{3}{School of Mathematics and Statistics, University of St Andrews, St Andrews, Scotland KY16 9SS}
 	%Abstract
@@
 	\end{abstract}
+	%Keywords
+	\keywords{Sun:corona, Sun:nanoflares, plasmas, hydrodynamics}
 	%Body
@@
 	\label{sec:intro}
+	%
+	\par\authorcomment1{Maybe intro is a bit lengthy...where to cut it down?}
 	%
@@
 It is important to stress for a single nanoflare that while the ``hot'' plasma is present, it cannot actually be detected.
-\hl{EXPAND/MODIFY??}
 	%
-	\par However, nanoflare heating requires that we consider a ``train'' of nanoflares along a magnetic strand \hl{(REFERENCES??)}.
+	\par However, nanoflare heating requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}.
 While a single nanoflare in the LF heating scenario will always occur in a plasma of characteristic AR density ($\sim10^9$ cm$^{-3}$), with significant consequences.
@@
 	\begin{figure}
-		\centering
-		\includegraphics[width=\columnwidth]{figures/heating_functions.pdf}
+		\plotone{figures/heating_functions.pdf}
 		\caption{\textbf{Top}: Uniform heating amplitudes for $t_N=1000$ s; \textbf{Middle:} Uniform heating amplitudes for $t_N=5000$ s; \textbf{Bottom:} Heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$.
@@
 	%
-	\par We now show the results of our loop simulations for each point in our multidimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$).
+	\par We now show the results of our nanoflare train simulations for each point in our multidimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$).
 In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s.
@@
 	\begin{figure*}[t]
-		\centering
-		\includegraphics[width=2\columnwidth]{figures/em_grid_single_a25.pdf}
+		\plotone{figures/em_grid_single_a25.pdf}
 		\caption{Emission measure distributions for waiting-times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case.
@@
 	\begin{figure*}[t]
-		\centering
-		\includegraphics[width=2\columnwidth]{figures/em_grid_electron_a25.pdf}
+		\plotone{figures/em_grid_electron_a25.pdf}
 		\caption{Same as \autoref{fig:single_em}, but for the case where only the electrons are heated.}
@@
 	\begin{figure*}
-		\centering
-		\includegraphics[width=2\columnwidth]{figures/em_grid_ion_a25.pdf}
+		\plotone{figures/em_grid_ion_a25.pdf}
 		\caption{Same as \autoref{fig:single_em}, but for the case where only the ions are heated.}
@@
 Furthermore, the dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$.
+The cases shown in \citetalias{barnes_inference_2016} correspond approximately to the red curves in the lower right panels ($t_N=5000$ s) of each of the three figures since the loop is allowed to cool and drain completely before reheating and a single nanoflare energy is used.
 	%
-	\par Recall from \autoref{subsec:heating_stats} that for those heating functions which choose peak heating rates from a power-law distribution, for each $t_N$, we run the model $N_R$ times.
+	\par In \autoref{subsec:heating_stats}, we noted that for heating functions using a power-law energy distribution, for each $t_N$, we run the model $N_R$ times.
 Thus, for each point in our parameter space, we produce $N_R$ $\mathrm{EM}(T)$ curves.
@@
 	\par We look first at $\mathrm{EM}(T)$ for the single-fluid case, \autoref{fig:single_em}.
-Looking at all six panels, we note that as $t_N$ increases, $\mathrm{EM}(T)$ widens, extending to both cooler ($<4$ MK) and hotter ($>4$ MK) temperatures.
-$\mathrm{EM}(T)$ extends toward cooler temperatures because as $t_N$ increases and there is more time between successive heating events, the loop is allowed more time to cool both by radiation and enthalpy-driven cooling.
-$\mathrm{EM}(T)$ extends towards hotter temperatures for similar, but more subtle reasons.
-As $t_N\to0$, we approach the steady heating case in which conductive and radiative cooling exactly balance the heating.
-As $t_N$ increases and becomes comparable to and greater than a cooling time, the loop beceomes increasingly tenuous at the time of the subsequent heating event, allowing the loop to reach much hotter temperatures since radiative cooling is very inefficient at low densities and the heat flux saturates.
-In this way, $\mathrm{EM}(T)$ can ``see'' this greater range of temperatures, both hot and cool, provided it is allowed to undergo a typical heating and cooling cycle.
-The more curtailed this cycle is by continued reheatings, the more narrow $\mathrm{EM}(T)$ will be.
-	%
-	\par Looking at the different curves in each panel of \autoref{fig:single_em}, it is important to note that, although $\mathrm{EM}(T)$ for all three types of heating functions widen with increasing wait time, their dependence on $t_N$ is quite different.
+Firstly, as expected from \citet{cargill_active_2014}, as $t_N$ increases, $\mathrm{EM}(T)$ widens, extending to both cooler ($<4$ MK) and hotter ($>4$ MK) temperatures.
+The extension toward cooler temperatures arises because as $t_N$ increases there is more time between successive heating events so that the loop so that the loops cools to lower temperatures before being reheated.
+The dependence on $\alpha$ and $\beta$ is similar to that described in \citet{cargill_active_2014}.
 The uniform (red) and $\beta=0$ (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the $\beta=1$ curves (green) extend to cooler temperatures much more rapidly.
 For example, at $t_N=1500$ s, both the uniform and $\beta=0$ cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK \citep{cargill_active_2014}.
-Contrastingly, on the hot side, the $\beta=0$ and $\beta=1$ curves evolve nearly identically with increasing $t_N$ while the unfiorm heating case shows a cutoff at much lower temperatures, particularly for $t_N\le2500$ s.
+As in \citetalias{barnes_inference_2016}, the results below $T_m$ are relatively independent of which species is heated.
 	%
-	\par The $\mathrm{EM}(T)$ curves for the different types of heating functions shown in \autoref{fig:el_em}, in which only the electrons are heated, evolve similarly to those shown in \autoref{fig:single_em}.
-This is particularly true on the cool side where the density is sufficiently high, allowing the electrons and the ions to equilibrate such that there is no discernible difference compared to the single-fluid case.
+	\par The behavior of $\mathrm{EM}(T)$ above $T_m$ is more complicated.
+For small $t_N$, the emission measure distribution falls off sharply on the hot side for a uniform nanoflare train but a power law distribution leads to a broader distribution above $T_m$.
+This just reflects the different initial temperatures generated with a power-law distribution since $T \simeq H^{2/7}$.
+As $t_N$ increases, the distribution for uniform heating gradually broadens as the initial temperature rises due to the lower density in which the heating occurs.
+A similar broadening occurs for the power laws with the $\beta=0$ and $\beta=1$ results showing little difference.
+Note that the $\beta=0$ curve is barely visible as it overlaps almost completely with the $\beta=1$ curve.
+Especially interesting in this case are the results with NEI included.
+For a uniform nanoflare train, NEI plays no role up to $t_N$ = 2500 sec, but above that it restricts the temperatures that can be detected, as shown in \citetalias{barnes_inference_2016}.
+This hot emission is relocated to cooler temperatures, resulting in a ``bump'' in the emission measure distribution near 10 MK.
+On the other hand, NEI plays almost no role in the power law distributions, in both the $\beta=1$ and $\beta=0$ cases.
+	%
+	\par From these initial results, there is an important difference in the information available in potential observations.
+Below $T_m$ the value of $a$ requires a specific form of the waiting time between nanoflares which in turn informs about the nature of energy release \citep{cargill_active_2014}.
+Above $T_m$, there is no information about the role of a waiting time, but the emission measure distribution does inform about the need for a power-law energy distribution and the density in which the nanoflare occurs.
+Taken together, the overall conclusion is the same: nanoflares require an \textit{intermediate frequency}.
+	%
+	\par For electron heating, the $\mathrm{EM}(T)$ curves for the different types of heating functions shown in \autoref{fig:el_em} evolve similarly to those shown in \autoref{fig:single_em}, especially on the cool side where the density is sufficiently high such that the electrons and the ions to equilibrate.
 On the hot side, for $t_N\le750$ s, the electron and single-fluid cases are quite similar.
@@
 In the power-law cases, this feature is less pronounced though $\mathrm{EM}(T)$ extends to slightly higher temperatures.
+The conclusions regarding the role of NEI are similar to those in the single-fluid case: it is not a factor when the heating rates are determined by a power-law.
+In the uniform case, the hot emission is again truncated and relocated to cooler temperatures, with more pronounced ``bump'' in the $\mathrm{EM}(T)$ near $10$ MK.
 	%
-	\par In \autoref{fig:ion_em} in which only the ions are heated, the cool side of the $\mathrm{EM}(T)$ is very similar to both the single-fluid and electron heating cases because the electron and ion populations are in equilibrium during this portion of the loop's evolution.
+	\par When only the ions are heated (\autoref{fig:ion_em}), the cool side of the $\mathrm{EM}(T)$ is again very similar to both the single-fluid and electron heating cases due to equilibration.
 On the hot side, for intermediate to low heating frequencies (i.e.
@@
 Additionally, in both the uniform and power-law cases, the peak of $\mathrm{EM}(T)$ is wider for these low frequencies compared to those cases shown in the lower right panels of \autoref{fig:single_em} and \autoref{fig:el_em}.
-	%
-	\par The dashed lines in the panels of \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the corresponding $\mathrm{EM}(T_{eff})$ for each heating function type.
-Only the mean $\mathrm{EM}(T_{eff})$ over $N_R$ runs is shown for these results.
-In all three figures, for the intermediate to high frequencies (i.e.
-$t_N\le1500$ s), there is no discernible difference between $\mathrm{EM}(T)$ and $\mathrm{EM}(T_{eff})$.
-Furthermore, both of the power-law cases show little deviation from ionization equilibrium in the emission measure for even the lowest heating frequencies in the single-fluid, electron heating, and ion heating cases.
-For $t_N\ge2500$ s in the uniform heating case, in both \autoref{fig:single_em} and \autoref{fig:el_em}, $\mathrm{EM}(T_{eff})$ is truncated at slightly lower temperatures as compared to $\mathrm{EM}(T)$.
-This hot emission is relocated to cooler temperatures, resulting in a ``bump'' in the emission measure distribution near 10 MK.
-None of the panels of \autoref{fig:ion_em} show any significant difference between $\mathrm{EM}(T)$ and $\mathrm{EM}(T_{eff})$.
-This is because the electrons are essentially heated on a timescale dictated by the Coulomb collision frequency which is slow enough to ensure ionization equilibrium during the entire heating phase.
+Regarding the role of NEI, there is no significant difference between $\mathrm{EM}(T)$ and $\mathrm{EM}(T_{eff})$ for either the uniform or power-law cases.
+Here the electrons are essentially heated on a timescale dictated by the Coulomb collision frequency which is slow enough to ensure ionization equilibrium throughout the heating and conductive cooling phases.
 	%
@@
 	\begin{figure*}
-		\centering
-		\includegraphics[width=2\columnwidth]{figures/nT_sample_curves_tn2500_electron.pdf}
+		\plotone{figures/nT_sample_curves_tn2500_electron.pdf}
 		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for the case in which only the electrons are heated with an intermediate heating frequency of $t_N=2500$ s.
@@
 	%
+	\par In \citet{cargill_active_2014}, \citetalias{barnes_inference_2016}, and \autoref{subsec:em_dist}, we have suggested that the plasma density prior to the nanoflare occuring is a crucial parameter in determining the emission measure distribution.
+This arises in two distinct ways.
+Below $T_m$, the temperature and density at which the nanoflare occurs cuts off the emission at lower temperatures.
+When combined with an energy-dependent waiting time, this can lead to a range of EM slopes in this region \citep{cargill_active_2014}.
+Above $T_m$, the initial density determines the temperature increase due to the nanoflare, how quickly the initial hot plasma cools, and whether NEI effects are important.
+We now examine this further.
+	% 
 	\par In the single-fluid and electron heating cases, while $\mathrm{EM}(T)$ in the uniform and power-law heating cases generally agree for low-frequency heating ($t_N=5000$ s), for intermediate frequencies ($t_N\approx750-2500$ s), the power-law cases show an enhanced high-temperature component compared to the uniform case as seen in \autoref{fig:single_em} and \autoref{fig:el_em}.
+\autoref{fig:nT_sample_profiles} shows sample heating, temperature, and density profiles for an intermediate heating frequency ($t_N=2500$ s), in the case where only the electrons are heated, for the three different types of heating functions.
+In the uniform heating rate case (red), each event has a maximum heating rate of $H_0$ such that the loop undergoes $N\approx30$ identical heating and cooling cycles, each time reaching a maximum temperature and density of $T_{max,0}$ and $n_{max,0}$, respectively.
 	%
-	\par\autoref{fig:nT_sample_profiles} shows sample heating, temperature, and density profiles for an intermediate heating frequency ($t_N=2500$ s), in the case where only the electrons are heated, for the three different types of heating functions.
-In the uniform heating rate case (red), each event has a max heating rate of $H_0$ such that the loop undergoes $N\approx30$ identical heating and cooling cycles, each time reaching a maximum temperature and density of $T_{max,0}$ and $n_{max,0}$, respectively.
-Recall from \autoref{eq:heating_rate_constraint} that the total energy injected into the loop is constrained such that $H_0=(1/N)\sum_{i=1}^NH_i$.
-In the case where the heating rates are distributed according to a power-law, there will be many events where $H_i<H_0$ and a few events where $H_i\gg H_0$.
-	%
-	\par These few high energy events allow for $T\gg T_{max,0}$ in the case where the events are chosen from a power-law distribution(blue and green curves) as seen in the middle panel of \autoref{fig:nT_sample_profiles}.
-Because these events are injected into a plasma that is already sufficiently dense due to the relatively short draining and cooling times, the emission measure is able to ``see'' these hot temperatures, resulting in a $>10$ MK component of $\mathrm{EM}(T)$ (see lower left panel of \autoref{fig:single_em} and \autoref{fig:el_em}).
-Contrastingly, in the uniform case, $T_{max,0}<10$ MK such that $\mathrm{EM}(T)$ has a steep cutoff right at 10 MK.
+	\par In comparing various heating models, we insist that the total energy injected into the loop is the same for each run (see \autoref{eq:heating_rate_constraint}).
+When the nanoflare heating rates are distributed according to a power-law, there will be many events where $H_i<H_0$ and a few events where $H_i\gg H_0$.
+These few high energy events lead to $T\gg T_{max,0}$ (blue and green curves) as seen in the middle panel of \autoref{fig:nT_sample_profiles}.
+Because these events are injected into a plasma that is sufficiently dense due to the draining and cooling times being longer than the time since the previous event, the emission measure is able to ``see'' these hot temperatures, resulting in a $>10$ MK component of $\mathrm{EM}(T)$ (see lower left panel of \autoref{fig:single_em} and \autoref{fig:el_em}).
+In the uniform case, $T_{max,0}<10$ MK such that $\mathrm{EM}(T)$ has a steep cutoff right at 10 MK.
 Additionally, we note that the only effect of the longer wait times in the $\beta=1$ case as compared to the $\beta=0$ case is an extended cool emission measure at intermediation frequencies (e.g.
 $t_N=2500$ s); the hot part of $\mathrm{EM}(T)$ for both power-law cases is nearly identical.
-In this way, the hot and cool sides of the emission measure distribution are largely isolated from one another as they are determined by separate phases of the loop evolution.
-	%
-	\par Another important discrepancy between the uniform and power-law cases is the impact of NEI on the hot part of $\mathrm{EM}(T)$.
-Recall from \autoref{subsec:params} that the uniform heating rate $H_0=2t_{total}H_{eq}/N\tau=2H_{eq}(t_N/\tau+1)$.
-From the top panel of \autoref{fig:nT_sample_profiles} we see that in the power-law case, the heating rate can be as high as $H_i\sim0.3$ erg cm$^{-3}$ s$^{-1}$.
-In terms of a uniform heating rate, this corresponds to a waiting time of $t_N\approx8100$ s.
-So even for the lowest heating frequency in the uniform case, the heating rate is still much lower.
-Furthermore, for $t_N=5000$ s, the lowest heating frequency considered here, the loop is allowed to drain to its equilibrium value (as determined by the background heating) between each event such that events with a heating rate $H_0\approx0.2$ erg cm$^{-3}$ s$^{-1}$ are injected into a low-density loop, meaning that the ionization state will not be able to keep pace with the subsequently rapid rise in temperature, resulting in $\mathrm{EM}(T_{eff})$ having a lower temperature cutoff.
-On the other hand, when the heating events are selected from a power-law distribution, events with $H_i>0.2$ erg cm$^{-3}$ s$^{-1}$ can be injected into a much higher density loop (because lower values of $t_N$ prevent longer draining times).
-This allows the ionization state to be relatively representative of the electron temperature such that $\mathrm{EM}(T)\approx\mathrm{EM}(T_{eff})$.
+Thus, the hot and cool sides of the emission measure distribution are largely isolated from one another as they are determined by separate phases of the loop evolution.
 	%
@@
 	\begin{figure*}
-		\centering
-		\includegraphics[width=2\columnwidth]{figures/em_slope_varying_bounds.pdf}
+		\plotone{figures/em_slope_varying_bounds.pdf}
 		\caption{Fits to a sample emission measure distribution constructed from a loop plasma in which only the electrons were heated by events chosen from a power-law distribution with $\alpha=-2.5$ and equally spaced by an interval of $t_N=5000$ s.
@@
 \textbf{Right:} $\mathrm{EM}(T)$ with the overlaid hot (red) and cool (blue) fit lines whose slopes correspond to those shown on the left.
-The cool power-law fits describe describe $\mathrm{EM}(T)$ for $T<4$ MK quite well while a similar fit on the hot side fails to accurately describe the shape of the emission measure distribution for $T>4$ MK.}
+The cool power-law fits describe $\mathrm{EM}(T)$ for $T<4$ MK quite well while a similar fit on the hot side fails to accurately describe the shape of the emission measure distribution for $T>4$ MK.}
 		\label{fig:em_slope_varying_bounds}
@@
 The most common observable is the emission measure slope $a$ such that $\mathrm{EM}\propto T^a$ for $10^{5.5}\le T\le10^{6.6}$ K.
-Both observational and modeling studies have found that $2<a<5$ \citep[see Table 3 of][]{bradshaw_diagnosing_2012} and in particular, \citet{cargill_active_2014} found that a heating function of the form $t_N\propto\varepsilon$ was needed in order to account for this range of slopes.
+Both observational and modeling studies have found that $2\lesssim a\lesssim5$ \citep[see Table 3 of][]{bradshaw_diagnosing_2012} and in particular, \citet{cargill_active_2014} found that a heating function of the form $t_N\propto\varepsilon$ was needed in order to account for this range of slopes.
 Additionally, a similar scaling of $\mathrm{EM}\propto T^{-b}$ for $10^{6.6}\le T\le10^{7.0}$ has been claimed though measurements of $b$ have been subject to large uncertainties \citep{warren_systematic_2012}.
 	%
-	\par\autoref{fig:em_slope_varying_bounds} shows an example of how both $T^a$ and $T^{-b}$ can be fit to the cool and hot sides of $\mathrm{EM}(T)$, respectively.
-We select a single sample run from our parameter space in which only the electrons are heated by the events chosen from a power-law distribution of $\alpha=-2.5$ and spaced uniformly by an interval of $t_N=5000$ s.
+	\par\autoref{fig:em_slope_varying_bounds} shows an example of how both $a$ and $b$ can be calculated from the cool and hot sides of $\mathrm{EM}(T)$, respectively.
+We select a single sample run from our parameter space in which only the electrons are heated by nanoflares from a power-law distribution of $\alpha=-2.5$ and spaced uniformly by an interval of $t_N=5000$ s.
 We calculate the resulting $\mathrm{EM}(T)$ and fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}.
-We fix the lower limit on each interval such that $T_{c,min}=10^{5.7}$ K and $T_{h,min} = 10^{6.7}$  K and vary the upper limits over $10^{6.1}<T_{c,max}<10^{6.5}$ and $10^{6.8}<T_{h,max}<10^{7.2}$.
+We fix the lower limit on each interval such that $T_{c,min}=10^{5.7}$ K and $T_{h,min} = 10^{6.7}$  K and vary the upper limits over $10^{6.1}<T_{c,max}<10^{6.5}$ K and $10^{6.8}<T_{h,max}<10^{7.2}$ K.
 The left panel of \autoref{fig:em_slope_varying_bounds} shows $a$ (blue) and $b$ (red) as a function upper limit of the fit interval, $T_{c,max}$ (bottom axis) and $T_{h,max}$ (top axis), respectively.
@@
 	%
-	\par From the left panel of \autoref{fig:em_slope_varying_bounds}, we see that, while $a$ is relatively insensitive to the fit interval, $b$ varies between approximately 2 and 4.5 depending on the choice of bounds of the fit interval.
+	\par From the left panel of \autoref{fig:em_slope_varying_bounds}, we see that, while $a$ is relatively insensitive to the fit interval, $b$ varies between approximately 2 and 4.5 depending on the choice of bounds.
 Furthermore, the uncertainty in the fitting procedure for $b$ is relatively large, with the average uncertainty over the entire range of $T_{h,max}$ being $\bar{\sigma}_b\approx0.17$.
@@
 	%
+	\par\authorcomment1{More discussion here?
+Some conclusions?
+What else do we need to say?
+Lead in to the next point a bit better?
+Maybe some discussion of why the slopes are different?
+What slopes we should expect?
+Refer to Paper 1...}
+	%
 	\subsubsection{Emission Measure Ratio}
@@
 	\begin{figure*}
-		\centering
-		\subfigure[]{%
-		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_electron_T2.pdf}
-		}
-		\subfigure[]{%
-		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_electron_T2.pdf}
-		}
+		\plottwo{figures/ratio_hist_alpha_electron_T2.pdf}{figures/ratio_hist_twait_electron_T2.pdf}
 		\caption{Histograms of emission measure ratios for all heating function types and heating frequencies for the case in which only the electrons are heated.
@@
 	\begin{figure*}
-		\centering
-		\subfigure[]{%
-		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_ion_T2.pdf}
-		}
-		\subfigure[]{%
-		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_ion_T2.pdf}
-		}
+		\plottwo{figures/ratio_hist_alpha_ion_T2.pdf}{figures/ratio_hist_twait_ion_T2.pdf}
 		\caption{Same as \autoref{fig:em_ratio_hist_el}, but for the case where only the ions are heated.}
@@
 Unlike an emission measure slope, a simple emission measure ratio gives information about the emission at only a single ``hot'' temperature relative to a single ``cool'' temperature.
-We choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}\approx2\times10^6$ K, the latter slightly higher (closer to $T_{peak}\approx4$ MK) than the formation temperature of Fe XII such that the emission measure ratio is less sensitive to variations in the cool emission and thus a more accurate measure of the amount of hot plasma.
+We choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}\approx2\times10^6$ K, the latter slightly higher (closer to $T_{m}\approx4$ MK) than the formation temperature of Fe XII such that the emission measure ratio is less sensitive to variations in the cool emission and thus a more accurate measure of changes in the amount of hot plasma.
+The ratio of other emission lines could also be used.
 	%
-	\par The emission measure ratio provides a way to compactly compare every point in our multidimensional parameter space while acknowledging that we are reducing $8\times10^4$ s of loop evolution to a single value.
+	\par Such an emission measure ratio also provides a way to compare in a concise way every point in our multidimensional parameter space while acknowledging that we are reducing $8\times10^4$ s of loop evolution to a single value.
 The left panel of \autoref{fig:em_ratio_hist_el} shows the case in which only the electrons are heated, where each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function.
@@
 $<20$ emssion measure ratios).
-The right panel of \autoref{fig:em_ratio_hist_el} shows these same emission measure ratios, but now separated by $t_N$.
+	%
+	\par The right panel of \autoref{fig:em_ratio_hist_el} shows these same emission measure ratios, but now separated by $t_N$.
 For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e.
@@
 In particular, $t_N=5000$ s peaks above 1.0 and extends past 1.5 while $t_N=1000$ peaks near 0 and drops off very steeply before 0.5.
-In general, the emission measure ratio appears to be more sensitive to $t_N$ compared to the electron heating case.
+In general, the emission measure ratios in the ion heating case appear to be more sensitive to $t_N$ compared to the electron heating case.
+	%
+	\par\authorcomment1{More interpretation here? Discuss conceptually the implication(s) of some of these results.}
 	%%
@@
 	\begin{enumerate}
-	\item \hl{$>10$ MK present in nanoflare train runs relative to single pulse results from paper I}
-	\item \hl{consistency of results with Cargill (2014) on the cool side; unsuitability of the hot emission measure slope}
-	\item \hl{importance of density preconditioning in departures from IEQ} 
-	\item \hl{emission measure ratio results in light of Brosius et al, 2014}
-	\item \hl{can we say something about possible heating frequencies? likelihood of electron heating over ion heating?}
+	\item \authorcomment2{$>10$ MK present in nanoflare train runs relative to single pulse results from paper I}
+	\item \authorcomment2{consistency of results with Cargill (2014) on the cool side; unsuitability of the hot emission measure slope}
+	\item \authorcomment2{importance of density preconditioning in departures from IEQ} 
+	\item \authorcomment2{emission measure ratio results in light of Brosius et al, 2014}
+	\item \authorcomment2{can we say something about possible heating frequencies? likelihood of electron heating over ion heating?}
 	\end{enumerate}
+	%
+	\par\authorcomment1{Adding this paragraph here for now.
+Maybe chop up and incorporate into discussion or delete altogether} Another important difference between the uniform and power-law cases is the impact of NEI on the hot part of $\mathrm{EM}(T)$.
+Recall from \autoref{subsec:params} that the uniform heating rate $H_0=2t_{total}H_{eq}/N\tau=2H_{eq}(t_N/\tau+1)$.
+From the top panel of \autoref{fig:nT_sample_profiles} we see that in the power-law case, the heating rate can be as high as $H_i\sim0.3$ erg cm$^{-3}$ s$^{-1}$.
+In terms of a uniform heating rate, this corresponds to a waiting time of $t_N\approx8100$ s.
+So even for the lowest heating frequency in the uniform case, the heating rate is still much lower.
+Furthermore, for $t_N=5000$ s, the lowest heating frequency considered here, the loop is allowed to drain to its equilibrium value (as determined by the background heating) between each event such that events with a heating rate $H_0\approx0.2$ erg cm$^{-3}$ s$^{-1}$ are injected into a low-density loop, meaning that the ionization state will not be able to keep pace with the subsequently rapid rise in temperature, resulting in $\mathrm{EM}(T_{eff})$ having a lower temperature cutoff.
+On the other hand, when the heating events are selected from a power-law distribution, events with $H_i>0.2$ erg cm$^{-3}$ s$^{-1}$ can be injected into a much higher density loop (because lower values of $t_N$ prevent longer draining times).
+This allows the ionization state to be relatively representative of the electron temperature such that $\mathrm{EM}(T)\approx\mathrm{EM}(T_{eff})$.
 	%
@@
 	%
-	\section*{Acknowledgment}
+	\acknowledgments
 	%
@@
 This work was supported in part by the Big-Data Private-Cloud Research Cyberinfrastructure MRI-award funded by NSF under grant CNS-1338099 and by Rice University.
+	%
+	\software{IPython \citep{perez_ipython:_2007}, Jupyter notebook, matplotlib \citep{hunter_matplotlib:_2007}, NumPy, seaborn \citep{waskom_seaborn:_2016}, Scipy \citep{van_der_walt_numpy_2011}}
 	%
@@
 	%\bibliography{hot_non-flaring_plasma_2.bbl}
-	\clearpage
 \end{document}

### 2016-07-23 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
adding updated figures to text, changes in description, added some more concluding marks in Results

@@
-\documentclass[preprint2,linenumbers]{aastex}
+\documentclass[preprint,linenumbers]{aastex}
 
@@
 In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$.
-Preferential species heating, NEU, power-law nanoflare distributions, and the effects of a variable $t_N$ between events are considered and an emission measure ratio metric, similar to that discussed in \citet{brosius_pervasive_2014}, is used to characterize the various results.
+Preferential species heating, NEI, power-law nanoflare distributions, and the effects of a variable $t_N$ between events are considered and an emission measure ratio metric, similar to that discussed in \citet{brosius_pervasive_2014}, is used to characterize the various results.
 \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated.
@@
 	%
-	\par\authorcomment1{More discussion here?
-Some conclusions?
-What else do we need to say?
-Lead in to the next point a bit better?
-Maybe some discussion of why the slopes are different?
-What slopes we should expect?
-Refer to Paper 1...}
+	\par Our results here suggest that while $a$ is an adequate parameter for describing the cool side of $\mathrm{EM}(T)$, the functional form $\mathrm{EM}\sim T^{-b}$ does not adequately capture the character of the hot part of $\mathrm{EM}(T)$ over any reasonable temperature range.
+\citep{antiochos_evaporative_1978} showed analytically that accounting for evaporative cooling and assuming constant pressure gives $b=11/2$, though this value can be as low as $b=5/2$ if a flux limiter is included.
+However, in \citetalias{barnes_inference_2016}, we showed that in the case of a single 200 s nanoflare that heats only the electrons, the assumption of constant electron pressure during the heating and early conductive cooling phases does not hold.
+In this way, we should not expect to recover these analytic values from our numerical or observational results.
+Clearly, we need an alternate metric to assess the amount of hot plasma seen by the emission measure distribution.
+	%
+	\par\authorcomment1{I think discussing the results of this section in the context of Paper 1 is a good idea. Not sure how well this works...needs something else?}
 	%
@@
 	\begin{figure*}
+		\plottwo{figures/ratio_hist_alpha_single_T2.pdf}{figures/ratio_hist_twait_single_T2.pdf}
+		\caption{Histograms of emission measure ratios $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$, where $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}$ K, for all heating function types and heating frequencies for the single fluid case.
+In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the Bayesian blocks method of \citep{scargle_studies_2013} as implemented in the astroML Python package for statistical learning in astronomy \citep{vanderplas_introduction_2012}.
+\textbf{Left:} Emission measure ratios separated by heating function type for all heating frequencies, $250\le t_N\le5000$ s.
+\textbf{Right:} Emission measure ratios separated by waiting time, $t_N$.
+For aesthetic purposes, only five values of $t_N$ are shown, $t_N=1000,2000,3000,4000,5000$ s.}
+		\label{fig:em_ratio_hist_single}
+	\end{figure*}
+	%%
+	\begin{figure*}
 		\plottwo{figures/ratio_hist_alpha_electron_T2.pdf}{figures/ratio_hist_twait_electron_T2.pdf}
-		\caption{Histograms of emission measure ratios for all heating function types and heating frequencies for the case in which only the electrons are heated.
-In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the well-known Freedman-Diaconis formula \citep{freedman_histogram_1981}.
-\textbf{Left:} Emission measure ratios separated by heating function type.
-\textbf{Right:} Emission measure ratios separated by waiting time, $t_N$.
-For aesthetic purposes, only five values of $t_N$ are shown.}
+		\caption{Same as \autoref{fig:em_ratio_hist_single}, but for the case where only the electrons are heated.}
 		\label{fig:em_ratio_hist_el}
@@
 		\plottwo{figures/ratio_hist_alpha_ion_T2.pdf}{figures/ratio_hist_twait_ion_T2.pdf}
-		\caption{Same as \autoref{fig:em_ratio_hist_el}, but for the case where only the ions are heated.}
+		\caption{Same as \autoref{fig:em_ratio_hist_single}, but for the case where only the ions are heated.
+Here, the bin widths are calculated according to the well-known Freedman-Diaconis formula \citep{freedman_histogram_1981}}
 		\label{fig:em_ratio_hist_ion}	
@@
 	\par Such an emission measure ratio also provides a way to compare in a concise way every point in our multidimensional parameter space while acknowledging that we are reducing $8\times10^4$ s of loop evolution to a single value.
-The left panel of \autoref{fig:em_ratio_hist_el} shows the case in which only the electrons are heated, where each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function.
+The left panel of \autoref{fig:em_ratio_hist_single} shows the single-fluid case, where each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function.
 This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$ and $t_{N,i}=t_N$ for all $i$ (i.e.
@@
 	%
-	\par The right panel of \autoref{fig:em_ratio_hist_el} shows these same emission measure ratios, but now separated by $t_N$.
+	\par The right panel of \autoref{fig:em_ratio_hist_single} shows these same emission measure ratios, but now separated by $t_N$.
 For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e.
@@
 Note that we choose to only show results for five values of $t_N$ for aesthetic purposes.
-We find that for $t_N\le3000$ s, the emission measure ratios are largely clustered below 0.5, with $t_N=2000,3000,4000$ s peaking between $\sim0.3-0.45$.
-For $t_N>4000$ s, the emission measure ratio seems to be more sensitive to the heating frequency .
+For $t_N\le3000$ s, the results cluster just below 0.5 while the $t_N=4000,5000$ s cases peak at $\sim0.6$ and $\sim0.9$, respectively.
+In general, it seems that the distribution widens as $t_N$ increases.
 	%
-	\par Similarly, we compute the same emission measure ratio for the case in which only the ions are heated.
+	\par Similarly, \autoref{fig:em_ratio_hist_el} shows the emission measure ratio for the case in which only the electrons are heated.
+Looking first at the left panel, we see that, as in \autoref{fig:em_ratio_hist_single}, the emission measure ratio is largely insensitive to $\alpha$, but is comparatively more narrow and falls off more quickly twoard higher emission measure ratios.
+The $\beta=0$ cases (for all $\alpha$) peak near $0.25$, with the $\beta=1$ cases all peaking at slightly higher values, but all less than 1.
+Again, we have not included the uniform case.
+The right panel shows the same emission measure ratios now grouped by $t_N$.
+The lower frequencies, $t_N=1000,2000,3000$ s, tend to cluster at approximately the same value as in \autoref{fig:em_ratio_hist_el}.
+However, for all $t_N$, the distributions are significantly more narrow.
+Furthermore, the lower heating frequencies, $t_N=4000,5000$ s, peak at considerably lower lower values, $\sim0.45$ and $\sim0.7$, respectively.
+Overall, for all $t_N$ in the electron heating case, the emission measure ratio distributions tend to be comparatively narrow and clustered near $0.5$.
+	%
+	\par Finally, we compute the same emission measure ratio for the case in which only the ions are heated.
 The left panel of \autoref{fig:em_ratio_hist_ion} shows histograms for each type of heating function.
@@
 The right panel of \autoref{fig:em_ratio_hist_ion} shows the same emission measure ratios now grouped by waiting time where again we only show five values of $t_N$.
-With the exception of the $t_N=2000$ s and $t_N=3000$ s group, the distributions for each value of $t_N$ are much more spread out (as compared \autoref{fig:em_ratio_hist_el}).
+With the exception of the $t_N=2000$ s and $t_N=3000$ s group, the distributions for each value of $t_N$ are much more spread out (as compared to \autoref{fig:em_ratio_hist_single} and \autoref{fig:em_ratio_hist_el}).
 In particular, $t_N=5000$ s peaks above 1.0 and extends past 1.5 while $t_N=1000$ peaks near 0 and drops off very steeply before 0.5.
@@
 	%
-	\software{IPython \citep{perez_ipython:_2007}, Jupyter notebook, matplotlib \citep{hunter_matplotlib:_2007}, NumPy, seaborn \citep{waskom_seaborn:_2016}, Scipy \citep{van_der_walt_numpy_2011}}
+	\software{astroML \citep{vanderplas_introduction_2012}, IPython \citep{perez_ipython:_2007}, Jupyter notebook, matplotlib \citep{hunter_matplotlib:_2007}, NumPy, seaborn \citep{waskom_seaborn:_2016}, Scipy \citep{van_der_walt_numpy_2011}}
 	%

### 2016-08-08 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
updating descriptions of results to be consistent with new figures; filling out some parts in the results and conclusions

@@
 	%
-	\par\authorcomment1{Maybe intro is a bit lengthy...where to cut it down?}
-	%
 	\par The concept of heating the solar corona by nanoflares, first proposed by \citet{parker_nanoflares_1988}, has been developed extensively over the past two decades \citep[e.g.][]{cargill_implications_1994,cargill_nanoflare_2004,klimchuk_solving_2006}.
@@
 Below $T_m$, there is a scaling $\mathrm{EM}(T)\sim T^a$ over a temperature range $10^6\lesssim T\lesssim T_m$, a result first discussed by \citet{jordan_structure_1975}.
-Observations from the \textit{Hinode} spacecraft \citep{kosugi_hinode_2007} have shown that $2\lesssim a\lesssim5$, with $T_m\approx10^{6.5-6.6}$ \citep{warren_constraints_2011,warren_systematic_2012,winebarger_using_2011,tripathi_emission_2011,schmelz_cold_2012,del_zanna_evolution_2015}.
+Observations from instruments onboard the Solar Dynamics Observatory \citep[SDO,][]{pesnell_solar_2012} and \textit{Hinode} spacecraft \citep{kosugi_hinode_2007} have shown that $2\lesssim a\lesssim5$, with $T_m\approx10^{6.5-6.6}$ \citep{warren_constraints_2011,warren_systematic_2012,winebarger_using_2011,tripathi_emission_2011,schmelz_cold_2012,del_zanna_evolution_2015}.
 	%
@@
 However, measured values of these ``hotward" slopes are poorly constrained due to both the low magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}.
-\citet{warren_systematic_2012}, find $7\lesssim b\lesssim10$, with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$.
+\citet{warren_systematic_2012} find $7\lesssim b\lesssim10$ with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$.
 It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with differrent inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013,aschwanden_benchmark_2015}.
@@
 For example, while \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$.
-\citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<t_N<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the full range of observed emission measure slopes be found.
+\citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250\le t_N\le5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the full range of observed emission measure slopes be found.
 	%
@@
 	%
-	\par However, nanoflare heating requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}.
-While a single nanoflare in the LF heating scenario will always occur in a plasma of characteristic AR density ($\sim10^9$ cm$^{-3}$), with significant consequences.
+	\par While a single nanoflare in the LF heating scenario will always occur in a plasma of characteristic AR density ($\sim10^9$ cm$^{-3}$) with significant consequences, nanoflare heating requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}.
 In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$.
@@
 	%
-	\par 1D hydrodynamic models are excellent tools for computing field-aligned quantities in coronal loops.
+	\par Hydrodynamic models are excellent tools for computing field-aligned quantities in coronal loops.
 However, because of the small cell sizes needed to resolve the transition region and consequently small timesteps demanded by thermal conduction, the use of such models in large parameter space explorations is made impractical by long computational runtimes \citep{bradshaw_influence_2013}.
@@
 	\begin{align}
-		\frac{d}{dt}\bar{p}_e &= \frac{\gamma - 1}{L}\left\lbrack\psi_{TR} - (\mathcal{R}_{TR} + \mathcal{R}_C)\right\rbrack + \nonumber\\ &k_B\bar{n}\nu_{ei}(\bar{T}_i - \bar{T}_e) + (\gamma - 1)\bar{Q}_e,\label{eq:ebtel2fl_pe}\\
-		\frac{d}{dt}\bar{p}_i &= -\frac{\gamma - 1}{L}\psi_{TR} + k_B\bar{n}\nu_{ei}(\bar{T}_e - \bar{T}_i) +\nonumber\\ &(\gamma - 1)\bar{Q}_i,\label{eq:ebtel2fl_pi}\\
+		\frac{d}{dt}\bar{p}_e &= \frac{\gamma - 1}{L}\left\lbrack\psi_{TR} - (\mathcal{R}_{TR} + \mathcal{R}_C)\right\rbrack + k_B\bar{n}\nu_{ei}(\bar{T}_i - \bar{T}_e) + (\gamma - 1)\bar{Q}_e,\label{eq:ebtel2fl_pe}\\
+		\frac{d}{dt}\bar{p}_i &= -\frac{\gamma - 1}{L}\psi_{TR} + k_B\bar{n}\nu_{ei}(\bar{T}_e - \bar{T}_i) + (\gamma - 1)\bar{Q}_i,\label{eq:ebtel2fl_pi}\\
 		\frac{d}{dt}\bar{n} &= \frac{c_2(\gamma - 1)}{c_3\gamma Lk_B\bar{T}_e}\left(\psi_{TR} - F_{ce,0} - \mathcal{R}_{TR}\right),\label{eq:ebtel2fl_n}
@@
 	%%
-	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency and $\psi_{TR}$ is a term included to maintain charge and current and neutrality.
+	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency, and $\psi_{TR}$ is a term included to maintain charge and current and neutrality.
 Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional corrections detailed in Appendix 1 of \citetalias{barnes_inference_2016}.
@@
 		\plotone{figures/heating_functions.pdf}
-		\caption{\textbf{Top}: Uniform heating amplitudes for $t_N=1000$ s; \textbf{Middle:} Uniform heating amplitudes for $t_N=5000$ s; \textbf{Bottom:} Heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$.
-The events shown in red have wait times that depend on the previous event energy while the events shown in blue have uniform wait times.
+		\caption{Examples of four different heating functions: uniform heating amplitudes for $t_N=1000$ s (top), uniform heating amplitudes for $t_N=5000$ s (middle), and heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$ (bottom).
+In the bottom panel, the events shown in red have waiting times that depend on the previous event energy while the events shown in blue have uniform wait times.
 The mean wait time in both cases is $t_N=2000$ s.}
@@
 In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored.
-Thus, to maintain an emission measure peaked about $T_{m}$, for triangular pulses, the individual event heating rates are constrained by
+Thus, to maintain an emission measure peaked about $T_{m}$, for triangular pulses, the individual event heating rates are constrained by,
 	\begin{equation}
@@
 ``single'' indicates a single-fluid model.
-$\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent.
-Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions.}
+$\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $\varepsilon\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent.
+Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions per heated species.}
 		\label{fig:parameter_space}
@@
 	%
-	\par In our first set of results, we compare $\mathrm{EM}(T)$ for three different types of heating functions, across six different heating frequencies.
+	\par In our first set of results, we compare $\mathrm{EM}(T)$ for three different types of heating functions, across a sample of six different heating frequencies.
 \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions in the single-fluid case, electron heating case, and ion heating case, respectively.
@@
 The shading represents $1\sigma$ from the mean.
-In this way, we account for the variations that may occur because of a lack/excess of strong heating events due to limited sampling from the distribution.
+In this way, we account for the variations that may occur because of a lack/excess of strong heating events due to limited sampling from the power-law distribution of possible heating rates.
 	%
@@
 Firstly, as expected from \citet{cargill_active_2014}, as $t_N$ increases, $\mathrm{EM}(T)$ widens, extending to both cooler ($<4$ MK) and hotter ($>4$ MK) temperatures.
-The extension toward cooler temperatures arises because as $t_N$ increases there is more time between successive heating events so that the loop so that the loops cools to lower temperatures before being reheated.
+The extension toward cooler temperatures arises because as $t_N$ increases there is more time between successive heating events so that the loop cools to lower temperatures before being reheated.
 The dependence on $\alpha$ and $\beta$ is similar to that described in \citet{cargill_active_2014}.
@@
 	\par The behavior of $\mathrm{EM}(T)$ above $T_m$ is more complicated.
-For small $t_N$, the emission measure distribution falls off sharply on the hot side for a uniform nanoflare train but a power law distribution leads to a broader distribution above $T_m$.
+For small $t_N$, the emission measure distribution falls off sharply on the hot side for a uniform nanoflare train but a power-law distribution leads to a broader distribution above $T_m$.
 This just reflects the different initial temperatures generated with a power-law distribution since $T \simeq H^{2/7}$.
@@
 	%%
+	The relation of these results to potential solar observations is made difficult by incomplete temperature coverage.
+For example, we noted earlier that the temperature coverage for \textit{Hinode} and SDO is good for $T<T_m$, but patchy for $T>T_m$.
+On the other hand, the proposed MaGIXS instrument has the opposite performance regime.
+This differs from EUVE observations of some stellar coronae which have very complete temperature coverage from $10^6$ K to over $10^7$ K \citep[e.g.][]{sanz-forcada_structure_2003}, and have been modeled using low frequency nanoflares \citep{cargill_temperature-emission_2006}.
+In the following sub-sections we propose ways that the paucity of solar temperature coverage can be partially remedied.
+	%
 	\subsubsection{Emission Measure Slope}
@@
 	%
-	\par We now examine several observables often used to characterize the emission measure distribution.
-The most common observable is the emission measure slope $a$ such that $\mathrm{EM}\propto T^a$ for $10^{5.5}\le T\le10^{6.6}$ K.
+	\par As we discussed in the \autoref{sec:intro}, a commonly-used observable is the emission measure slope $a$ such that $\mathrm{EM}\propto T^a$ for $10^{5.5}\le T\le10^{6.6}$ K.
 Both observational and modeling studies have found that $2\lesssim a\lesssim5$ \citep[see Table 3 of][]{bradshaw_diagnosing_2012} and in particular, \citet{cargill_active_2014} found that a heating function of the form $t_N\propto\varepsilon$ was needed in order to account for this range of slopes.
-Additionally, a similar scaling of $\mathrm{EM}\propto T^{-b}$ for $10^{6.6}\le T\le10^{7.0}$ has been claimed though measurements of $b$ have been subject to large uncertainties \citep{warren_systematic_2012}.
+The EIS instrument \citep{culhane_euv_2007} on \textit{Hinode} permits good temperature coverage.
+Additionally, a similar scaling of $\mathrm{EM}\propto T^{-b}$ for $10^{6.6}\le T\le10^{7.0}$ has been claimed though measurements of $b$ have been subject to large uncertainties \citep{warren_systematic_2012} due to intermittent temperature coverage.
 	%
@@
 We select a single sample run from our parameter space in which only the electrons are heated by nanoflares from a power-law distribution of $\alpha=-2.5$ and spaced uniformly by an interval of $t_N=5000$ s.
-We calculate the resulting $\mathrm{EM}(T)$ and fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}.
+We calculate the resulting $\mathrm{EM}(T)$ and fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting as implemented in the scipy scientific Python package \citep{van_der_walt_numpy_2011}.
 We fix the lower limit on each interval such that $T_{c,min}=10^{5.7}$ K and $T_{h,min} = 10^{6.7}$  K and vary the upper limits over $10^{6.1}<T_{c,max}<10^{6.5}$ K and $10^{6.8}<T_{h,max}<10^{7.2}$ K.
@@
 	\par Our results here suggest that while $a$ is an adequate parameter for describing the cool side of $\mathrm{EM}(T)$, the functional form $\mathrm{EM}\sim T^{-b}$ does not adequately capture the character of the hot part of $\mathrm{EM}(T)$ over any reasonable temperature range.
-\citep{antiochos_evaporative_1978} showed analytically that accounting for evaporative cooling and assuming constant pressure gives $b=11/2$, though this value can be as low as $b=5/2$ if a flux limiter is included.
+\citet{antiochos_evaporative_1978} showed analytically that accounting for evaporative cooling and assuming constant pressure gives $b=11/2$, though this value can be as low as $b=5/2$ if a flux limiter is included.
 However, in \citetalias{barnes_inference_2016}, we showed that in the case of a single 200 s nanoflare that heats only the electrons, the assumption of constant electron pressure during the heating and early conductive cooling phases does not hold.
-In this way, we should not expect to recover these analytic values from our numerical or observational results.
-Clearly, we need an alternate metric to assess the amount of hot plasma seen by the emission measure distribution.
-	%
-	\par\authorcomment1{I think discussing the results of this section in the context of Paper 1 is a good idea. Not sure how well this works...needs something else?}
+Our results here are consistent with our findings in \citetalias{barnes_inference_2016} in that the parameter $b$ does not provide any valuable information about $\mathrm{EM}(T)$ for $T>T_m$ when two-fluid effects are considered.
+Clearly, an alternative metric for measuring the amount of hot plasma in the emission measure distribution is needed.
 	%
@@
 	\begin{figure*}
-		\plottwo{figures/ratio_hist_alpha_single_T2.pdf}{figures/ratio_hist_twait_single_T2.pdf}
-		\caption{Histograms of emission measure ratios $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$, where $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}$ K, for all heating function types and heating frequencies for the single fluid case.
-In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the Bayesian blocks method of \citep{scargle_studies_2013} as implemented in the astroML Python package for statistical learning in astronomy \citep{vanderplas_introduction_2012}.
+		\plottwo{figures/ratio_hist_alpha_single_T1.pdf}{figures/ratio_hist_twait_single_T1.pdf}
+		\caption{Histograms of emission measure ratios $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$, where $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.2}$ K, for all heating function types and heating frequencies for the single fluid case.
+In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the Bayesian blocks method of \citet{scargle_studies_2013} as implemented in the astroML Python package for statistical learning in astronomy \citep{vanderplas_introduction_2012}.
 \textbf{Left:} Emission measure ratios separated by heating function type for all heating frequencies, $250\le t_N\le5000$ s.
+Because there are too few ($<20$) $\mathrm{EM}$ ratio measurements for the uniform case to construct a meaningful histogram, we denote the median of the uniform results with a vertical line, shown here in purple.
 \textbf{Right:} Emission measure ratios separated by waiting time, $t_N$.
@@
 	\begin{figure*}
-		\plottwo{figures/ratio_hist_alpha_electron_T2.pdf}{figures/ratio_hist_twait_electron_T2.pdf}
+		\plottwo{figures/ratio_hist_alpha_electron_T1.pdf}{figures/ratio_hist_twait_electron_T1.pdf}
 		\caption{Same as \autoref{fig:em_ratio_hist_single}, but for the case where only the electrons are heated.}
@@
 	\begin{figure*}
-		\plottwo{figures/ratio_hist_alpha_ion_T2.pdf}{figures/ratio_hist_twait_ion_T2.pdf}
+		\plottwo{figures/ratio_hist_alpha_ion_T1.pdf}{figures/ratio_hist_twait_ion_T1.pdf}
 		\caption{Same as \autoref{fig:em_ratio_hist_single}, but for the case where only the ions are heated.
@@
 	%%
-	\par\citet{brosius_pervasive_2014}, using observations of an active region from the \textit{EUNIS-13} sounding rocket, found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside, providing possible evidence for impulsive heating.
-As a proxy for this intensity ratio and an alternative to the hot emission measure slope $b$, we propose using an emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$.
-Unlike an emission measure slope, a simple emission measure ratio gives information about the emission at only a single ``hot'' temperature relative to a single ``cool'' temperature.
-We choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}\approx2\times10^6$ K, the latter slightly higher (closer to $T_{m}\approx4$ MK) than the formation temperature of Fe XII such that the emission measure ratio is less sensitive to variations in the cool emission and thus a more accurate measure of changes in the amount of hot plasma.
-The ratio of other emission lines could also be used.
+	\par One characteristic of the $\mathrm{EM}(T)$ distribution arising from low- and intermediate-frequency nanoflares is that $\mathrm{EM}(T)$ is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}.
+For example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 10^{6.2}$ K and $10^{6.9}$ K.
+Given two observed temperatures (due say to specific emission lines), this suggests that predictions from the ratio of emission at these temperatures can be compared with data.
+This is of particular use where very limited spectral coverage is available either above or below $T_m$.
+Indeed for impulsive heating of any kind, the generic $\mathrm{EM}(T)$ curve remains similar (though not identical) as the magnitude of the heating changes.
+For flare-like energy release one would expect the hot emission to be much greater than the cold emission, with the opposite in the quiet Sun.
+For nanoflares, one might expect them to be of the same order.
+	%
+	\par An example of how this approach might work can be found in \citet{brosius_pervasive_2014}.
+Using observations of an active region from the \textit{EUNIS-13} sounding rocket, they found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside.
+They argue that this provides possible evidence for impulsive heating.
+\authorcomment1{These next few sentences need tightening up; next round of edits...have updated to be consistent with new choice for em ratio}As a proxy for this intensity ratio and an alternative to the hot emission measure slope $b$, we propose using an emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$.
+Unlike an emission measure slope, where a functional relationship is assumed over a range of $T$ in $\mathrm{EM}(T)$, a simple emission measure ratio gives information about the emission at only a single ``hot'' temperature relative to a single ``cool'' temperature.
+Using this ratio, we can assess the relative strength of $\mathrm{EM}(T)$ above and below $T_m$ and in doing so, assess the expected range of emission measure ratios consistent with nanoflare heating.
+We choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.2}$ K, consistent with \citet{brosius_pervasive_2014} The ratio of other emission lines could also be used.
 	%
@@
 $\beta=0$).
-We see that the emission measure ratio is largely insensitive to $\alpha$ and is peaked sharply at approximately $0.25$; the distribution peaks at slightly higher values for the $\beta=1$ case though the overall shape of the distribution is the same.
-Here we have not included the uniform heating case due to small number statistics (i.e.
-$<20$ emssion measure ratios).
+We see that the emission measure ratio is largely insensitive to $\alpha$ and is peaked sharply at $\sim0.75-1.0$; the distribution peaks at slightly higher values for the $\beta=1$ case ($\sim1.25$) though the overall shape of the distributions is the same.
+Note that the uniform heating results (whose median is denoted by the vertical purple line near $\sim0.5$) show emission measure ratios significantly less than those in the power-law cases, consistent with the reduced hot emission shown in \autoref{fig:el_em}.
 	%
@@
 Note that we choose to only show results for five values of $t_N$ for aesthetic purposes.
-For $t_N\le3000$ s, the results cluster just below 0.5 while the $t_N=4000,5000$ s cases peak at $\sim0.6$ and $\sim0.9$, respectively.
-In general, it seems that the distribution widens as $t_N$ increases.
+For $t_N\le4000$ s, the results cluster just near 1.0, though the $t_N=3000$ s distribution is slightly bimodal, peaking strongly at $\sim0.75$ and more weakly at $\sim1.25$.
+Additionally, the $t_N=5000$ s case peaks slightly higher at $\sim1.5$ and does not ``pile up'' near 1.0 as the other values of $t_N$ do.
+In general, the distributions for all $t_N$ have a positive skew and are peaked in the range $\sim0.5-1.5$.
 	%
@@
 Looking first at the left panel, we see that, as in \autoref{fig:em_ratio_hist_single}, the emission measure ratio is largely insensitive to $\alpha$, but is comparatively more narrow and falls off more quickly twoard higher emission measure ratios.
-The $\beta=0$ cases (for all $\alpha$) peak near $0.25$, with the $\beta=1$ cases all peaking at slightly higher values, but all less than 1.
-Again, we have not included the uniform case.
+The $\beta=0$ cases (for all $\alpha$) peak near $0.5$, with the $\beta=1$ cases all peaking at slightly higher values, but all less than 1.
 The right panel shows the same emission measure ratios now grouped by $t_N$.
-The lower frequencies, $t_N=1000,2000,3000$ s, tend to cluster at approximately the same value as in \autoref{fig:em_ratio_hist_el}.
-However, for all $t_N$, the distributions are significantly more narrow.
-Furthermore, the lower heating frequencies, $t_N=4000,5000$ s, peak at considerably lower lower values, $\sim0.45$ and $\sim0.7$, respectively.
-Overall, for all $t_N$ in the electron heating case, the emission measure ratio distributions tend to be comparatively narrow and clustered near $0.5$.
+The $t_N=3000$ distribution has a very strong and narrow peak at $\approx0.5$ while all of the other distributions peak at $\sim1$.
+For $t_N\ge3000$ s, the location of the peak increases weakly with increasing $t_N$ though this is not the case for $t_N=1000,2000$ s.
 	%
@@
 Similar to the electron  heating results, we find that the $\beta=0$ distributions peak at lower values compared to the $\beta=1$ distributions and that in the $\beta=0$ case, the distribution of emission measure ratios is relatively insensitive to $\alpha$.
-However, unlike the electron heating case, the distributions in all cases are much wider and peak at higher values, $\sim0.5$ for $\beta=0$ and $>1$ for $\beta=1$.
+However, unlike the electron heating case, the distributions in all cases are much wider and peak at higher values, $\sim1.5$ for $\beta=0$ and $>2$ for $\beta=1$.
 Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$.
 The right panel of \autoref{fig:em_ratio_hist_ion} shows the same emission measure ratios now grouped by waiting time where again we only show five values of $t_N$.
-With the exception of the $t_N=2000$ s and $t_N=3000$ s group, the distributions for each value of $t_N$ are much more spread out (as compared to \autoref{fig:em_ratio_hist_single} and \autoref{fig:em_ratio_hist_el}).
-In particular, $t_N=5000$ s peaks above 1.0 and extends past 1.5 while $t_N=1000$ peaks near 0 and drops off very steeply before 0.5.
-In general, the emission measure ratios in the ion heating case appear to be more sensitive to $t_N$ compared to the electron heating case.
+Compared to the results in the left panels of \autoref{fig:em_ratio_hist_single} and \autoref{fig:em_ratio_hist_el}, the distributions for each value of $t_N$ are much wider and the peak values show a stronger dependence on $t_N$.
+The range of peak values is also much larger, with the $t_N=1000$ s peaking near 0 and $t_N=5000$ s peaking at $\sim2$.
+As in \autoref{fig:em_ratio_hist_single}, we see that the $t_N=3000$ s distribution is bimodal.
 	%
-	\par\authorcomment1{More interpretation here? Discuss conceptually the implication(s) of some of these results.}
+	\par\authorcomment2{These results suggest that emission measure ratios, for $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.2}$ K, consistent with nanoflare heating fall approximately in the range $\sim0.5-1.5$.
+We find that the resulting distributions of ratios are largely independent of the power-law index $\alpha$ and only weakly-dependent on the heating frequency, $t_N$ (with the exception of the ion heating case).
+Furthermore, the distributions are also weakly dependent on the relationship between the waiting time and heating rate, $\beta$.
+In this way, a determination of more detailed nanoflare properties from observations may be difficult without a very large number of measurements and relatively small uncertainties in the atomic data.
+However, while the single-fluid and electron heating distributions are relatively similar (see \autoref{fig:em_ratio_hist_single} and \autoref{fig:em_ratio_hist_el}), the resulting ion heating distributions are much wider, peak at higher values, and show a stronger dependence on $\alpha$, $\beta$, and $t_N$.
+We may interpret this as the emission on the hot side of $\mathrm{EM}(T)$ being relatively insensitive to these parameter changes when only the ions are heated.
+In this way, the emission measure ratio probes mostly changes in the cool emission which we already know to be sensitive to both $\beta$ and $t_N$ \citep{cargill_active_2014}.}
 	%%
@@
 	%%
-	\begin{enumerate}
-	\item \authorcomment2{$>10$ MK present in nanoflare train runs relative to single pulse results from paper I}
-	\item \authorcomment2{consistency of results with Cargill (2014) on the cool side; unsuitability of the hot emission measure slope}
-	\item \authorcomment2{importance of density preconditioning in departures from IEQ} 
-	\item \authorcomment2{emission measure ratio results in light of Brosius et al, 2014}
-	\item \authorcomment2{can we say something about possible heating frequencies? likelihood of electron heating over ion heating?}
-	\end{enumerate}
-	%
-	\par\authorcomment1{Adding this paragraph here for now.
-Maybe chop up and incorporate into discussion or delete altogether} Another important difference between the uniform and power-law cases is the impact of NEI on the hot part of $\mathrm{EM}(T)$.
-Recall from \autoref{subsec:params} that the uniform heating rate $H_0=2t_{total}H_{eq}/N\tau=2H_{eq}(t_N/\tau+1)$.
-From the top panel of \autoref{fig:nT_sample_profiles} we see that in the power-law case, the heating rate can be as high as $H_i\sim0.3$ erg cm$^{-3}$ s$^{-1}$.
-In terms of a uniform heating rate, this corresponds to a waiting time of $t_N\approx8100$ s.
-So even for the lowest heating frequency in the uniform case, the heating rate is still much lower.
-Furthermore, for $t_N=5000$ s, the lowest heating frequency considered here, the loop is allowed to drain to its equilibrium value (as determined by the background heating) between each event such that events with a heating rate $H_0\approx0.2$ erg cm$^{-3}$ s$^{-1}$ are injected into a low-density loop, meaning that the ionization state will not be able to keep pace with the subsequently rapid rise in temperature, resulting in $\mathrm{EM}(T_{eff})$ having a lower temperature cutoff.
-On the other hand, when the heating events are selected from a power-law distribution, events with $H_i>0.2$ erg cm$^{-3}$ s$^{-1}$ can be injected into a much higher density loop (because lower values of $t_N$ prevent longer draining times).
-This allows the ionization state to be relatively representative of the electron temperature such that $\mathrm{EM}(T)\approx\mathrm{EM}(T_{eff})$.
+	\authorcomment1{Is this section really even necessary?
+Can the discussion be entirely contained in (last part of) the Results section?
+Or we could convert \autoref{subsec:diagnostics} to the Discussion section...}
 	%
@@
 	%
+	\par In this paper we have carried out two-fluid modeling of nanoflare trains in AR cores and considered a range of power-law slopes and models of waiting time between events.
+For each set of parameters we have generated the emission measure distribution, $\mathrm{EM}(T)$.
+An important outcome is that, defining the peak of the emission measure as $T = T_m$, the distribution $\mathrm{EM}(T)$ on either side of $T_m$ reveals different information about the heating mechanism.
+Below $T_m$ the principle factor in determining the distribution is the presence of a waiting time between nanoflares: the high densities below $T_m$ mean that species equilibration has occurred; thus no information of which species was heated remains.
+	%
+	\par Above $T_m$, higher temperatures arise when a power law distribution of energy is assumed.
+However, no information about the presence of a waiting time survives.
+Higher observed temperatures also arise for the cases of a single fluid and electron heating than ion heating since a finite equilibration time means that in the latter case the electrons are heated more slowly.
+In all these cases we find that, unlike some of the examples in \citetalias{barnes_inference_2016}, NEI is not a major consideration.
+	%
+	\par Two possible ways to relate these results to present and future observations were discussed.
+First we showed that while below $T_m$ a power law representation of $\mathrm{EM}\sim T^a$ was quite robust, that was not the case above $T_m$.
+On the other hand the calculation of a ratio between the emission measure at a pair temperatures above and below $T_m$ held more promise.
+\authorcomment2{By using this ratio as an alternative to the emission measure slope, we do not assume $\mathrm{EM}(T)$ to have a particular functional form and we account for emission on the hot and cool side of $\mathrm{EM}(T)$, both of which contain signatures of the heating.}
+	%
+	\par\authorcomment2{While our emission measure ratio results show a relatively weak dependence on the particular properties of the heating (e.g.
+$\alpha,\beta,t_N$), we find that, for the electron heating, ion heating, and single-fluid cases, the peaks of the distributions all fall in the range $~0.5-1.5$.
+In this way, we find that the 0.59 emission measure ratio of \citet{brosius_pervasive_2014}, which they conclude to be a signature of nanoflares, is consistent with nanoflare heating for a range of different heating properties.
+A larger sample of observations in this wavelength range combined with the analysis presented here will help to constrain the heating properties of nanoflares.}
 	%
@@
 	%
-	WTB was provided travel support to the Coronal Loops Workshop VII held in Cambridge, UK, July 21-23, 2015, at which a preliminary version of this work was presented, by NSF award number 1536094.
+	WTB was provided travel support to the Coronal Loops Workshop VII held in Cambridge, UK, at which a preliminary version of this work was presented, by NSF award number 1536094.
 This work was supported in part by the Big-Data Private-Cloud Research Cyberinfrastructure MRI-award funded by NSF under grant CNS-1338099 and by Rice University.
 	%
-	\software{astroML \citep{vanderplas_introduction_2012}, IPython \citep{perez_ipython:_2007}, Jupyter notebook, matplotlib \citep{hunter_matplotlib:_2007}, NumPy, seaborn \citep{waskom_seaborn:_2016}, Scipy \citep{van_der_walt_numpy_2011}}
+	\software{astroML \citep{vanderplas_introduction_2012}, IPython \citep{perez_ipython:_2007}, Jupyter notebook, matplotlib \citep{hunter_matplotlib:_2007}, NumPy, seaborn \citep{waskom_seaborn:_2016}, scipy \citep{van_der_walt_numpy_2011}}
 	%

### 2016-08-10 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
minor corrections pointed out by PC

@@
 \citet{warren_systematic_2012} find $7\lesssim b\lesssim10$ with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$.
-It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with differrent inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013,aschwanden_benchmark_2015}.
+It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with different inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013,aschwanden_benchmark_2015}.
 	%
@@
 	%
-	\par While a single nanoflare in the LF heating scenario will always occur in a plasma of characteristic AR density ($\sim10^9$ cm$^{-3}$) with significant consequences, nanoflare heating requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}.
+	\par Single nanoflare are a good proxy for the LF heating scenario, but a study of nanoflare heating over a range of heating frequencies requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}.
 In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$.
@@
 	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency, and $\psi_{TR}$ is a term included to maintain charge and current and neutrality.
-Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional corrections detailed in Appendix 1 of \citetalias{barnes_inference_2016}.
+Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional modifications detailed in Appendix 1 of \citetalias{barnes_inference_2016}.
 These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$.
@@
 Note that if $H_i=H_0$ for all $i$, the heating rate for each event is $H_i=H_0=2t_{total}H_{eq}/N\tau$.
-Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the average energy per event for a loop heated by $N=20$ nanoflares in $t_{total}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx5.8\times10^{24}$ erg, consistent with the energy budget of the Parker nanoflare model.
+Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the average energy per event for a loop heated by $N=20$ nanoflares in $t_{total}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx5.8\times10^{24}$ erg.
 	%
@@
 The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).
+Note that in some panels, the blue $\beta=0$ curves may not be visible because they overlap heavily with the green $\beta=1$ curves.
 The solid lines in the two power-law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean.
@@
 	\par From these initial results, there is an important difference in the information available in potential observations.
-Below $T_m$ the value of $a$ requires a specific form of the waiting time between nanoflares which in turn informs about the nature of energy release \citep{cargill_active_2014}.
+Below $T_m$ the observed values of $a$ require a specific form of the waiting time between nanoflares which in turn informs about the nature of energy release \citep{cargill_active_2014}.
 Above $T_m$, there is no information about the role of a waiting time, but the emission measure distribution does inform about the need for a power-law energy distribution and the density in which the nanoflare occurs.
@@
 For example, we noted earlier that the temperature coverage for \textit{Hinode} and SDO is good for $T<T_m$, but patchy for $T>T_m$.
-On the other hand, the proposed MaGIXS instrument has the opposite performance regime.
+On the other hand, the proposed MaGIXS \citep{kobayashi_marshall_2011,winebarger_new_2014} instrument has the opposite performance regime.
 This differs from EUVE observations of some stellar coronae which have very complete temperature coverage from $10^6$ K to over $10^7$ K \citep[e.g.][]{sanz-forcada_structure_2003}, and have been modeled using low frequency nanoflares \citep{cargill_temperature-emission_2006}.
@@
 Both observational and modeling studies have found that $2\lesssim a\lesssim5$ \citep[see Table 3 of][]{bradshaw_diagnosing_2012} and in particular, \citet{cargill_active_2014} found that a heating function of the form $t_N\propto\varepsilon$ was needed in order to account for this range of slopes.
-The EIS instrument \citep{culhane_euv_2007} on \textit{Hinode} permits good temperature coverage.
+In this range, the EIS instrument \citep{culhane_euv_2007} on \textit{Hinode} permits good temperature coverage.
 Additionally, a similar scaling of $\mathrm{EM}\propto T^{-b}$ for $10^{6.6}\le T\le10^{7.0}$ has been claimed though measurements of $b$ have been subject to large uncertainties \citep{warren_systematic_2012} due to intermittent temperature coverage.
@@
 	%%
-	\section{Discussion}
-	\label{sec:discussion}
-	%%
-	\authorcomment1{Is this section really even necessary?
-Can the discussion be entirely contained in (last part of) the Results section?
-Or we could convert \autoref{subsec:diagnostics} to the Discussion section...}
-	%
 	\section{Conclusions}

### 2016-08-10 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
rewrite of section 3.2.2 and conclusions by PC, small edits

@@
 	%%
-	\par One characteristic of the $\mathrm{EM}(T)$ distribution arising from low- and intermediate-frequency nanoflares is that $\mathrm{EM}(T)$ is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}.
-For example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 10^{6.2}$ K and $10^{6.9}$ K.
-Given two observed temperatures (due say to specific emission lines), this suggests that predictions from the ratio of emission at these temperatures can be compared with data.
-This is of particular use where very limited spectral coverage is available either above or below $T_m$.
+		\par\citet{brosius_pervasive_2014} proposed another possible diagnostic for the hot non-flaring corona.
+Using observations of an active region from the \textit{EUNIS-13} sounding rocket, they found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside.
+They argue that this provides possible evidence for impulsive heating.
+This arises from the fact that the $\mathrm{EM}(T)$ distribution arising from low- and intermediate-frequency nanoflares is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}: for example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 10^{6.2}$ K and $10^{6.9}$ K.
+This suggests that the approach of \citet{brosius_pervasive_2014} could be used for any pair of appropriate emission lines and is likely to be of particular use where very limited spectral coverage is available either above or below $T_m$.
 Indeed for impulsive heating of any kind, the generic $\mathrm{EM}(T)$ curve remains similar (though not identical) as the magnitude of the heating changes.
 For flare-like energy release one would expect the hot emission to be much greater than the cold emission, with the opposite in the quiet Sun.
-For nanoflares, one might expect them to be of the same order.
-	%
-	\par An example of how this approach might work can be found in \citet{brosius_pervasive_2014}.
-Using observations of an active region from the \textit{EUNIS-13} sounding rocket, they found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside.
-They argue that this provides possible evidence for impulsive heating.
-\authorcomment1{These next few sentences need tightening up; next round of edits...have updated to be consistent with new choice for em ratio}As a proxy for this intensity ratio and an alternative to the hot emission measure slope $b$, we propose using an emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$.
-Unlike an emission measure slope, where a functional relationship is assumed over a range of $T$ in $\mathrm{EM}(T)$, a simple emission measure ratio gives information about the emission at only a single ``hot'' temperature relative to a single ``cool'' temperature.
-Using this ratio, we can assess the relative strength of $\mathrm{EM}(T)$ above and below $T_m$ and in doing so, assess the expected range of emission measure ratios consistent with nanoflare heating.
-We choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.2}$ K, consistent with \citet{brosius_pervasive_2014} The ratio of other emission lines could also be used.
-	%
-	\par Such an emission measure ratio also provides a way to compare in a concise way every point in our multidimensional parameter space while acknowledging that we are reducing $8\times10^4$ s of loop evolution to a single value.
-The left panel of \autoref{fig:em_ratio_hist_single} shows the single-fluid case, where each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function.
+
+	\par We define a general emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$ and for this paper consider $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.2}$ K, consistent with \citet{brosius_pervasive_2014}.
+This also provides a way to compare in a concise way every point in our multidimensional parameter space while acknowledging that we are reducing $8\times10^4$ s of loop evolution to a single value.
+This ratio is shown in \autoref{fig:em_ratio_hist_single}, \autoref{fig:em_ratio_hist_el}, and \autoref{fig:em_ratio_hist_ion} for the single-fluid model, electron and ion heating, respectively.
+In the left-hand panels each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function.
 This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$ and $t_{N,i}=t_N$ for all $i$ (i.e.
 $\beta=0$).
-We see that the emission measure ratio is largely insensitive to $\alpha$ and is peaked sharply at $\sim0.75-1.0$; the distribution peaks at slightly higher values for the $\beta=1$ case ($\sim1.25$) though the overall shape of the distributions is the same.
-Note that the uniform heating results (whose median is denoted by the vertical purple line near $\sim0.5$) show emission measure ratios significantly less than those in the power-law cases, consistent with the reduced hot emission shown in \autoref{fig:el_em}.
-	%
-	\par The right panel of \autoref{fig:em_ratio_hist_single} shows these same emission measure ratios, but now separated by $t_N$.
+The right panel of \autoref{fig:em_ratio_hist_single} shows these same emission measure ratios, but now categorized by $t_N$.
 For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e.
@@
 Note that we choose to only show results for five values of $t_N$ for aesthetic purposes.
-For $t_N\le4000$ s, the results cluster just near 1.0, though the $t_N=3000$ s distribution is slightly bimodal, peaking strongly at $\sim0.75$ and more weakly at $\sim1.25$.
+
+	\par Considering first the left hand panels, in the single fluid model the ratio is largely insensitive to $\alpha$ and is peaked sharply at $\sim0.75-1.0$ although the distribution peaks at slightly higher values for the $\beta=1$ case ($\sim1.25$).
+Note that the uniform heating results (whose median is denoted by the vertical purple line near $\sim0.5$) show emission measure ratios significantly less than those in the power-law cases, consistent with the reduced hot emission shown in \autoref{fig:single_em}.
+For electron heating the ratio is again insensitive to $\alpha$, but is narrower and falls off more quickly toward higher emission measure ratios.
+The $\beta=0$ cases (for all $\alpha$) peak near $0.5$, with the $\beta=1$ cases all peaking at slightly higher values, but all less than 1.
+For ion heating the $\beta=0$ distributions peak at lower values compared to those with $\beta=1$.
+Again the results are relatively insensitive to $\alpha$.
+However, compared to the electron heating case, all of the distributions are much wider and peak at higher values, $\sim1.5$ for $\beta=0$ and $>2$ for $\beta=1$.
+Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$.
+
+	\par Turning to the right hand panels, in the single-fluid model for $t_N\le4000$ s, the results cluster just near 1.0, though the $t_N=3000$ s distribution is slightly bimodal, peaking strongly at $\sim0.75$ and more weakly at $\sim1.25$.
 Additionally, the $t_N=5000$ s case peaks slightly higher at $\sim1.5$ and does not ``pile up'' near 1.0 as the other values of $t_N$ do.
-In general, the distributions for all $t_N$ have a positive skew and are peaked in the range $\sim0.5-1.5$.
+For electron herating, the $t_N=3000$ distribution has a very strong and narrow peak at $\approx0.5$ while all of the other distributions peak at $\sim1$.
+For $t_N\ge3000$ s, the location of the peak increases weakly with increasing $t_N$ though this is not the case for $t_N=1000,2000$ s.
+Finally, for ion heating the distributions for each value of $t_N$ are much wider than for a single fluid and electron heating and the peak values show a stronger dependence on $t_N$.
+The range of peak values is also much larger, with the $t_N=1000$ s case peaking near 0 and the $t_N=5000$ s case peaking at $\sim2$.
+As in \autoref{fig:em_ratio_hist_single}, we see that the $t_N=3000$ s distribution is bimodal.
+In general, the distributions grouped by $t_N$ for all three heating types have a positive skew and are peaked in the range $\sim0.5-1.5$ except for some extreme case in the ion heating scenario.
 	%
-	\par Similarly, \autoref{fig:em_ratio_hist_el} shows the emission measure ratio for the case in which only the electrons are heated.
-Looking first at the left panel, we see that, as in \autoref{fig:em_ratio_hist_single}, the emission measure ratio is largely insensitive to $\alpha$, but is comparatively more narrow and falls off more quickly twoard higher emission measure ratios.
-The $\beta=0$ cases (for all $\alpha$) peak near $0.5$, with the $\beta=1$ cases all peaking at slightly higher values, but all less than 1.
-The right panel shows the same emission measure ratios now grouped by $t_N$.
-The $t_N=3000$ distribution has a very strong and narrow peak at $\approx0.5$ while all of the other distributions peak at $\sim1$.
-For $t_N\ge3000$ s, the location of the peak increases weakly with increasing $t_N$ though this is not the case for $t_N=1000,2000$ s.
-	%
-	\par Finally, we compute the same emission measure ratio for the case in which only the ions are heated.
-The left panel of \autoref{fig:em_ratio_hist_ion} shows histograms for each type of heating function.
-Similar to the electron  heating results, we find that the $\beta=0$ distributions peak at lower values compared to the $\beta=1$ distributions and that in the $\beta=0$ case, the distribution of emission measure ratios is relatively insensitive to $\alpha$.
-However, unlike the electron heating case, the distributions in all cases are much wider and peak at higher values, $\sim1.5$ for $\beta=0$ and $>2$ for $\beta=1$.
-Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$.
-The right panel of \autoref{fig:em_ratio_hist_ion} shows the same emission measure ratios now grouped by waiting time where again we only show five values of $t_N$.
-Compared to the results in the left panels of \autoref{fig:em_ratio_hist_single} and \autoref{fig:em_ratio_hist_el}, the distributions for each value of $t_N$ are much wider and the peak values show a stronger dependence on $t_N$.
-The range of peak values is also much larger, with the $t_N=1000$ s peaking near 0 and $t_N=5000$ s peaking at $\sim2$.
-As in \autoref{fig:em_ratio_hist_single}, we see that the $t_N=3000$ s distribution is bimodal.
-	%
-	\par\authorcomment2{These results suggest that emission measure ratios, for $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.2}$ K, consistent with nanoflare heating fall approximately in the range $\sim0.5-1.5$.
-We find that the resulting distributions of ratios are largely independent of the power-law index $\alpha$ and only weakly-dependent on the heating frequency, $t_N$ (with the exception of the ion heating case).
+	\par These results suggest that the emission measure ratio is generally in the range $\sim0.5-1.5$, with some higher values.
+Given the uncertainties in the atomic physics in particular, this seems to support the conclusion of the presence of nanoflare heating by \citet{brosius_pervasive_2014}.
+Thus the calculation of such ratios from limited data has the potential to be a powerful diagnostic of the existence of nanoflare heating.
+Whether one can say more about the precise form of nanoflare heating is less clear.
+In these results the ratios are largely independent of the power-law index $\alpha$ and only weakly-dependent on the heating frequency, $t_N$.
 Furthermore, the distributions are also weakly dependent on the relationship between the waiting time and heating rate, $\beta$.
-In this way, a determination of more detailed nanoflare properties from observations may be difficult without a very large number of measurements and relatively small uncertainties in the atomic data.
-However, while the single-fluid and electron heating distributions are relatively similar (see \autoref{fig:em_ratio_hist_single} and \autoref{fig:em_ratio_hist_el}), the resulting ion heating distributions are much wider, peak at higher values, and show a stronger dependence on $\alpha$, $\beta$, and $t_N$.
-We may interpret this as the emission on the hot side of $\mathrm{EM}(T)$ being relatively insensitive to these parameter changes when only the ions are heated.
-In this way, the emission measure ratio probes mostly changes in the cool emission which we already know to be sensitive to both $\beta$ and $t_N$ \citep{cargill_active_2014}.}
+The exception is the ion heating case where the distributions are much wider, peak at higher values, and show a stronger dependence on $\alpha$, $\beta$, and $t_N$.
+The problem with drawing conclusions from the details of these results lies in the numerous uncertainties in any data, especially concerning atomic physics.
 	%%
@@
 First we showed that while below $T_m$ a power law representation of $\mathrm{EM}\sim T^a$ was quite robust, that was not the case above $T_m$.
-On the other hand the calculation of a ratio between the emission measure at a pair temperatures above and below $T_m$ held more promise.
-\authorcomment2{By using this ratio as an alternative to the emission measure slope, we do not assume $\mathrm{EM}(T)$ to have a particular functional form and we account for emission on the hot and cool side of $\mathrm{EM}(T)$, both of which contain signatures of the heating.}
+On the other hand the calculation of a ratio between the emission measure at a pair of temperatures above and below $T_m$ held more promise.
+For a wide range of parameters the ratio of the emission measure at two temperatures, $T_{hot}>T_m$ at $10^{6.9}$ and $T_{cool}<T_m$ at $10^{6.2}$ was of order unity, consistent with \citet{brosius_pervasive_2014} within various errors.
+Further observational evidence of such ratios would, in our view, provide a very strong case for the presence of nanoflare heating.
+On the other hand, given the uncertainties in atomic physics and emission emasure analysis, such a comparison seems unlikely to be able to shed more detailed light on the details of the actual heating process.
 	%
-	\par\authorcomment2{While our emission measure ratio results show a relatively weak dependence on the particular properties of the heating (e.g.
-$\alpha,\beta,t_N$), we find that, for the electron heating, ion heating, and single-fluid cases, the peaks of the distributions all fall in the range $~0.5-1.5$.
-In this way, we find that the 0.59 emission measure ratio of \citet{brosius_pervasive_2014}, which they conclude to be a signature of nanoflares, is consistent with nanoflare heating for a range of different heating properties.
-A larger sample of observations in this wavelength range combined with the analysis presented here will help to constrain the heating properties of nanoflares.}
-	%
+	\par It is clear from this and the preceeding paper that characterization of this ``hot'' component is extremely challenging for a multiplicity of reasons.
+Progress is likely to come from the good spectral coverage of the MaGIXS instrument, and in particular from a space-based successor which could confirm beyond doubt the presence of the hot component.
+On the other hand, it seems doubtful that information regarding the plasma physics of the heating process can come from such instrumentation.
+Information from high-energy instruments would be then desirable, but the energies of interest ($\approx1$ keV) are highly challenging.
+In any event, complete wavelength coverage seems essential, something that we noted earlier stellar astronomers have had for decades.
+
 	\acknowledgments

### 2016-08-10 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
fixing reference to nonexistent section discussion

@@
 \autoref{sec:results} shows the resulting emission measure distributions and diagnostics for the entire parameter space.
-In \autoref{sec:discussion}, we discuss the impacts of two-fluid effects, pre-nanoflare density, and NEI on these calculated observables and how they may be interpreted in the context of nanoflare heating.
-Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.
+Finally, \autoref{sec:conclusions} discusses how our results may be interpreted in the broader context of nanoflare heating and provides some concluding comments on our findings.
 	%%

### 2016-08-16 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
incorporating revised section 3.1, abstract, and conclusions from PC; some more minor edits and markup comments

@@
 	\begin{abstract}
-		Faint, high-temperature emission in active region cores has long been predicted as a signature of nanoflare heating.
-However, the detection of such emission has proved difficult due to a combination of the efficiency of thermal conduction, non-equilibrium ionization, and inadequate instrument sensitivity.
-In this second paper in our series on ``hot'' non-flaring plasma in active regions, we investigate the influence of repeating nanoflares of varying frequency on the resulting emission measure distribution .
-We have used an efficient two-fluid hydrodynamic model to carry out a parameter exploration in preferentially heated species, heating event frequency, and the power-law index determining the distribution of event energies.
-We compute the emission measure distribution for each point in our multi-dimensional heating parameter space in an effort to understand how each of these variables impacts the observed emission.
-Additionally, we calculate several observables and compare their efficacy in capturing the character of both the hot and cool parts of the emission measure distribution.
+	Despite its prediction over two decades ago, the detection of faint, high-temperature (``hot'') emission due to nanoflare heating in non-flaring active region cores has proved challenging.
+Using an efficient two-fluid hydrodynamic model, this paper investigates the properties of the emission expected from repeating nanoflares (a nanoflare train) of varying frequency as well as the separate heating of electrons and ions.
+If the emission measure distribution ($\mathrm{EM}(T)$) peaks at $T = T_m$, we find that $\mathrm{EM}(T_m)$ is independent of details of the nanoflare train, and $\mathrm{EM}(T)$ above and below $T_m$ reflects different aspects of the heating.
+Below $T_m$ the main influence is the relationship of the waiting time between successive nanoflares to the nanoflare energy.
+Above $T_m$ power-law nanoflare distributions lead to an extensive plasma population not present in a monoenergetic train.
+Furthermore, in some cases characteristic features are present in $\mathrm{EM}(T)$.
+Such details may be detectable given adequate spectral resolution and a good knowledge of the relevant atomic physics.
+In the absence of such resolution we propose some metrics that can be used to infer the presence of ``hot'' plasma.
 	\end{abstract}
@@
 Both species cool through a combination of thermal conduction ($F_{ce,0},\,F_{ci,0}$) and an enthalpy flux to the lower atmosphere, with the electrons also undergoing radiative cooling ($\mathcal{R_C}$).
-In the case of conductive cooling, a flux limiter, $F=(1/2)fnk_BTV_e$, is imposed to mitigate runaway cooling in a low-density, high-temperature plasma.
+In the case of conductive cooling, a flux limiter, $F_s=(1/2)fnk_BTV_e$, is imposed to mitigate runaway cooling in a low-density, high-temperature plasma.
 In all cases we use a saturation limit of $f=1$.
@@
 Note that in some panels, the blue $\beta=0$ curves may not be visible because they overlap heavily with the green $\beta=1$ curves.
-The solid lines in the two power-law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean.
+The solid lines in the two power law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean.
 The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.
@@
 	%
-	\par In our first set of results, we compare $\mathrm{EM}(T)$ for three different types of heating functions, across a sample of six different heating frequencies.
-\autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions in the single-fluid case, electron heating case, and ion heating case, respectively.
-Each panel in each figure corresponds to a different waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a power-law distribution of index $\alpha=-2.5$ ($\beta=0$ case, blue), and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event ($\beta=1$ case, green).
-Note that in all three figures, we show the results for only a single power-law index, $\alpha=2.5$.
-Furthermore, the dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$.
-The cases shown in \citetalias{barnes_inference_2016} correspond approximately to the red curves in the lower right panels ($t_N=5000$ s) of each of the three figures since the loop is allowed to cool and drain completely before reheating and a single nanoflare energy is used.
+	\par We compare $\mathrm{EM}(T)$ for three different types of heating functions, across a sample of six different heating frequencies.
+\autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions for the single-fluid, electron heating, and ion heating cases respectively.
+Each panel corresponds to a different waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a single power-law distribution of index $\alpha=-2.5$ with constant waiting time ($\beta=0$ case, blue), and a waiting time that depends on the energy released in the preceding event ($\beta=1$ case, green).
+The dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$.
+The cases shown in \citetalias{barnes_inference_2016} correspond approximately to the red curves in the lower right panels ($t_N=5000$ s) in each of the three figures since the loop is allowed to cool and drain completely before reheating and a single nanoflare energy is used.
 	%
@@
 	%
-	\par We look first at $\mathrm{EM}(T)$ for the single-fluid case, \autoref{fig:single_em}.
+	\par In all cases, $\mathrm{EM}(T)$ has some generic properties.
 Firstly, as expected from \citet{cargill_active_2014}, as $t_N$ increases, $\mathrm{EM}(T)$ widens, extending to both cooler ($<4$ MK) and hotter ($>4$ MK) temperatures.
-The extension toward cooler temperatures arises because as $t_N$ increases there is more time between successive heating events so that the loop cools to lower temperatures before being reheated.
+Secondly, for a prescribed value of $t_N$, the values of $\mathrm{EM}(T_m)$ and $T_m$ are approximately the same for all forms of heating.
+This can be attributed to the effective coupling between the species at $n(T_m)$ and suggests that $\mathrm{EM}(T)$ above and below $T_m$ can be considered separately, with each providing information about different aspects of the heating.
+	%
+	\par For $T<T_m$, the extension of $\mathrm{EM}(T)$ toward cooler temperatures arises because as $t_N$ increases there is more time between successive heating events so that the loop cools to lower temperatures before being reheated.
 The dependence on $\alpha$ and $\beta$ is similar to that described in \citet{cargill_active_2014}.
-The uniform (red) and $\beta=0$ (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the $\beta=1$ curves (green) extend to cooler temperatures much more rapidly.
-For example, at $t_N=1500$ s, both the uniform and $\beta=0$ cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK \citep{cargill_active_2014}.
-As in \citetalias{barnes_inference_2016}, the results below $T_m$ are relatively independent of which species is heated.
+For both uniform heating (red) and a power-law index without waiting time (blue), $\mathrm{EM}(T)$ falls off more rapidly than when a waiting time is included (green) for intermediate frequencies.
+For example, for $t_N=1500$ s, both the uniform and $\beta=0$ cases show little to no emission below 2 MK while the $\beta=1$ case extends to temperatures well below 1 MK.
+Thus this part of $\mathrm{EM}(T)$ has information about the need for a waiting time, but not about the details of which species is heated.
 		%
-	\par The behavior of $\mathrm{EM}(T)$ above $T_m$ is more complicated.
-For small $t_N$, the emission measure distribution falls off sharply on the hot side for a uniform nanoflare train but a power-law distribution leads to a broader distribution above $T_m$.
-This just reflects the different initial temperatures generated with a power-law distribution since $T \simeq H^{2/7}$.
+	\par The behavior of $\mathrm{EM}(T)$ above $T_m$ is more complicated, but because $\mathrm{EM}(T_m)$ and $T_m$ are the same for all parameters, we can make a meaningful comparison between the different heating models.
+For the single-fluid model and short $t_N$, the emission measure distribution falls off sharply on the hot side for a uniform nanoflare train, but choosing heating events from a power law leads to a broader distribution.
+This just reflects the different initial temperatures generated with a power-law distribution since $T \simeq H^{2/7}$, where $H$ is the heating rate.
 As $t_N$ increases, the distribution for uniform heating gradually broadens as the initial temperature rises due to the lower density in which the heating occurs.
-A similar broadening occurs for the power laws with the $\beta=0$ and $\beta=1$ results showing little difference.
+A similar broadening occurs for power law heating distributions with the $\beta=0$ and $\beta=1$ results showing little difference.
 Note that the $\beta=0$ curve is barely visible as it overlaps almost completely with the $\beta=1$ curve.
@@
 For a uniform nanoflare train, NEI plays no role up to $t_N$ = 2500 sec, but above that it restricts the temperatures that can be detected, as shown in \citetalias{barnes_inference_2016}.
-This hot emission is relocated to cooler temperatures, resulting in a ``bump'' in the emission measure distribution near 10 MK.
-On the other hand, NEI plays almost no role in the power law distributions, in both the $\beta=1$ and $\beta=0$ cases.
+This hot emission is relocated to cooler temperatures, resulting in a small ``bump'' in the emission measure distribution near 10 MK.
+On the other hand, NEI plays almost no role in the power-law distributions, for either the $\beta=0$ or $\beta=1$ cases.
 	%
-	\par From these initial results, there is an important difference in the information available in potential observations.
-Below $T_m$ the observed values of $a$ require a specific form of the waiting time between nanoflares which in turn informs about the nature of energy release \citep{cargill_active_2014}.
-Above $T_m$, there is no information about the role of a waiting time, but the emission measure distribution does inform about the need for a power-law energy distribution and the density in which the nanoflare occurs.
-Taken together, the overall conclusion is the same: nanoflares require an \textit{intermediate frequency}.
+	\par For electron heating, the $\mathrm{EM}(T)$ curves for the different types of heating functions shown in \autoref{fig:el_em} evolve similarly to those shown in \autoref{fig:single_em}.
+For $t_N\le750$ s, the electron and single-fluid cases are quite similar at $T>T_m$.
+However, for $t_N\ge1500$ s $\mathrm{EM}(T)$ steepens just above 4 MK and then flattens out near 10 MK.
+This change in shape is most obvious in the uniform heating case where a distinct ``hot shoulder'' forms just above 10 MK.
+In the power law cases, this feature is less pronounced though $\mathrm{EM}(T)$ extends to slightly higher temperatures.
+Again for a power-law distribution NEI is not important while for uniform heating, the hot emission is again truncated and leads to a``bump'' in $\mathrm{EM}(T)$ near $10$ MK.
 	%
-	\par For electron heating, the $\mathrm{EM}(T)$ curves for the different types of heating functions shown in \autoref{fig:el_em} evolve similarly to those shown in \autoref{fig:single_em}, especially on the cool side where the density is sufficiently high such that the electrons and the ions to equilibrate.
-On the hot side, for $t_N\le750$ s, the electron and single-fluid cases are quite similar.
-However, for $t_N\ge1500$ s, in the electron heating case, $\mathrm{EM}(T)$ steepens just above 4 MK and then flattens out near 10 MK.
-This change in shape is most obvious in the uniform heating case where a distinct ``hot shoulder'' forms just above 10 MK.
-In the power-law cases, this feature is less pronounced though $\mathrm{EM}(T)$ extends to slightly higher temperatures.
-The conclusions regarding the role of NEI are similar to those in the single-fluid case: it is not a factor when the heating rates are determined by a power-law.
-In the uniform case, the hot emission is again truncated and relocated to cooler temperatures, with more pronounced ``bump'' in the $\mathrm{EM}(T)$ near $10$ MK.
+	\par When only the ions are heated (\autoref{fig:ion_em}), for intermediate to low heating frequencies (i.e.
+$t_N\ge1500$ s), $\mathrm{EM}(T)$ in the uniform heating case is truncated below 10 MK and in the power law cases extends to just above 10 MK for the lowest heating frequency ($t_N=5000$ s).
+This cutoff at lower temperatures is due to the fact that the electrons cannot ``see'' the ions until they have cooled well below their peak temperature.
+This is discussed in \citetalias{barnes_inference_2016} though in the single-pulse cases, the cutoff occured at lower temperatures.
+Additionally, in both the uniform and power law cases, the peak of $\mathrm{EM}(T)$ is wider for these low frequencies compared to those shown in the lower right panels of \autoref{fig:single_em} and \autoref{fig:el_em}.
+NEI now plays no role in any of the cases.
 	%
-	\par When only the ions are heated (\autoref{fig:ion_em}), the cool side of the $\mathrm{EM}(T)$ is again very similar to both the single-fluid and electron heating cases due to equilibration.
-On the hot side, for intermediate to low heating frequencies (i.e.
-$t_N\ge1500$ s), the $\mathrm{EM}(T)$ in the uniform heating case is truncated below 10 MK and in the power-law cases extends to just above 10 MK for the lowest heating frequency ($t_N=5000$ s).
-This cutoff at lower temperatures is due to the fact that electrons cannot ``see'' the ions until they have cooled well below their peak temperature.
-This is discussed in \citetalias{barnes_inference_2016} though in the single-pulse cases, the cutoff occured at lower temperatures.
-Additionally, in both the uniform and power-law cases, the peak of $\mathrm{EM}(T)$ is wider for these low frequencies compared to those cases shown in the lower right panels of \autoref{fig:single_em} and \autoref{fig:el_em}.
-Regarding the role of NEI, there is no significant difference between $\mathrm{EM}(T)$ and $\mathrm{EM}(T_{eff})$ for either the uniform or power-law cases.
-Here the electrons are essentially heated on a timescale dictated by the Coulomb collision frequency which is slow enough to ensure ionization equilibrium throughout the heating and conductive cooling phases.
+	\par From these results, we see that new information about the heating is potentially available above $T_m$, but unlike at lower temperatures (i.e.
+$T<T_m$), information about the role of a waiting time is lost.
+For high frequency nanoflares, there is no plasma above $10^{6.8}$ K in any of the heating scenarios.
+For intermediate frequency, there is a significant enhancement in the hot emission when a power-law energy distribution is used compared with the uniform heating case.
+For low frequencies, the enhancement with the power-law distrubution is less noticeable, while for uniform heating both electron and single fluid models show distinctive features in the emission measure distribution.
+\authorcomment1{Not really sure about this last paragraph here...what are we trying to say?
+$T>T_m$ offers up more information about the heating, but the frequency determines how much information you get?
+Reworking the last two sentences: }\authorcomment2{For intermediate heating frequencies, there is a significant enhancement in $\mathrm{EM}(T>T_m)$ for the power law cases relative to the uniform heating case in the single-fluid, electron heating, and ion heating cases.
+For low frequencies, this discrepancy is less pronounced, though the uniform single-fluid and electron heating cases show distinctive features in $\mathrm{EM}(T)$ near 10 MK.}
 	%
@@
 	% 
-	\par In the single-fluid and electron heating cases, while $\mathrm{EM}(T)$ in the uniform and power-law heating cases generally agree for low-frequency heating ($t_N=5000$ s), for intermediate frequencies ($t_N\approx750-2500$ s), the power-law cases show an enhanced high-temperature component compared to the uniform case as seen in \autoref{fig:single_em} and \autoref{fig:el_em}.
+	\par In the single-fluid and electron heating cases, while $\mathrm{EM}(T)$ in the uniform and power-law heating cases generally agree for low-frequency heating ($t_N=5000$ s), for intermediate frequencies ($t_N\approx750-2500$ s), the power law cases show an enhanced high-temperature component compared to the uniform case as seen in \autoref{fig:single_em} and \autoref{fig:el_em}.
 \autoref{fig:nT_sample_profiles} shows sample heating, temperature, and density profiles for an intermediate heating frequency ($t_N=2500$ s), in the case where only the electrons are heated, for the three different types of heating functions.
@@
 	\par In comparing various heating models, we insist that the total energy injected into the loop is the same for each run (see \autoref{eq:heating_rate_constraint}).
-When the nanoflare heating rates are distributed according to a power-law, there will be many events where $H_i<H_0$ and a few events where $H_i\gg H_0$.
+When the nanoflare heating rates are distributed according to a power law, there will be many events where $H_i<H_0$ and a few events where $H_i\gg H_0$.
 These few high energy events lead to $T\gg T_{max,0}$ (blue and green curves) as seen in the middle panel of \autoref{fig:nT_sample_profiles}.
@@
 Additionally, we note that the only effect of the longer wait times in the $\beta=1$ case as compared to the $\beta=0$ case is an extended cool emission measure at intermediation frequencies (e.g.
-$t_N=2500$ s); the hot part of $\mathrm{EM}(T)$ for both power-law cases is nearly identical.
+$t_N=2500$ s); the hot part of $\mathrm{EM}(T)$ for both power law cases is nearly identical.
 Thus, the hot and cool sides of the emission measure distribution are largely isolated from one another as they are determined by separate phases of the loop evolution.
@@
 	%%
-	The relation of these results to potential solar observations is made difficult by incomplete temperature coverage.
+	\par The relation of these results to potential solar observations is made difficult by incomplete temperature coverage.
 For example, we noted earlier that the temperature coverage for \textit{Hinode} and SDO is good for $T<T_m$, but patchy for $T>T_m$.
@@
 This differs from EUVE observations of some stellar coronae which have very complete temperature coverage from $10^6$ K to over $10^7$ K \citep[e.g.][]{sanz-forcada_structure_2003}, and have been modeled using low frequency nanoflares \citep{cargill_temperature-emission_2006}.
-In the following sub-sections we propose ways that the paucity of solar temperature coverage can be partially remedied.
+The results in \autoref{subsec:em_dist} suggest that given good spectral resolution, there may be detectable features in $\mathrm{EM}(T)$, although atomic physics and other uncertainties would still be a concern.
+Instead, in the following sub-sections we propose ways that the paucity of solar temperature coverage can be partially remedied by a consideration of simple metrics.
 	%
@@
 We select a single sample run from our parameter space in which only the electrons are heated by nanoflares from a power-law distribution of $\alpha=-2.5$ and spaced uniformly by an interval of $t_N=5000$ s.
-We calculate the resulting $\mathrm{EM}(T)$ and fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting as implemented in the scipy scientific Python package \citep{van_der_walt_numpy_2011}.
+We calculate the resulting $\mathrm{EM}(T)$ and fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting.
 We fix the lower limit on each interval such that $T_{c,min}=10^{5.7}$ K and $T_{h,min} = 10^{6.7}$  K and vary the upper limits over $10^{6.1}<T_{c,max}<10^{6.5}$ K and $10^{6.8}<T_{h,max}<10^{7.2}$ K.
@@
 They argue that this provides possible evidence for impulsive heating.
-This arises from the fact that the $\mathrm{EM}(T)$ distribution arising from low- and intermediate-frequency nanoflares is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}: for example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 10^{6.2}$ K and $10^{6.9}$ K.
+This arises from the fact that the $\mathrm{EM}(T)$ distribution resulting from low- and intermediate-frequency nanoflares is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}: for example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 10^{6.2}$ K and $10^{6.9}$ K.
 This suggests that the approach of \citet{brosius_pervasive_2014} could be used for any pair of appropriate emission lines and is likely to be of particular use where very limited spectral coverage is available either above or below $T_m$.
@@
 	\par We define a general emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$ and for this paper consider $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.2}$ K, consistent with \citet{brosius_pervasive_2014}.
-This also provides a way to compare in a concise way every point in our multidimensional parameter space while acknowledging that we are reducing $8\times10^4$ s of loop evolution to a single value.
+This also provides a way to compare in a concise way every point in our multidimensional parameter space though we acknowledge that we are reducing $8\times10^4$ s of loop evolution to a single value.
 This ratio is shown in \autoref{fig:em_ratio_hist_single}, \autoref{fig:em_ratio_hist_el}, and \autoref{fig:em_ratio_hist_ion} for the single-fluid model, electron and ion heating, respectively.
@@
 $\beta=0$).
-The right panel of \autoref{fig:em_ratio_hist_single} shows these same emission measure ratios, but now categorized by $t_N$.
+The right panels show these same emission measure ratios, but now categorized by $t_N$.
 For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e.
@@
 	\par Considering first the left hand panels, in the single fluid model the ratio is largely insensitive to $\alpha$ and is peaked sharply at $\sim0.75-1.0$ although the distribution peaks at slightly higher values for the $\beta=1$ case ($\sim1.25$).
-Note that the uniform heating results (whose median is denoted by the vertical purple line near $\sim0.5$) show emission measure ratios significantly less than those in the power-law cases, consistent with the reduced hot emission shown in \autoref{fig:single_em}.
+Note that the uniform heating results (whose median is denoted by the vertical purple line near $\sim0.5$) show emission measure ratios significantly less than those in the power law cases, consistent with the reduced hot emission shown in \autoref{fig:single_em}.
 For electron heating the ratio is again insensitive to $\alpha$, but is narrower and falls off more quickly toward higher emission measure ratios.
@@
 Additionally, the $t_N=5000$ s case peaks slightly higher at $\sim1.5$ and does not ``pile up'' near 1.0 as the other values of $t_N$ do.
-For electron herating, the $t_N=3000$ distribution has a very strong and narrow peak at $\approx0.5$ while all of the other distributions peak at $\sim1$.
+For electron herating, the $t_N=3000$ s distribution has a very strong and narrow peak at $\approx0.5$ while all of the other distributions peak at $\sim1$.
 For $t_N\ge3000$ s, the location of the peak increases weakly with increasing $t_N$ though this is not the case for $t_N=1000,2000$ s.
@@
 	%
-	\par In this paper we have carried out two-fluid modeling of nanoflare trains in AR cores and considered a range of power-law slopes and models of waiting time between events.
-For each set of parameters we have generated the emission measure distribution, $\mathrm{EM}(T)$.
-An important outcome is that, defining the peak of the emission measure as $T = T_m$, the distribution $\mathrm{EM}(T)$ on either side of $T_m$ reveals different information about the heating mechanism.
-Below $T_m$ the principle factor in determining the distribution is the presence of a waiting time between nanoflares: the high densities below $T_m$ mean that species equilibration has occurred; thus no information of which species was heated remains.
+	\par In this paper we have carried out two-fluid modeling of nanoflare trains in AR cores and considered a range of models for the nanoflare energy distribution and timing as well as preferential heating of different species.
+For each set of parameters we have generated the emission measure distribution as a function of temperature.
+If the peak of the emission measure occurs at $T = T_m$, then we found that $T_m$ and $\mathrm{EM}(T_m)$ were independent of the properties of the nanoflare train and which species was heated.
+As a consequence, we demonstrated that the form of $\mathrm{EM}(T)$ on either side of $T_m$ reflected different aspects of the heating process.
+Below $T_m$ the principle factor in determining $\mathrm{EM}(T)$ is the presence of a waiting time between nanoflares: the high densities below $T_m$ mean that species temperature equilibration has occurred so that no information about which species was heated remains.
 		%
-	\par Above $T_m$, higher temperatures arise when a power law distribution of energy is assumed.
+	\par Above $T_m$, higher temperatures arise when a power-law distribution of energy is assumed than for a nanoflare train with uniform heating rates.
 However, no information about the presence of a waiting time survives.
-Higher observed temperatures also arise for the cases of a single fluid and electron heating than ion heating since a finite equilibration time means that in the latter case the electrons are heated more slowly.
-In all these cases we find that, unlike some of the examples in \citetalias{barnes_inference_2016}, NEI is not a major consideration.
+Higher observed temperatures also arise for the single-fluid and electron heating cases compared to the ion heating case since a finite equilibration time means that in the latter case the electrons are heated more slowly, and in some cases there are local peaks in $\mathrm{EM}(T)$.
+\authorcomment1{What does the last part of the sentence mean?} We find that, unlike some of the examples in \citetalias{barnes_inference_2016}, NEI is not a major consideration, a constant nanoflare train being the exception.
 		%
 	\par Two possible ways to relate these results to present and future observations were discussed.
-First we showed that while below $T_m$ a power law representation of $\mathrm{EM}\sim T^a$ was quite robust, that was not the case above $T_m$.
+First we showed that while below $T_m$ the well-known relation $\mathrm{EM}\sim T^a$ was quite robust, that was not the case above $T_m$.
 On the other hand the calculation of a ratio between the emission measure at a pair of temperatures above and below $T_m$ held more promise.
-For a wide range of parameters the ratio of the emission measure at two temperatures, $T_{hot}>T_m$ at $10^{6.9}$ and $T_{cool}<T_m$ at $10^{6.2}$ was of order unity, consistent with \citet{brosius_pervasive_2014} within various errors.
+For a wide range of parameters the ratio of the emission measure at two temperatures, $T_{hot}=10^{6.9}>T_m$ and $T_{cool}=10^{6.2}<T_m$, was of order unity, consistent with \citet{brosius_pervasive_2014} within various errors.
 Further observational evidence of such ratios would, in our view, provide a very strong case for the presence of nanoflare heating.
-On the other hand, given the uncertainties in atomic physics and emission emasure analysis, such a comparison seems unlikely to be able to shed more detailed light on the details of the actual heating process.
+On the other hand, given the uncertainties in atomic physics and emission emasure analysis, such a comparison seems unlikely to be able to shed more detailed light on the details (e.g.
+$t_N$, $\alpha$, $\beta$) of the actual heating process.
 		%
 	\par It is clear from this and the preceeding paper that characterization of this ``hot'' component is extremely challenging for a multiplicity of reasons.
-Progress is likely to come from the good spectral coverage of the MaGIXS instrument, and in particular from a space-based successor which could confirm beyond doubt the presence of the hot component.
-On the other hand, it seems doubtful that information regarding the plasma physics of the heating process can come from such instrumentation.
-Information from high-energy instruments would be then desirable, but the energies of interest ($\approx1$ keV) are highly challenging.
-In any event, complete wavelength coverage seems essential, something that we noted earlier stellar astronomers have had for decades.
-
+Progress is likely to come from the good spectral coverage of the MaGIXS instrument, and in particular from a space-based successor which could confirm beyond doubt the presence of the hot component and perhaps measure the predicted features of $\mathrm{EM}(T)$.
+In the absence of complete spectral coverage, we propose a pair of metrics for the ``hot'' coronal component.
+Of particular interest is the ratio of pairs of emission lines characteristic of cool and hot plasma, as was recently discussed by \citet{brosius_pervasive_2014}.
+When high temperature spectral coverage is limited, information from high-energy instruments \authorcomment1{FOXSI or NuStar reference here?} would be then desirable, but the energies of interest ($\approx1$ keV) are highly challenging.
+In any event, complete wavelength coverage seems essential, something that we noted stellar astronomers have had for decades.
+	%
 	\acknowledgments

### 2016-08-26 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
some final edits before first round of review

@@
 \usepackage[utf8]{inputenc} %force unicode in bibtex
-\usepackage{enumitem}
 
@@
 \newcommand{\ang}{\AA~}
-\defcitealias{barnes_inference_2016}{Paper I}
+\defcitealias{barnes_inference_2016-1}{Paper I}
 \renewcommand{\sectionautorefname}{Section}
 \renewcommand{\subsectionautorefname}{Subsection}
-%\linenumbers
-%Set options for list spacing
-\setenumerate{noitemsep}
 %Set tikz options
@@
 	\par The emission component above $T_m$ has been the subject of less study, but is likely to be important as the so-called ``smoking gun'' of nanoflare heating since its properties may bear a close link to the actual heating.
-While many workers \citep{reale_evidence_2009,schmelz_hinode_2009,miceli_x-ray_2012,testa_hinode/eis_2012,del_zanna_elemental_2014,petralia_thermal_2014,schmelz_hot_2015} have claimed evidence of this hot, faint component of the emission measure, poor spectral resolution \citep{testa_temperature_2011,winebarger_defining_2012} and non-equilibrium ionization \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008} have made a positive detection of nanoflare heating difficult.
+While many workers \citep{reale_evidence_2009,schmelz_hinode_2009,miceli_x-ray_2012,testa_hinode/eis_2012,del_zanna_elemental_2014,petralia_thermal_2014,schmelz_hot_2015} have claimed evidence of this hot, faint component of the emission measure, poor spectral resolution \citep{testa_temperature_2011,winebarger_defining_2012} and non-equilibrium ionization \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008} may make a positive detection of nanoflare heating difficult.
 However, \citet{brosius_pervasive_2014} used observations from the \textit{EUNIS-13} sounding rocket to identify relatively faint emission from Fe XIX in a non-flaring active region (AR), suggesting temperatures of $\sim8.9$ MK.
@@
 \citet{warren_systematic_2012} find $7\lesssim b\lesssim10$ with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$.
-It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with different inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013,aschwanden_benchmark_2015}.
+It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with different inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013}.
 	%
@@
 	\par An analogous approach can be used to investigate the properties of the ``hot" coronal component expected from nanoflare heating, and is the subject of the present series of papers.
-In \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we looked at the hot plasma properties due to a single isolated nanoflare.
+In \citet{barnes_inference_2016-1} \citepalias[hereafter]{barnes_inference_2016-1}, we looked at the hot plasma properties due to a single isolated nanoflare.
 The effects of heating pulse duration, changes to conductive cooling due to heat flux limiting, differential heating of electrons and ions, and non-equilibrium ionization (NEI) were studied.
@@
 This amounts to computing spatial averages of the two-fluid hydrodynamic equations over both the transition region and corona.
-A full description and derivation of these equations can be found in the appendix of \citetalias{barnes_inference_2016}.
+A full description and derivation of these equations can be found in the appendix of \citetalias{barnes_inference_2016-1}.
 The relevant two-fluid pressure and density equations are,
@@
 	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency, and $\psi_{TR}$ is a term included to maintain charge and current and neutrality.
-Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional modifications detailed in Appendix 1 of \citetalias{barnes_inference_2016}.
+Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional modifications detailed in Appendix 1 of \citetalias{barnes_inference_2016-1}.
 These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$.
@@
 In all cases we use a saturation limit of $f=1$.
-See \citetalias{barnes_inference_2016} for a discussion of how $f$ is likely to effect the presence of hot emission in a nanoflare-heated plasma.
+See \citetalias{barnes_inference_2016-1} for a discussion of how $f$ is likely to effect the presence of hot emission in a nanoflare-heated plasma.
 	%
@@
 		\caption{Examples of four different heating functions: uniform heating amplitudes for $t_N=1000$ s (top), uniform heating amplitudes for $t_N=5000$ s (middle), and heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$ (bottom).
-In the bottom panel, the events shown in red have waiting times that depend on the previous event energy while the events shown in blue have uniform wait times.
-The mean wait time in both cases is $t_N=2000$ s.}
+In the bottom panel, the events shown in red have waiting times that depend on the previous event energy while the events shown in blue have uniform waiting times.
+The average waiting time in both cases is $t_N=2000$ s.}
 		\label{fig:heating_funcs}
@@
 Bursty, nanoflare heating is thought to arise from the stressing and subsequent relaxation of the coronal field.
-If a sufficient amount of energy is released into the loop, the field will need enough time to ``unravel'' and ``wind up'' again before the next event such that the subsequent waiting time is large.
-Conversely, if only a small amount of energy is released, the field will require a shorter unwinding time, resulting in a shorter interval between the subsequent events.
+If a sufficient amount of energy is released into the loop, the field will need enough time to ``wind up'' again before the next event such that the subsequent waiting time is large.
+Conversely, if only a small amount of energy is released, the field will require a shorter re-winding time, resulting in a shorter interval between the subsequent events.
 Thus, this scaling provides a way to incorporate a more physically motivated heating function into a hydrodynamic model which cannot self-consistently determine the heat input based on the evolving magnetic field.
 \autoref{fig:heating_funcs} shows the various heating functions used for several example $t_N$ values.
+Note that when $\beta=1$, $t_N$ is the \textit{average} waiting time between events since the waiting time after a particular event $i$ is dependent on the energy of that event.
 	%
@@
 This procedure is repeated $N_R$ times until $N\times N_R\sim10^4$ is satisfied.
-Thus, when $t_N=5000$ s and $N\sim16$, $N_R=625$, meaning the model is run 625 times with a heating frequency of $t_N=5000$ s in order to properly fill out the event energy distribution.
+Thus, when $t_N=5000$ s and $N\sim16$, $N_R=625$, meaning the model is run 625 times with a waiting time of $t_N=5000$ s in order to properly fill out the event energy distribution.
 	%
@@
 	%%
-	\par When considering the role of nanoflares in the production of hot plasma in AR cores, it is important to take non-equilibrium ionization (NEI) into account \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008}.
+	\par When considering the role of nanoflares in the production of hot plasma in AR cores, it is important to take non-equilibrium ionization (NEI) into account \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008,barnes_inference_2016-1}.
 In a steady heating scenario, the ionization state is an adequate measure of the electron plasma temperature.
@@
 	%
-	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results.
+	\par As in \citetalias{barnes_inference_2016-1}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results.
 Given a temperature ($T(t)$) and density ($n(t)$) profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$, that would be inferred by assuming ionization equilibrium.
@@
 	%
-	\par We now show the results of our nanoflare train simulations for each point in our multidimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$).
+	\par We now show the results of our nanoflare train simulations for each point in our multidimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), waiting time ($t_N$), and waiting-time/event energy relationship ($\beta$).
 In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s.
@@
 We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$.
-In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016}.
+In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016-1}.
 The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$.
@@
 		\plotone{figures/em_grid_single_a25.pdf}
-		\caption{Emission measure distributions for waiting-times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case.
-The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).
+		\caption{Emission measure distributions for waiting times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case.
+The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the waiting time after each event is proportional to the heating rate of the event (green).
+For the last case ($\beta=1$), $t_N$ is the average waiting time for all events.
 Note that in some panels, the blue $\beta=0$ curves may not be visible because they overlap heavily with the green $\beta=1$ curves.
@@
 \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions for the single-fluid, electron heating, and ion heating cases respectively.
-Each panel corresponds to a different waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a single power-law distribution of index $\alpha=-2.5$ with constant waiting time ($\beta=0$ case, blue), and a waiting time that depends on the energy released in the preceding event ($\beta=1$ case, green).
+Each panel corresponds to a different average waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a single power-law distribution of index $\alpha=-2.5$ with constant waiting time ($\beta=0$ case, blue), and a waiting time that depends on the energy released in the preceding event ($\beta=1$ case, green).
 The dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$.
-The cases shown in \citetalias{barnes_inference_2016} correspond approximately to the red curves in the lower right panels ($t_N=5000$ s) in each of the three figures since the loop is allowed to cool and drain completely before reheating and a single nanoflare energy is used.
+The cases shown in \citetalias{barnes_inference_2016-1} correspond approximately to the red curves in the lower right panels ($t_N=5000$ s) in each of the three figures since the loop is allowed to cool and drain completely before reheating and a single nanoflare energy is used.
 	%
@@
 Especially interesting in this case are the results with NEI included.
-For a uniform nanoflare train, NEI plays no role up to $t_N$ = 2500 sec, but above that it restricts the temperatures that can be detected, as shown in \citetalias{barnes_inference_2016}.
+For a uniform nanoflare train, NEI plays no role up to $t_N$ = 2500 sec, but above that it restricts the temperatures that can be detected, as shown in \citetalias{barnes_inference_2016-1}.
 This hot emission is relocated to cooler temperatures, resulting in a small ``bump'' in the emission measure distribution near 10 MK.
@@
 	\par When only the ions are heated (\autoref{fig:ion_em}), for intermediate to low heating frequencies (i.e.
-$t_N\ge1500$ s), $\mathrm{EM}(T)$ in the uniform heating case is truncated below 10 MK and in the power law cases extends to just above 10 MK for the lowest heating frequency ($t_N=5000$ s).
+$t_N\ge1500$ s), $\mathrm{EM}(T)$ in the uniform heating case is truncated below 10 MK and in the power law cases extends to just above 10 MK for the longest waiting time ($t_N=5000$ s).
 This cutoff at lower temperatures is due to the fact that the electrons cannot ``see'' the ions until they have cooled well below their peak temperature.
-This is discussed in \citetalias{barnes_inference_2016} though in the single-pulse cases, the cutoff occured at lower temperatures.
+This is discussed in \citetalias{barnes_inference_2016-1} though in the single-pulse cases, the cutoff occured at lower temperatures.
 Additionally, in both the uniform and power law cases, the peak of $\mathrm{EM}(T)$ is wider for these low frequencies compared to those shown in the lower right panels of \autoref{fig:single_em} and \autoref{fig:el_em}.
@@
 For high frequency nanoflares, there is no plasma above $10^{6.8}$ K in any of the heating scenarios.
-For intermediate frequency, there is a significant enhancement in the hot emission when a power-law energy distribution is used compared with the uniform heating case.
-For low frequencies, the enhancement with the power-law distrubution is less noticeable, while for uniform heating both electron and single fluid models show distinctive features in the emission measure distribution.
-\authorcomment1{Not really sure about this last paragraph here...what are we trying to say?
-$T>T_m$ offers up more information about the heating, but the frequency determines how much information you get?
-Reworking the last two sentences: }\authorcomment2{For intermediate heating frequencies, there is a significant enhancement in $\mathrm{EM}(T>T_m)$ for the power law cases relative to the uniform heating case in the single-fluid, electron heating, and ion heating cases.
-For low frequencies, this discrepancy is less pronounced, though the uniform single-fluid and electron heating cases show distinctive features in $\mathrm{EM}(T)$ near 10 MK.}
+For intermediate heating frequencies, there is a significant enhancement in $\mathrm{EM}(T>T_m)$ for the power law cases relative to the uniform heating case in the single-fluid, electron heating, and ion heating cases.
+For low frequencies, this discrepancy is less pronounced, though the uniform single-fluid and electron heating cases show distinctive features in $\mathrm{EM}(T)$ near 10 MK.
 	%
@@
 		\plotone{figures/nT_sample_curves_tn2500_electron.pdf}
-		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for the case in which only the electrons are heated with an intermediate heating frequency of $t_N=2500$ s.
+		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for the case in which only the electrons are heated with a waiting time of $t_N=2500$ s (i.e.
+an intermediate heating frequency).
 The three curves shown in each panel correspond to uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).}
@@
 	%
-	\par In \citet{cargill_active_2014}, \citetalias{barnes_inference_2016}, and \autoref{subsec:em_dist}, we have suggested that the plasma density prior to the nanoflare occuring is a crucial parameter in determining the emission measure distribution.
+	\par In \citet{cargill_active_2014}, \citetalias{barnes_inference_2016-1}, and \autoref{subsec:em_dist}, we have suggested that the plasma density prior to the nanoflare occuring is a crucial parameter in determining the emission measure distribution.
 This arises in two distinct ways.
@@
 	\par In the single-fluid and electron heating cases, while $\mathrm{EM}(T)$ in the uniform and power-law heating cases generally agree for low-frequency heating ($t_N=5000$ s), for intermediate frequencies ($t_N\approx750-2500$ s), the power law cases show an enhanced high-temperature component compared to the uniform case as seen in \autoref{fig:single_em} and \autoref{fig:el_em}.
-\autoref{fig:nT_sample_profiles} shows sample heating, temperature, and density profiles for an intermediate heating frequency ($t_N=2500$ s), in the case where only the electrons are heated, for the three different types of heating functions.
+\autoref{fig:nT_sample_profiles} shows sample heating, temperature, and density profiles for an intermediate heating frequency (i.e.
+a waiting time of $t_N=2500$ s), in the case where only the electrons are heated, for the three different types of heating functions.
 In the uniform heating rate case (red), each event has a maximum heating rate of $H_0$ such that the loop undergoes $N\approx30$ identical heating and cooling cycles, each time reaching a maximum temperature and density of $T_{max,0}$ and $n_{max,0}$, respectively.
@@
 In the uniform case, $T_{max,0}<10$ MK such that $\mathrm{EM}(T)$ has a steep cutoff right at 10 MK.
-Additionally, we note that the only effect of the longer wait times in the $\beta=1$ case as compared to the $\beta=0$ case is an extended cool emission measure at intermediation frequencies (e.g.
-$t_N=2500$ s); the hot part of $\mathrm{EM}(T)$ for both power law cases is nearly identical.
-Thus, the hot and cool sides of the emission measure distribution are largely isolated from one another as they are determined by separate phases of the loop evolution.
 	%
@@
 \citet{antiochos_evaporative_1978} showed analytically that accounting for evaporative cooling and assuming constant pressure gives $b=11/2$, though this value can be as low as $b=5/2$ if a flux limiter is included.
-However, in \citetalias{barnes_inference_2016}, we showed that in the case of a single 200 s nanoflare that heats only the electrons, the assumption of constant electron pressure during the heating and early conductive cooling phases does not hold.
-Our results here are consistent with our findings in \citetalias{barnes_inference_2016} in that the parameter $b$ does not provide any valuable information about $\mathrm{EM}(T)$ for $T>T_m$ when two-fluid effects are considered.
+However, in \citetalias{barnes_inference_2016-1}, we showed that in the case of a single 200 s nanoflare that heats only the electrons, the assumption of constant electron pressure during the heating and early conductive cooling phases does not hold.
+Our results here are consistent with our findings in \citetalias{barnes_inference_2016-1} in that the parameter $b$ does not provide any valuable information about $\mathrm{EM}(T)$ for $T>T_m$ when two-fluid effects are considered.
 Clearly, an alternative metric for measuring the amount of hot plasma in the emission measure distribution is needed.
@@
 Whether one can say more about the precise form of nanoflare heating is less clear.
-In these results the ratios are largely independent of the power-law index $\alpha$ and only weakly-dependent on the heating frequency, $t_N$.
+In these results the ratios are largely independent of the power-law index $\alpha$ and only weakly-dependent on the waiting time, $t_N$.
 Furthermore, the distributions are also weakly dependent on the relationship between the waiting time and heating rate, $\beta$.
@@
 However, no information about the presence of a waiting time survives.
-Higher observed temperatures also arise for the single-fluid and electron heating cases compared to the ion heating case since a finite equilibration time means that in the latter case the electrons are heated more slowly, and in some cases there are local peaks in $\mathrm{EM}(T)$.
-\authorcomment1{What does the last part of the sentence mean?} We find that, unlike some of the examples in \citetalias{barnes_inference_2016}, NEI is not a major consideration, a constant nanoflare train being the exception.
+Higher observed temperatures also arise for the single-fluid and electron heating cases where a ``hot shoulder'' can occur in $\mathrm{EM}(T)$ at $T\sim10$ MK.
+This is compared to the ion heating case where a finite equilibration time means that the electrons are heated more slowly.
+We find that, unlike some of the examples in \citetalias{barnes_inference_2016-1}, NEI is not a major consideration, a constant nanoflare train being the exception.
 		%
@@
 Of particular interest is the ratio of pairs of emission lines characteristic of cool and hot plasma, as was recently discussed by \citet{brosius_pervasive_2014}.
-When high temperature spectral coverage is limited, information from high-energy instruments \authorcomment1{FOXSI or NuStar reference here?} would be then desirable, but the energies of interest ($\approx1$ keV) are highly challenging.
+When high temperature spectral coverage is limited, information from high-energy instruments \citep{ishikawa_constraining_2014,hannah_first_2016,grefenstette_first_2016} would be then desirable, but the energies of interest ($\approx1$ keV) are highly challenging.
 In any event, complete wavelength coverage seems essential, something that we noted stellar astronomers have had for decades.
@@
 	%Bibliography
-	\bibliography{astrophys-abbrev.bib,references.bib}
+	\bibliography{references.bib}
 	\bibliographystyle{aasjournal}

### 2016-08-26 tex/paper.tex
updating paper.tex to current text, adding Tikz drawing

--- 2016-08-26 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
@@
 	\begin{figure}
-		\plotone{figures/heating_functions.pdf}
+		\plotone{../results/heating_functions.pdf}
 		\caption{Examples of four different heating functions: uniform heating amplitudes for $t_N=1000$ s (top), uniform heating amplitudes for $t_N=5000$ s (middle), and heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$ (bottom).
@@
 	\begin{figure*}[t]
-		\plotone{figures/em_grid_single_a25.pdf}
+		\plotone{../results/em_grid_single_a25.pdf}
 		\caption{Emission measure distributions for waiting times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case.
@@
 	\begin{figure*}[t]
-		\plotone{figures/em_grid_electron_a25.pdf}
+		\plotone{../results/em_grid_electron_a25.pdf}
 		\caption{Same as \autoref{fig:single_em}, but for the case where only the electrons are heated.}
@@
 	\begin{figure*}
-		\plotone{figures/em_grid_ion_a25.pdf}
+		\plotone{../results/em_grid_ion_a25.pdf}
 		\caption{Same as \autoref{fig:single_em}, but for the case where only the ions are heated.}
@@
 	\begin{figure*}
-		\plotone{figures/nT_sample_curves_tn2500_electron.pdf}
+		\plotone{../results/nT_sample_curves_tn2500_electron.pdf}
 		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for the case in which only the electrons are heated with a waiting time of $t_N=2500$ s (i.e.
@@
 	\begin{figure*}
-		\plotone{figures/em_slope_varying_bounds.pdf}
+		\plotone{../results/em_slope_varying_bounds.pdf}
 		\caption{Fits to a sample emission measure distribution constructed from a loop plasma in which only the electrons were heated by events chosen from a power-law distribution with $\alpha=-2.5$ and equally spaced by an interval of $t_N=5000$ s.
@@
 	\begin{figure*}
-		\plottwo{figures/ratio_hist_alpha_single_T1.pdf}{figures/ratio_hist_twait_single_T1.pdf}
+		\plottwo{../results/ratio_hist_alpha_single_T1.pdf}{../results/ratio_hist_twait_single_T1.pdf}
 		\caption{Histograms of emission measure ratios $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$, where $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.2}$ K, for all heating function types and heating frequencies for the single fluid case.
@@
 	\begin{figure*}
-		\plottwo{figures/ratio_hist_alpha_electron_T1.pdf}{figures/ratio_hist_twait_electron_T1.pdf}
+		\plottwo{../results/ratio_hist_alpha_electron_T1.pdf}{../results/ratio_hist_twait_electron_T1.pdf}
 		\caption{Same as \autoref{fig:em_ratio_hist_single}, but for the case where only the electrons are heated.}
@@
 	\begin{figure*}
-		\plottwo{figures/ratio_hist_alpha_ion_T1.pdf}{figures/ratio_hist_twait_ion_T1.pdf}
+		\plottwo{../results/ratio_hist_alpha_ion_T1.pdf}{../results/ratio_hist_twait_ion_T1.pdf}
 		\caption{Same as \autoref{fig:em_ratio_hist_single}, but for the case where only the ions are heated.

### 2016-08-28 make_aas_pkg.sh
adding figure manifest and script for packaging for AAS submission

@@ -1,0 +1,49 @@
+#!/bin/bash
+
+#Package TeX files in specific way for AAS/IOP submission. This script adjust paths and copies everything to a new folder and zips it up for you.
+
+#Create an arXiv package folder in the desired directory
+DEST=$1"aas_pkg/"
+if ! [ -d "$DEST" ]; then
+  mkdir $DEST
+fi
+
+#Clean up
+if [ "$2" == "clean" ]; then
+	echo "Cleaning up archive and directory at "$DEST
+	rm $1"aas_pkg.tar.gz"
+	exit 0
+fi
+
+#Make sure we are resolving paths correctly (even if not run in this dir)
+PATH2FILES=$(cd `dirname $0` && pwd)"/"
+
+#Copy needed TeX files
+cp $PATH2FILES"tex/paper."{"tex","bbl"} $DEST
+#cp $PATH2FILES"tex/aasjournal.bst" $DEST
+#cp $PATH2FILES"tex/aastex.cls" $DEST
+
+#Load figure manifest
+fig_array=(`cat $PATH2FILES"FIG_MANIFEST"`)
+array_len=${#fig_array[@]}
+for i in `seq 0 $((array_len-1))`
+do
+	cp $PATH2FILES"results/"${fig_array[$((i))]} $DEST
+done
+
+#copy tikz graphics to right spot
+cp $PATH2FILES"results/static/parameter_space_graphic.tex" $DEST
+
+#Replace relative paths to results
+OLD_PATH='../results/static/'
+NEW_PATH=''
+sed -i '' "s%${OLD_PATH}%${NEW_PATH}%g" $DEST"paper.tex"
+OLD_PATH='../results/'
+sed -i '' "s%${OLD_PATH}%${NEW_PATH}%g" $DEST"paper.tex"
+
+#Tar the file
+CURDIR=`pwd`
+cd $1
+tar cvzf "aas_pkg.tar.gz" "aas_pkg/"
+cd $CURDIR
+rm -r $DEST

### 2016-08-28 tex/paper.tex
fixing tikz include to import
final edits for content before submitting to ApJ

@@
 	%Frontmatter
-	\title{Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains}
+	\title{Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores. II. Nanoflare Trains}
 	\shorttitle{``Hot'' Non-flaring Plasmas II. Nanoflare Trains}
@@
 The term \textit{nanoflare} has now become synonomous with impulsive heating in the energy range $10^{24}-10^{27}$ erg, with no specific assumption regarding the underlying physical mechanism (for example, small-scale magnetic reconnection or hydromagnetic wave dissipation).
-	%
 In active region (AR) cores such as those we discuss in this paper, one strategy for constraining potential heating models is the analysis of the emission measure distribution as a function of temperature, $\mathrm{EM}(T)=\int n^2\mathrm{d}h$.
@@
 Below $T_m$, there is a scaling $\mathrm{EM}(T)\sim T^a$ over a temperature range $10^6\lesssim T\lesssim T_m$, a result first discussed by \citet{jordan_structure_1975}.
-Observations from instruments onboard the Solar Dynamics Observatory \citep[SDO,][]{pesnell_solar_2012} and \textit{Hinode} spacecraft \citep{kosugi_hinode_2007} have shown that $2\lesssim a\lesssim5$, with $T_m\approx10^{6.5-6.6}$ \citep{warren_constraints_2011,warren_systematic_2012,winebarger_using_2011,tripathi_emission_2011,schmelz_cold_2012,del_zanna_evolution_2015}.
+Observations from instruments onboard the \textit{Solar Dynamics Observatory} \citep[\textit{SDO},][]{pesnell_solar_2012} and \textit{Hinode} spacecraft \citep{kosugi_hinode_2007} have shown that $2\lesssim a\lesssim5$, with $T_m\approx10^{6.5-6.6}$ \citep{tripathi_emission_2011,warren_constraints_2011,warren_systematic_2012,winebarger_using_2011,schmelz_cold_2012,del_zanna_evolution_2015}.
 	%
@@
 However, measured values of these ``hotward" slopes are poorly constrained due to both the low magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}.
-\citet{warren_systematic_2012} find $7\lesssim b\lesssim10$ with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$.
+\citet{warren_systematic_2012} find $7\lesssim b\lesssim10$ with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the \textit{Solar Maximum Mission}, claim larger values for $b$.
 It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with different inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013}.
@@
 	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release along a single magnetic strand, where the observed loop comprises many such strands.
-Nanoflare heating can be classified as being either a \textit{high-} or \textit{low-frequency}.
-In the case of high-frequency (HF) heating, $t_N$, the time between successive events, is such that $t_N\ll\tau_{cool}$, where $\tau_{cool}$ is a characteristic loop cooling time, and in the case of low-frequency (LF) heating $t_N\gg\tau_{cool}$ \citep{mulu-moore_can_2011,warren_constraints_2011,bradshaw_diagnosing_2012,reep_diagnosing_2013,cargill_modelling_2015}.
-Steady heating is just high-frequency heating in the limit $t_N\to0$.
+Nanoflare heating can be classified as being either a \textit{high-} or \textit{low-frequency} (HF or LF, respectively).
+In the case of HF heating, $t_N$, the time between successive events, is such that $t_N\ll\tau_{cool}$, where $\tau_{cool}$ is a characteristic loop cooling time, and in the case of LF heating $t_N\gg\tau_{cool}$ \citep{mulu-moore_can_2011,warren_constraints_2011,bradshaw_diagnosing_2012,reep_diagnosing_2013,cargill_modelling_2015}.
+Steady heating is just HF heating in the limit $t_N\to0$.
 While a determination of $t_N$ is of great importance, its measurement is challenging.
@@
 	%
-	\par Single nanoflare are a good proxy for the LF heating scenario, but a study of nanoflare heating over a range of heating frequencies requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}.
+	\par Single nanoflares are a good proxy for the LF heating scenario, but a study of nanoflare heating over a range of heating frequencies requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}.
 In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$.
@@
 This amounts to computing spatial averages of the two-fluid hydrodynamic equations over both the transition region and corona.
-A full description and derivation of these equations can be found in the appendix of \citetalias{barnes_inference_2016-1}.
+A full description and derivation of these equations can be found in Appendix B of \citetalias{barnes_inference_2016-1}.
 The relevant two-fluid pressure and density equations are,
@@
 	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency, and $\psi_{TR}$ is a term included to maintain charge and current and neutrality.
-Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional modifications detailed in Appendix 1 of \citetalias{barnes_inference_2016-1}.
+Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional modifications detailed in Appendix A of \citetalias{barnes_inference_2016-1}.
 These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$.
@@
 		\caption{Examples of four different heating functions: uniform heating amplitudes for $t_N=1000$ s (top), uniform heating amplitudes for $t_N=5000$ s (middle), and heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$ (bottom).
-In the bottom panel, the events shown in red have waiting times that depend on the previous event energy while the events shown in blue have uniform waiting times.
+In the bottom panel, the events shown in red have waiting times that depend on the previous event energy ($\beta=1$) while the events shown in blue have uniform waiting times ($\beta=0$).
 The average waiting time in both cases is $t_N=2000$ s.}
@@
 	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{m}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}.
-Using our modified two-fluid EBTEL model, we have estimated the time-averaged volumetric heating rate needed to keep a loop of half-length $L=40$ Mm at $\bar{T}\approx4$ MK as  $H_{eq}\sim3.6\times10^{-3}$.
+Using our modified two-fluid EBTEL model, we have estimated the time-averaged volumetric heating rate needed to keep a loop of half-length $L=40$ Mm at $\bar{T}\approx4$ MK as  $H_{eq}\sim3.6\times10^{-3}$ erg cm$^{-3}$ s$^{-1}$.
 In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored.
@@
 	%
-	\begin{figure}
-		\centering
-		\include{parameter_space_graphic}
-		\caption{Total Parameter space covered.
-``single'' indicates a single-fluid model.
-$\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $\varepsilon\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent.
-Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions per heated species.}
-		\label{fig:parameter_space}
-	\end{figure}
-	%
 	\par According to the nanoflare heating model of \citet{parker_nanoflares_1988}, turbulent loop footpoint motions twist and stress the field, leading to a buildup and subsequent release of energy.
@@
 	\label{subsec:heating_stats}
+	%
+	\begin{figure}
+		\centering
+		\input{../results/static/parameter_space_graphic}
+		\caption{Total Parameter space covered.
+``single'' indicates a single-fluid model.
+$\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $\varepsilon\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent (i.e.
+$t_N$ is uniform).
+Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions per heated species.}
+		\label{fig:parameter_space}
+	\end{figure}
 	%
@@
 	\par As in \citetalias{barnes_inference_2016-1}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results.
-Given a temperature ($T(t)$) and density ($n(t)$) profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$, that would be inferred by assuming ionization equilibrium.
+Given a temperature and density profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$, that would be inferred by assuming ionization equilibrium.
 Using $T_{eff}$, we are then able to compute a corresponding NEI emission measure distribution, $\mathrm{EM}(T_{eff})$.
@@
 The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$.
-All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}.
-All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.
 	%%
@@
 		\caption{Fits to a sample emission measure distribution constructed from a loop plasma in which only the electrons were heated by events chosen from a power-law distribution with $\alpha=-2.5$ and equally spaced by an interval of $t_N=5000$ s.
-\textbf{Left:} $\mathrm{EM}(T)$ slope as a function of upper bound on fit interval for both the hot (red) and cool (blue) side of $\mathrm{EM}(T)$.
+\textbf{Left:} Emission measure slope as a function of upper bound on the fit interval for both the hot (red) and cool (blue) side of $\mathrm{EM}(T)$.
 The shading denotes the uncertainty of the fit.
@@
 \textbf{Right:} $\mathrm{EM}(T)$ with the overlaid hot (red) and cool (blue) fit lines whose slopes correspond to those shown on the left.
-The cool power-law fits describe $\mathrm{EM}(T)$ for $T<4$ MK quite well while a similar fit on the hot side fails to accurately describe the shape of the emission measure distribution for $T>4$ MK.}
+The cool power-law fits describe $\mathrm{EM}(T)$ for $T<4$ MK quite well while a similar fit on the hot side fails to accurately describe the shape of $\mathrm{EM}(T)$ for $T>4$ MK.}
 		\label{fig:em_slope_varying_bounds}
@@
 They argue that this provides possible evidence for impulsive heating.
-This arises from the fact that the $\mathrm{EM}(T)$ distribution resulting from low- and intermediate-frequency nanoflares is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}: for example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 10^{6.2}$ K and $10^{6.9}$ K.
+This arises from the fact that the $\mathrm{EM}(T)$ distribution resulting from low- and intermediate-frequency nanoflares is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}.
+For example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 10^{6.2}$ K and $10^{6.9}$ K.
 This suggests that the approach of \citet{brosius_pervasive_2014} could be used for any pair of appropriate emission lines and is likely to be of particular use where very limited spectral coverage is available either above or below $T_m$.
@@
 
-	\par Considering first the left hand panels, in the single fluid model the ratio is largely insensitive to $\alpha$ and is peaked sharply at $\sim0.75-1.0$ although the distribution peaks at slightly higher values for the $\beta=1$ case ($\sim1.25$).
+	\par Considering first the left hand panels, in the single fluid model (\autoref{fig:em_ratio_hist_single}) the ratio is largely insensitive to $\alpha$ and is peaked sharply at $\sim0.75-1.0$ although the distribution peaks at slightly higher values for the $\beta=1$ case ($\sim1.25$).
 Note that the uniform heating results (whose median is denoted by the vertical purple line near $\sim0.5$) show emission measure ratios significantly less than those in the power law cases, consistent with the reduced hot emission shown in \autoref{fig:single_em}.
-For electron heating the ratio is again insensitive to $\alpha$, but is narrower and falls off more quickly toward higher emission measure ratios.
+For electron heating (\autoref{fig:em_ratio_hist_el}) the ratio is again insensitive to $\alpha$, but is narrower and falls off more quickly toward higher emission measure ratios.
 The $\beta=0$ cases (for all $\alpha$) peak near $0.5$, with the $\beta=1$ cases all peaking at slightly higher values, but all less than 1.
-For ion heating the $\beta=0$ distributions peak at lower values compared to those with $\beta=1$.
+For ion heating (\autoref{fig:em_ratio_hist_ion}) the $\beta=0$ distributions peak at lower values compared to those with $\beta=1$.
 Again the results are relatively insensitive to $\alpha$.
@@
 Additionally, the $t_N=5000$ s case peaks slightly higher at $\sim1.5$ and does not ``pile up'' near 1.0 as the other values of $t_N$ do.
-For electron herating, the $t_N=3000$ s distribution has a very strong and narrow peak at $\approx0.5$ while all of the other distributions peak at $\sim1$.
+For electron heating, the $t_N=3000$ s distribution has a very strong and narrow peak at $\sim0.5$ while all of the other distributions peak at $\sim1$.
 For $t_N\ge3000$ s, the location of the peak increases weakly with increasing $t_N$ though this is not the case for $t_N=1000,2000$ s.
-Finally, for ion heating the distributions for each value of $t_N$ are much wider than for a single fluid and electron heating and the peak values show a stronger dependence on $t_N$.
-The range of peak values is also much larger, with the $t_N=1000$ s case peaking near 0 and the $t_N=5000$ s case peaking at $\sim2$.
+Finally, for ion heating the distributions for each value of $t_N$ are much wider than for the single fluid and electron heating cases and the peak values show a stronger dependence on $t_N$.
+The range of peak values is also much larger, with the $t_N=1000$ s case peaking near 0 and the $t_N=5000$ s case peaking just above $2$.
 As in \autoref{fig:em_ratio_hist_single}, we see that the $t_N=3000$ s distribution is bimodal.
-In general, the distributions grouped by $t_N$ for all three heating types have a positive skew and are peaked in the range $\sim0.5-1.5$ except for some extreme case in the ion heating scenario.
+In general, the distributions grouped by $t_N$ for all three heating types have a positive skew and are peaked in the range $\sim0.5-1.5$ except for some extreme cases in the ion heating scenario.
 	%
 	\par These results suggest that the emission measure ratio is generally in the range $\sim0.5-1.5$, with some higher values.
-Given the uncertainties in the atomic physics in particular, this seems to support the conclusion of the presence of nanoflare heating by \citet{brosius_pervasive_2014}.
+Given the uncertainties in the atomic physics, This seems to support the conclusion of the presence of nanoflare heating by \citet{brosius_pervasive_2014}.
 Thus the calculation of such ratios from limited data has the potential to be a powerful diagnostic of the existence of nanoflare heating.
@@
 On the other hand the calculation of a ratio between the emission measure at a pair of temperatures above and below $T_m$ held more promise.
-For a wide range of parameters the ratio of the emission measure at two temperatures, $T_{hot}=10^{6.9}>T_m$ and $T_{cool}=10^{6.2}<T_m$, was of order unity, consistent with \citet{brosius_pervasive_2014} within various errors.
+For a wide range of parameters the ratio of the emission measure at two temperatures, $T_{hot}=10^{6.95}>T_m$ and $T_{cool}=10^{6.2}<T_m$, was of order unity, consistent with \citet{brosius_pervasive_2014} within various errors.
 Further observational evidence of such ratios would, in our view, provide a very strong case for the presence of nanoflare heating.
@@
 	%
-	\software{astroML \citep{vanderplas_introduction_2012}, IPython \citep{perez_ipython:_2007}, Jupyter notebook, matplotlib \citep{hunter_matplotlib:_2007}, NumPy, seaborn \citep{waskom_seaborn:_2016}, scipy \citep{van_der_walt_numpy_2011}}
+	\software{astroML \citep{vanderplas_introduction_2012}, IPython/Jupyter \citep{perez_ipython:_2007}, matplotlib \citep{hunter_matplotlib:_2007}, NumPy, seaborn \citep{waskom_seaborn:_2016}, scipy \citep{van_der_walt_numpy_2011}}
 	%
@@
 	\bibliographystyle{aasjournal}
-	%\bibliography{hot_non-flaring_plasma_2.bbl}
 \end{document}

### 2016-08-28 make_aas_pkg.sh
updating packaging script

@@ -11,7 +11,7 @@ fi
 #Clean up
 if [ "$2" == "clean" ]; then
 	echo "Cleaning up archive and directory at "$DEST
-	rm $1"aas_pkg.tar.gz"
+	rm $1"aas_pkg.tar.gz" && rm -r $DEST
 	exit 0
 fi
 

### 2016-08-28 make_aas_pkg.sh
more sensible fig names when packaging

@@ -26,9 +26,14 @@ cp $PATH2FILES"tex/paper."{"tex","bbl"} $DEST
 #Load figure manifest
 fig_array=(`cat $PATH2FILES"FIG_MANIFEST"`)
 array_len=${#fig_array[@]}
-for i in `seq 0 $((array_len-1))`
+for i in `seq 0 2 $((array_len-1))`
 do
-	cp $PATH2FILES"results/"${fig_array[$((i))]} $DEST
+	OLD_FIG=${fig_array[$((i))]}
+	NEW_FIG=${fig_array[$((i+1))]}
+	#copy the file over
+	cp $PATH2FILES"results/"$OLD_FIG $DEST$NEW_FIG
+	#replace the name
+	sed -i '' "s%${OLD_FIG}%${NEW_FIG}%g" $DEST"paper.tex"
 done
 
 #copy tikz graphics to right spot

### 2016-08-28 make_aas_pkg.sh
updating packaging script

@@ -21,7 +21,7 @@ PATH2FILES=$(cd `dirname $0` && pwd)"/"
 #Copy needed TeX files
 cp $PATH2FILES"tex/paper."{"tex","bbl"} $DEST
 #cp $PATH2FILES"tex/aasjournal.bst" $DEST
-#cp $PATH2FILES"tex/aastex.cls" $DEST
+cp $PATH2FILES"tex/aastex.cls" $DEST
 
 #Load figure manifest
 fig_array=(`cat $PATH2FILES"FIG_MANIFEST"`)

### 2016-10-13 tex/paper.tex
minor paper updates

@@
 \newcommand{\ang}{\AA~}
-\defcitealias{barnes_inference_2016-1}{Paper I}
+\defcitealias{barnes_inference_2016}{Paper I}
 \renewcommand{\sectionautorefname}{Section}
@@
 	\par An analogous approach can be used to investigate the properties of the ``hot" coronal component expected from nanoflare heating, and is the subject of the present series of papers.
-In \citet{barnes_inference_2016-1} \citepalias[hereafter]{barnes_inference_2016-1}, we looked at the hot plasma properties due to a single isolated nanoflare.
+In \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we looked at the hot plasma properties due to a single isolated nanoflare.
 The effects of heating pulse duration, changes to conductive cooling due to heat flux limiting, differential heating of electrons and ions, and non-equilibrium ionization (NEI) were studied.
@@
 	\par In order to treat the evolution of the electron and ion populations separately, we use a modified version of the usual EBTEL equations.
-This amounts to computing spatial averages of the two-fluid hydrodynamic equations over both the transition region and corona.
-A full description and derivation of these equations can be found in Appendix B of \citetalias{barnes_inference_2016-1}.
+This amounts to computing spatial averages of the two-fluid hydrodynamic equations over both the transition region and corona\footnote{The two-fluid EBTEL  code is freely available and can be downloaded at: \url{https://github.com/rice-solar-physics/ebtelPlusPlus}.}.
+A full description and derivation of these equations can be found in Appendix B of \citetalias{barnes_inference_2016}.
 The relevant two-fluid pressure and density equations are,
@@
 	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency, and $\psi_{TR}$ is a term included to maintain charge and current and neutrality.
-Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional modifications detailed in Appendix A of \citetalias{barnes_inference_2016-1}.
+Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional modifications detailed in Appendix A of \citetalias{barnes_inference_2016}.
 These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$.
@@
 In all cases we use a saturation limit of $f=1$.
-See \citetalias{barnes_inference_2016-1} for a discussion of how $f$ is likely to effect the presence of hot emission in a nanoflare-heated plasma.
+See \citetalias{barnes_inference_2016} for a discussion of how $f$ is likely to effect the presence of hot emission in a nanoflare-heated plasma.
 	%
@@
 	%%
-	\par When considering the role of nanoflares in the production of hot plasma in AR cores, it is important to take non-equilibrium ionization (NEI) into account \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008,barnes_inference_2016-1}.
+	\par When considering the role of nanoflares in the production of hot plasma in AR cores, it is important to take non-equilibrium ionization (NEI) into account \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008,barnes_inference_2016}.
 In a steady heating scenario, the ionization state is an adequate measure of the electron plasma temperature.
@@
 	%
-	\par As in \citetalias{barnes_inference_2016-1}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results.
+	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results.
 Given a temperature and density profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$, that would be inferred by assuming ionization equilibrium.
@@
 We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$.
-In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016-1}.
+In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016}.
 The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$.
@@
 The dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$.
-The cases shown in \citetalias{barnes_inference_2016-1} correspond approximately to the red curves in the lower right panels ($t_N=5000$ s) in each of the three figures since the loop is allowed to cool and drain completely before reheating and a single nanoflare energy is used.
+The cases shown in \citetalias{barnes_inference_2016} correspond approximately to the red curves in the lower right panels ($t_N=5000$ s) in each of the three figures since the loop is allowed to cool and drain completely before reheating and a single nanoflare energy is used.
 	%
@@
 Especially interesting in this case are the results with NEI included.
-For a uniform nanoflare train, NEI plays no role up to $t_N$ = 2500 sec, but above that it restricts the temperatures that can be detected, as shown in \citetalias{barnes_inference_2016-1}.
+For a uniform nanoflare train, NEI plays no role up to $t_N$ = 2500 sec, but above that it restricts the temperatures that can be detected, as shown in \citetalias{barnes_inference_2016}.
 This hot emission is relocated to cooler temperatures, resulting in a small ``bump'' in the emission measure distribution near 10 MK.
@@
 This cutoff at lower temperatures is due to the fact that the electrons cannot ``see'' the ions until they have cooled well below their peak temperature.
-This is discussed in \citetalias{barnes_inference_2016-1} though in the single-pulse cases, the cutoff occured at lower temperatures.
+This is discussed in \citetalias{barnes_inference_2016} though in the single-pulse cases, the cutoff occured at lower temperatures.
 Additionally, in both the uniform and power law cases, the peak of $\mathrm{EM}(T)$ is wider for these low frequencies compared to those shown in the lower right panels of \autoref{fig:single_em} and \autoref{fig:el_em}.
@@
 	%
-	\par In \citet{cargill_active_2014}, \citetalias{barnes_inference_2016-1}, and \autoref{subsec:em_dist}, we have suggested that the plasma density prior to the nanoflare occuring is a crucial parameter in determining the emission measure distribution.
+	\par In \citet{cargill_active_2014}, \citetalias{barnes_inference_2016}, and \autoref{subsec:em_dist}, we have suggested that the plasma density prior to the nanoflare occuring is a crucial parameter in determining the emission measure distribution.
 This arises in two distinct ways.
@@
 \citet{antiochos_evaporative_1978} showed analytically that accounting for evaporative cooling and assuming constant pressure gives $b=11/2$, though this value can be as low as $b=5/2$ if a flux limiter is included.
-However, in \citetalias{barnes_inference_2016-1}, we showed that in the case of a single 200 s nanoflare that heats only the electrons, the assumption of constant electron pressure during the heating and early conductive cooling phases does not hold.
-Our results here are consistent with our findings in \citetalias{barnes_inference_2016-1} in that the parameter $b$ does not provide any valuable information about $\mathrm{EM}(T)$ for $T>T_m$ when two-fluid effects are considered.
+However, in \citetalias{barnes_inference_2016}, we showed that in the case of a single 200 s nanoflare that heats only the electrons, the assumption of constant electron pressure during the heating and early conductive cooling phases does not hold.
+Our results here are consistent with our findings in \citetalias{barnes_inference_2016} in that the parameter $b$ does not provide any valuable information about $\mathrm{EM}(T)$ for $T>T_m$ when two-fluid effects are considered.
 Clearly, an alternative metric for measuring the amount of hot plasma in the emission measure distribution is needed.
@@
 	\label{subsubsec:em_ratio}
+	\authorcomment1{TODO:Change/update all temperatures ratio references appropriately.
+TODO: add additional figure/paragraph describing how changes in hot/cool temperatures are likely to affect our result}
 	%%
@@
 		\par\citet{brosius_pervasive_2014} proposed another possible diagnostic for the hot non-flaring corona.
-Using observations of an active region from the \textit{EUNIS-13} sounding rocket, they found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside.
+Using observations of an active region from the \textit{EUNIS-13} sounding rocket, they found that the intensity ratio of Fe XIX (formed at $T\approx8.9$ MK) to Fe XII (formed at $T\approx1.6$ MK) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside.
 They argue that this provides possible evidence for impulsive heating.
 This arises from the fact that the $\mathrm{EM}(T)$ distribution resulting from low- and intermediate-frequency nanoflares is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}.
-For example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 10^{6.2}$ K and $10^{6.9}$ K.
+For example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 1.6$ MK and $8.9$ MK.
 This suggests that the approach of \citet{brosius_pervasive_2014} could be used for any pair of appropriate emission lines and is likely to be of particular use where very limited spectral coverage is available either above or below $T_m$.
@@
 
-	\par We define a general emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$ and for this paper consider $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.2}$ K, consistent with \citet{brosius_pervasive_2014}.
+	\par We define a general emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$ and \textbf{for this paper consider $T_{hot}=10^{6.942}$ K and $T_{cool}=10^{6.187}$ K, the formation temperatures of Fe XIX and XII, respectively \citep[i.e.
+the temperature $T$ which maximizes the contribution function $G_{\lambda}(T)$ calculated using CHIANTI v8,][]{dere_chianti_1997,del_zanna_chianti_2015}}.
 This also provides a way to compare in a concise way every point in our multidimensional parameter space though we acknowledge that we are reducing $8\times10^4$ s of loop evolution to a single value.
@@
 This is compared to the ion heating case where a finite equilibration time means that the electrons are heated more slowly.
-We find that, unlike some of the examples in \citetalias{barnes_inference_2016-1}, NEI is not a major consideration, a constant nanoflare train being the exception.
+We find that, unlike some of the examples in \citetalias{barnes_inference_2016}, NEI is not a major consideration, a constant nanoflare train being the exception.
 		%

### 2016-10-14 tex/paper.tex
first draft after first round of referee feedback

@@
 In active region (AR) cores such as those we discuss in this paper, one strategy for constraining potential heating models is the analysis of the emission measure distribution as a function of temperature, $\mathrm{EM}(T)=\int n^2\mathrm{d}h$.
-\citet{cargill_implications_1994,cargill_nanoflare_2004} predicted that $\mathrm{EM}(T)$ resulting from nanoflare heating should be wide, with a maximum value at $T=T_m\sim10^{6.5}$ K and have a faint, high-temperature (8-10 MK) component.
+\citet{cargill_implications_1994,cargill_nanoflare_2004} predicted that the $\mathrm{EM}(T)$ resulting from nanoflare heating should be wide, with a maximum value at $T=T_m\sim10^{6.5}$ K and have a faint, high-temperature (8-10 MK) component.
 Below $T_m$, there is a scaling $\mathrm{EM}(T)\sim T^a$ over a temperature range $10^6\lesssim T\lesssim T_m$, a result first discussed by \citet{jordan_structure_1975}.
@@
 In all cases we use a saturation limit of $f=1$.
-See \citetalias{barnes_inference_2016} for a discussion of how $f$ is likely to effect the presence of hot emission in a nanoflare-heated plasma.
+See \citetalias{barnes_inference_2016} for a discussion of how $f$ is likely to affect the presence of hot emission in a nanoflare-heated plasma.
 	%
@@
 Note that if $H_i=H_0$ for all $i$, the heating rate for each event is $H_i=H_0=2t_{total}H_{eq}/N\tau$.
-Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the average energy per event for a loop heated by $N=20$ nanoflares in $t_{total}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx5.8\times10^{24}$ erg.
+Thus, for $L=40$ Mm and cross-sectional area $A=10^{14}$ cm$^2$, the average energy per event for a loop heated by $N=20$ nanoflares in $t_{total}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx5.8\times10^{24}$ erg.
 	%
@@
 Note that in some panels, the blue $\beta=0$ curves may not be visible because they overlap heavily with the green $\beta=1$ curves.
-The solid lines in the two power law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean.
+The solid lines in the two power law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates one standard deviation from the mean.
 The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.
@@
 In order to present our results compactly, the solid lines in \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} each show the mean $\mathrm{EM}(T)$ over all $N_R$ curves.
-The shading represents $1\sigma$ from the mean.
+The shading represents one standard deviation from the mean.
 In this way, we account for the variations that may occur because of a lack/excess of strong heating events due to limited sampling from the power-law distribution of possible heating rates.
@@
 	\label{subsubsec:em_ratio}
-	\authorcomment1{TODO:Change/update all temperatures ratio references appropriately.
-TODO: add additional figure/paragraph describing how changes in hot/cool temperatures are likely to affect our result}
 	%%
 	\begin{figure*}
-		\plottwo{../results/ratio_hist_alpha_single_T1.pdf}{../results/ratio_hist_twait_single_T1.pdf}
-		\caption{Histograms of emission measure ratios $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$, where $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.2}$ K, for all heating function types and heating frequencies for the single fluid case.
-In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the Bayesian blocks method of \citet{scargle_studies_2013} as implemented in the astroML Python package for statistical learning in astronomy \citep{vanderplas_introduction_2012}.
+		\plottwo{../results/ratio_hist_alpha_single_T0.pdf}{../results/ratio_hist_twait_single_T0.pdf}
+		\caption{Histograms of emission measure ratios $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$, where $T_{hot}=10^{6.942}$ K and $T_{cool}=10^{6.187}$ K, for all heating function types and heating frequencies for the single fluid case.
+In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the Bayesian blocks method of \citet{scargle_studies_2013}.
 \textbf{Left:} Emission measure ratios separated by heating function type for all heating frequencies, $250\le t_N\le5000$ s.
@@
 	\begin{figure*}
-		\plottwo{../results/ratio_hist_alpha_electron_T1.pdf}{../results/ratio_hist_twait_electron_T1.pdf}
+		\plottwo{../results/ratio_hist_alpha_electron_T0.pdf}{../results/ratio_hist_twait_electron_T0.pdf}
 		\caption{Same as \autoref{fig:em_ratio_hist_single}, but for the case where only the electrons are heated.}
@@
 	\begin{figure*}
-		\plottwo{../results/ratio_hist_alpha_ion_T1.pdf}{../results/ratio_hist_twait_ion_T1.pdf}
+		\plottwo{../results/ratio_hist_alpha_ion_T0.pdf}{../results/ratio_hist_twait_ion_T0.pdf}
 		\caption{Same as \autoref{fig:em_ratio_hist_single}, but for the case where only the ions are heated.
@@
 In the left-hand panels each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function.
-This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$ and $t_{N,i}=t_N$ for all $i$ (i.e.
-$\beta=0$).
+This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are evenly spaced (i.e.
+$\beta=0$) and chosen from a power-law distribution of $\alpha=-1.5$.
 The right panels show these same emission measure ratios, but now categorized by $t_N$.
@@
 
-	\par Considering first the left hand panels, in the single fluid model (\autoref{fig:em_ratio_hist_single}) the ratio is largely insensitive to $\alpha$ and is peaked sharply at $\sim0.75-1.0$ although the distribution peaks at slightly higher values for the $\beta=1$ case ($\sim1.25$).
-Note that the uniform heating results (whose median is denoted by the vertical purple line near $\sim0.5$) show emission measure ratios significantly less than those in the power law cases, consistent with the reduced hot emission shown in \autoref{fig:single_em}.
+	\par Considering first the left hand panels, in the single fluid model (\autoref{fig:em_ratio_hist_single}) the ratio is largely insensitive to $\alpha$ and is peaked sharply at $\sim1-1.25$ although the distribution peaks at slightly higher values for the $\beta=1$ case ($\sim1.5$).
+Note that the uniform heating results (whose median is denoted by the vertical purple line near $\sim0.6$) show emission measure ratios significantly less than those in the power law cases, consistent with the reduced hot emission shown in \autoref{fig:single_em}.
 For electron heating (\autoref{fig:em_ratio_hist_el}) the ratio is again insensitive to $\alpha$, but is narrower and falls off more quickly toward higher emission measure ratios.
-The $\beta=0$ cases (for all $\alpha$) peak near $0.5$, with the $\beta=1$ cases all peaking at slightly higher values, but all less than 1.
+The $\beta=0$ cases (for all $\alpha$) peak just above $0.5$, with the $\beta=1$ cases all peaking at slightly higher values just at or below 1.
 For ion heating (\autoref{fig:em_ratio_hist_ion}) the $\beta=0$ distributions peak at lower values compared to those with $\beta=1$.
 Again the results are relatively insensitive to $\alpha$.
-However, compared to the electron heating case, all of the distributions are much wider and peak at higher values, $\sim1.5$ for $\beta=0$ and $>2$ for $\beta=1$.
+However, compared to the electron heating case, all of the distributions are much wider and peak at higher values, $\sim1.75$ for $\beta=0$ and $\sim2-2.5$ for $\beta=1$.
 Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$.
 
-	\par Turning to the right hand panels, in the single-fluid model for $t_N\le4000$ s, the results cluster just near 1.0, though the $t_N=3000$ s distribution is slightly bimodal, peaking strongly at $\sim0.75$ and more weakly at $\sim1.25$.
-Additionally, the $t_N=5000$ s case peaks slightly higher at $\sim1.5$ and does not ``pile up'' near 1.0 as the other values of $t_N$ do.
-For electron heating, the $t_N=3000$ s distribution has a very strong and narrow peak at $\sim0.5$ while all of the other distributions peak at $\sim1$.
+	\par Turning to the right hand panels, in the single-fluid model for $t_N\le4000$ s, the results cluster just near 1.5, though the $t_N=3000$ s distribution is slightly bimodal, peaking strongly at $\sim0.75$ and more weakly at $\sim1.5$.
+Additionally, the $t_N=5000$ s case peaks slightly higher at $\sim2$ and does not ``pile up'' near $1.5$ as the other values of $t_N$ do.
+For electron heating, the $t_N=3000$ s distribution has a very strong and narrow peak at $\sim0.5$ while all of the other distributions peak at $\sim1-1.5$.
 For $t_N\ge3000$ s, the location of the peak increases weakly with increasing $t_N$ though this is not the case for $t_N=1000,2000$ s.
 Finally, for ion heating the distributions for each value of $t_N$ are much wider than for the single fluid and electron heating cases and the peak values show a stronger dependence on $t_N$.
-The range of peak values is also much larger, with the $t_N=1000$ s case peaking near 0 and the $t_N=5000$ s case peaking just above $2$.
+The range of peak values is also much larger, with the $t_N=1000$ s case peaking near 0 and the $t_N=5000$ s case peaking just at $\sim2.5$.
 As in \autoref{fig:em_ratio_hist_single}, we see that the $t_N=3000$ s distribution is bimodal.
-In general, the distributions grouped by $t_N$ for all three heating types have a positive skew and are peaked in the range $\sim0.5-1.5$ except for some extreme cases in the ion heating scenario.
+In general, the distributions grouped by $t_N$ for all three heating types have a positive skew and are peaked in the range $\sim0.5-2$ except for some extreme cases in the ion heating scenario.
 	%
-	\par These results suggest that the emission measure ratio is generally in the range $\sim0.5-1.5$, with some higher values.
-Given the uncertainties in the atomic physics, This seems to support the conclusion of the presence of nanoflare heating by \citet{brosius_pervasive_2014}.
+	\par These results suggest that the emission measure ratio is generally in the range $\sim0.5-2$, with some higher values.
+Given the uncertainties in the atomic physics, this seems to support the conclusion of the presence of nanoflare heating by \citet{brosius_pervasive_2014}.
 Thus the calculation of such ratios from limited data has the potential to be a powerful diagnostic of the existence of nanoflare heating.
@@
 The problem with drawing conclusions from the details of these results lies in the numerous uncertainties in any data, especially concerning atomic physics.
+	%%
+	\subsubsection{Additional Line Pairs}
+	\label{subsubsec:add_line_pairs}
+	%
+	\begin{figure*}
+		\plotone{../results/em_ratio_versus_tn.pdf}
+		\caption{Emission measure ratio as a function of $t_N$ for the single-fluid (left), electron heating (center), and ion heating (right) cases for four different line pairs: Fe XIX/Fe XII (blue), Fe XIX/Fe XV (green), Fe XX/Fe XII (red), and Fe XX/Fe XV (yellow).
+The formation temperatures of Fe XV and Fe XX, calculated using CHIANTI v8, are $10^{6.342}$ K and $10^{7.027}$ K, respectively.
+The circles ($\beta=0$) and stars ($\beta=1$) indicate the mean EM ratio calculated over all runs for a given $t_N$ (see \autoref{subsec:heating_stats}) and the error bars indicate one standard deviation from the mean.}
+		\label{fig:em_ratio_vs_tn}
+	\end{figure*}
+	%
+	\par \textbf{Because our proposed EM ratio diagnostic is based on only two points from each $\mathrm{EM}(T)$, it is reasonable to ask how this measurement might be affected by a different choice of hot/cool temperatures.
+\autoref{fig:em_ratio_vs_tn} shows the mean EM ratio (with the error bars corresponding to one standard deviation) as a function of $t_N$ for three additional line pairs: Fe XIX/XV, Fe XX/XII, and Fe XX/XV, as denoted by the color coding.
+The circles (stars) correspond to $\beta=0(1)$ and we consider only $\alpha=-2.5$ here.
+The values of the line ratios can be organized from high to low as Fe XIX/Fe XII, Fe XX/Fe XII, Fe XIX/Fe XV and Fe XX/Fe XV.
+The second and third pairs have similar ratio values.
+This ordering is to be expected from the general shape of the $\mathrm{EM}(T)$ curves, although the exact ratios cannot be predicted in any simple way.}
+%
+	\par \textbf{For $\beta=1$, the ratio decreases monotonically as $t_N$ decreases, however the values of the ratio lie within a narrow band.
+Given the many uncertainties in the measurements, it is unlikely that any of these line pairs can provide an unequivocal constraint on $t_N$.
+For $\beta=0$, there is an upturn in the ratio between $t_n = 2000$ s and $3000$ s, and below this value, the ratios are ill-defined due to lack of plasma at one or both of the measured temperatures.
+At lower temperatures, this arises because, for an evenly spaced nanoflare train, there is a sharp cut-off in $\mathrm{EM}(T)$ at some temperature $T< T_m$ which does not occur when a waiting time is included \citep{cargill_active_2014}.}
+% 
+	\par \textbf{On the other hand, the relative ratios of line pairs is a quantitative prediction that can be examined were such data to be available, and can be easily extended to other line pairs not considered here.
+In addition, for all line pairs, the detection of an emission measure ratio lying between the upper and lower bounds shown can be regarded as a very strong indicator of the presence of ``hot'' nanoflare-produced plasma.
+Further deductions require more detailed modeling of in particular the atomic physics which is beyond the scope of this paper.}
 	%%
@@
 On the other hand the calculation of a ratio between the emission measure at a pair of temperatures above and below $T_m$ held more promise.
-For a wide range of parameters the ratio of the emission measure at two temperatures, $T_{hot}=10^{6.95}>T_m$ and $T_{cool}=10^{6.2}<T_m$, was of order unity, consistent with \citet{brosius_pervasive_2014} within various errors.
+For a wide range of parameters the ratio of the emission measure at two temperatures, $T_{hot}=10^{6.942}>T_m$ and $T_{cool}=10^{6.187}<T_m$, was of order unity, consistent with \citet{brosius_pervasive_2014} within various errors.
 Further observational evidence of such ratios would, in our view, provide a very strong case for the presence of nanoflare heating.
@@
 	%
-	\software{astroML \citep{vanderplas_introduction_2012}, IPython/Jupyter \citep{perez_ipython:_2007}, matplotlib \citep{hunter_matplotlib:_2007}, NumPy, seaborn \citep{waskom_seaborn:_2016}, scipy \citep{van_der_walt_numpy_2011}}
+	\software{astroML \citep{vanderplas_introduction_2012}, IPython/Jupyter \citep{perez_ipython:_2007}, matplotlib \citep{hunter_matplotlib:_2007}, NumPy/scipy \citep{van_der_walt_numpy_2011}, seaborn \citep{waskom_seaborn:_2016}}
 	%

### 2016-10-18 make_aas_pkg.sh
build cover letter PDF

@@ -46,6 +46,12 @@ sed -i '' "s%${OLD_PATH}%${NEW_PATH}%g" $DEST"paper.tex"
 OLD_PATH='../results/'
 sed -i '' "s%${OLD_PATH}%${NEW_PATH}%g" $DEST"paper.tex"
 
+#Add a cover letter PDF if it exists (requires pandoc)
+if [-f $PATH2FILES"COVER_LETTER.md"];
+then
+	pandoc $PATH2FILES"COVER_LETTER.md" --latex-engine=xelatex -V geometry:margin=1in -o $DEST"COVER_LETTER.pdf"
+fi
+
 #Tar the file
 CURDIR=`pwd`
 cd $1

### 2016-10-18 tex/paper.tex
final tweaks before revisions submitted

@@
-\documentclass[preprint,linenumbers]{aastex}
+\documentclass[preprint]{aastex}
 
@@
 		\plottwo{../results/ratio_hist_alpha_ion_T0.pdf}{../results/ratio_hist_twait_ion_T0.pdf}
-		\caption{Same as \autoref{fig:em_ratio_hist_single}, but for the case where only the ions are heated.
-Here, the bin widths are calculated according to the well-known Freedman-Diaconis formula \citep{freedman_histogram_1981}}
+		\caption{Same as \autoref{fig:em_ratio_hist_single}, but for the case where only the ions are heated.}
 		\label{fig:em_ratio_hist_ion}
@@
 For flare-like energy release one would expect the hot emission to be much greater than the cold emission, with the opposite in the quiet Sun.
-
+\textbf{It should be noted that there can be considerable uncertainties in deriving a reliable $\mathrm{EM}(T)$ distribution from observations due to uncertainties from the atomic physics, line-of sight, loop geometry, etc., which will hopefully be mitigated by improved knowledge of such quantities in the future.
+\citet{guennou_can_2013} provide an extensive overview of this topic.}
+%
 	\par We define a general emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$ and \textbf{for this paper consider $T_{hot}=10^{6.942}$ K and $T_{cool}=10^{6.187}$ K, the formation temperatures of Fe XIX and XII, respectively \citep[i.e.
@@
 Note that we choose to only show results for five values of $t_N$ for aesthetic purposes.
-
+%
 	\par Considering first the left hand panels, in the single fluid model (\autoref{fig:em_ratio_hist_single}) the ratio is largely insensitive to $\alpha$ and is peaked sharply at $\sim1-1.25$ although the distribution peaks at slightly higher values for the $\beta=1$ case ($\sim1.5$).
@@
 Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$.
-
+%
 	\par Turning to the right hand panels, in the single-fluid model for $t_N\le4000$ s, the results cluster just near 1.5, though the $t_N=3000$ s distribution is slightly bimodal, peaking strongly at $\sim0.75$ and more weakly at $\sim1.5$.
@@
 		\caption{Emission measure ratio as a function of $t_N$ for the single-fluid (left), electron heating (center), and ion heating (right) cases for four different line pairs: Fe XIX/Fe XII (blue), Fe XIX/Fe XV (green), Fe XX/Fe XII (red), and Fe XX/Fe XV (yellow).
-The formation temperatures of Fe XV and Fe XX, calculated using CHIANTI v8, are $10^{6.342}$ K and $10^{7.027}$ K, respectively.
-The circles ($\beta=0$) and stars ($\beta=1$) indicate the mean EM ratio calculated over all runs for a given $t_N$ (see \autoref{subsec:heating_stats}) and the error bars indicate one standard deviation from the mean.}
+The circles ($\beta=0$) and stars ($\beta=1$) indicate the mean EM ratio calculated over all runs for a given $t_N$ (see \autoref{subsec:heating_stats}) and the error bars indicate one standard deviation from the mean.
+Here we only show the results for $\alpha=-2.5$.}
 		\label{fig:em_ratio_vs_tn}
@@
 \autoref{fig:em_ratio_vs_tn} shows the mean EM ratio (with the error bars corresponding to one standard deviation) as a function of $t_N$ for three additional line pairs: Fe XIX/XV, Fe XX/XII, and Fe XX/XV, as denoted by the color coding.
+The formation temperatures of Fe XV and Fe XX, calculated using CHIANTI v8, are $10^{6.342}$ K and $10^{7.027}$ K, respectively.
 The circles (stars) correspond to $\beta=0(1)$ and we consider only $\alpha=-2.5$ here.

### 2016-10-18 make_aas_pkg.sh
fixing bug in package builder script

@@ -47,7 +47,7 @@ OLD_PATH='../results/'
 sed -i '' "s%${OLD_PATH}%${NEW_PATH}%g" $DEST"paper.tex"
 
 #Add a cover letter PDF if it exists (requires pandoc)
-if [-f $PATH2FILES"COVER_LETTER.md"];
+if [ -f $PATH2FILES"COVER_LETTER.md" ];
 then
 	pandoc $PATH2FILES"COVER_LETTER.md" --latex-engine=xelatex -V geometry:margin=1in -o $DEST"COVER_LETTER.pdf"
 fi

### 2016-10-19 make_aas_pkg.sh
add arXiv flag

@@ -47,7 +47,7 @@ OLD_PATH='../results/'
 sed -i '' "s%${OLD_PATH}%${NEW_PATH}%g" $DEST"paper.tex"
 
 #Add a cover letter PDF if it exists (requires pandoc)
-if [ -f $PATH2FILES"COVER_LETTER.md" ];
+if [ -f $PATH2FILES"COVER_LETTER.md" ] && [ "$2" != "arxiv" ];
 then
 	pandoc $PATH2FILES"COVER_LETTER.md" --latex-engine=xelatex -V geometry:margin=1in -o $DEST"COVER_LETTER.pdf"
 fi

### 2016-10-19 tex/paper.tex
remove revision bolding

@@
 For flare-like energy release one would expect the hot emission to be much greater than the cold emission, with the opposite in the quiet Sun.
-\textbf{It should be noted that there can be considerable uncertainties in deriving a reliable $\mathrm{EM}(T)$ distribution from observations due to uncertainties from the atomic physics, line-of sight, loop geometry, etc., which will hopefully be mitigated by improved knowledge of such quantities in the future.
-\citet{guennou_can_2013} provide an extensive overview of this topic.}
+It should be noted that there can be considerable uncertainties in deriving a reliable $\mathrm{EM}(T)$ distribution from observations due to uncertainties from the atomic physics, line-of sight, loop geometry, etc., which will hopefully be mitigated by improved knowledge of such quantities in the future.
+\citet{guennou_can_2013} provide an extensive overview of this topic.
 %
-	\par We define a general emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$ and \textbf{for this paper consider $T_{hot}=10^{6.942}$ K and $T_{cool}=10^{6.187}$ K, the formation temperatures of Fe XIX and XII, respectively \citep[i.e.
-the temperature $T$ which maximizes the contribution function $G_{\lambda}(T)$ calculated using CHIANTI v8,][]{dere_chianti_1997,del_zanna_chianti_2015}}.
+	\par We define a general emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$ and for this paper consider $T_{hot}=10^{6.942}$ K and $T_{cool}=10^{6.187}$ K, the formation temperatures of Fe XIX and XII, respectively \citep[i.e.
+the temperature $T$ which maximizes the contribution function $G_{\lambda}(T)$ calculated using CHIANTI v8,][]{dere_chianti_1997,del_zanna_chianti_2015}.
 This also provides a way to compare in a concise way every point in our multidimensional parameter space though we acknowledge that we are reducing $8\times10^4$ s of loop evolution to a single value.
@@
 	%
-	\par \textbf{Because our proposed EM ratio diagnostic is based on only two points from each $\mathrm{EM}(T)$, it is reasonable to ask how this measurement might be affected by a different choice of hot/cool temperatures.
+	\par Because our proposed EM ratio diagnostic is based on only two points from each $\mathrm{EM}(T)$, it is reasonable to ask how this measurement might be affected by a different choice of hot/cool temperatures.
 \autoref{fig:em_ratio_vs_tn} shows the mean EM ratio (with the error bars corresponding to one standard deviation) as a function of $t_N$ for three additional line pairs: Fe XIX/XV, Fe XX/XII, and Fe XX/XV, as denoted by the color coding.
@@
 The second and third pairs have similar ratio values.
-This ordering is to be expected from the general shape of the $\mathrm{EM}(T)$ curves, although the exact ratios cannot be predicted in any simple way.}
+This ordering is to be expected from the general shape of the $\mathrm{EM}(T)$ curves, although the exact ratios cannot be predicted in any simple way.
 %
-	\par \textbf{For $\beta=1$, the ratio decreases monotonically as $t_N$ decreases, however the values of the ratio lie within a narrow band.
+	\par For $\beta=1$, the ratio decreases monotonically as $t_N$ decreases, however the values of the ratio lie within a narrow band.
 Given the many uncertainties in the measurements, it is unlikely that any of these line pairs can provide an unequivocal constraint on $t_N$.
 For $\beta=0$, there is an upturn in the ratio between $t_n = 2000$ s and $3000$ s, and below this value, the ratios are ill-defined due to lack of plasma at one or both of the measured temperatures.
-At lower temperatures, this arises because, for an evenly spaced nanoflare train, there is a sharp cut-off in $\mathrm{EM}(T)$ at some temperature $T< T_m$ which does not occur when a waiting time is included \citep{cargill_active_2014}.}
+At lower temperatures, this arises because, for an evenly spaced nanoflare train, there is a sharp cut-off in $\mathrm{EM}(T)$ at some temperature $T< T_m$ which does not occur when a waiting time is included \citep{cargill_active_2014}.
 % 
-	\par \textbf{On the other hand, the relative ratios of line pairs is a quantitative prediction that can be examined were such data to be available, and can be easily extended to other line pairs not considered here.
+	\par On the other hand, the relative ratios of line pairs is a quantitative prediction that can be examined were such data to be available, and can be easily extended to other line pairs not considered here.
 In addition, for all line pairs, the detection of an emission measure ratio lying between the upper and lower bounds shown can be regarded as a very strong indicator of the presence of ``hot'' nanoflare-produced plasma.
-Further deductions require more detailed modeling of in particular the atomic physics which is beyond the scope of this paper.}
+Further deductions require more detailed modeling of in particular the atomic physics which is beyond the scope of this paper.
 	%%
